\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools,bm}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{calc,decorations.pathreplacing}
\numberwithin{equation}{section}

\newcommand{\al}{\alpha'}
\newcommand{\perpD}{D_\perp}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\ii}{\mathrm{i}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\arxiv}[1]{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\newcommand{\doi}[1]{\href{https://doi.org/#1}{doi:#1}}

\title{Lightcone Mandelstam Amplitudes with Discrete \texorpdfstring{$\sigma$}{sigma}}
\author{}
\date{\today}

\begin{document}
\maketitle

\section{Goal}
We want a practical formulation of lightcone bosonic and superstring amplitudes in Mandelstam parametrization where:
\begin{itemize}
\item the worldsheet spatial direction $\sigma$ is discretized,
\item each propagator cylinder is an exactly solvable Gaussian (free transverse bosons $X^I$, $I=1,\dots,\perpD$, and free GS fermions $\theta^a$, $a=1,\dots,8$),
\item the kinematic overlap of full string boundaries is imposed exactly, leaving only a local interaction-point prefactor as the nontrivial dynamical input.
\end{itemize}

The main output should be a computable expression for amplitudes in which all bulk integrations are already done analytically.

\section{What is standard vs what is new}
Most structural ingredients are classical:
\begin{itemize}
\item Mandelstam lightcone diagrams and parametrization,
\item Green--Schwarz lightcone free worldsheet fields,
\item interaction-point insertions required by supersymmetry/Lorentz symmetry.
\end{itemize}
The key step here is different in emphasis: discretize only the worldsheet spatial coordinate $\sigma$ so that, at any loop order, each propagator becomes a finite-dimensional Gaussian kernel that is exactly computable. This turns the higher-loop problem into a controlled numerical task:
\begin{equation}
\label{eq:s2-001}
\begin{aligned}
{\cal A}_{h\text{-loop}}
=\int \dd\mu_{\text{moduli}}\;
{\cal G}_{\text{free}}(N,T)\;
{\cal I}_{\text{int}}(N,T).
\end{aligned}
\end{equation}
Here $h$ is the loop order, equivalently the genus of the lightcone worldsheet, $N$ denotes the collective lattice resolution data on all cylinders, $T$ the collective Schwinger lengths, ${\cal G}_{\text{free}}$ the exact Gaussian free-propagator factor, and ${\cal I}_{\text{int}}$ the product of local interaction-point insertions. The explicit loop-twist dependence $\varphi$ is suppressed in this formula only for brevity; later sections restore it explicitly in the propagator kernels and in the loop integration measure.

\section{Literature status}
A first literature pass suggests that the basic interaction-point problem is indeed old, but the discrete-$\sigma$ numerical version is not already sitting on the shelf in the form we need.

First, the lightcone Green--Schwarz construction of string interactions is classical. Green and Schwarz already constructed lightcone vertex operators for superstrings in their early work and then wrote down an off-shell three-string interaction vertex together with the cubic correction to the supercharge in \cite{GreenSchwarz1982Vertices,GreenSchwarz1983Interactions}. Green and Seiberg later emphasized that cubic overlap data alone is not the full story: contact interactions are required in lightcone gauge \cite{GreenSeiberg1988}.

Second, the interaction-point operator itself was recognized as the awkward part of the Green--Schwarz formalism. Berkovits explicitly stresses that lightcone and semi-lightcone Green--Schwarz amplitudes are complicated by non-trivial interaction-point operators, and shows that alternative super-worldsheet/twistor formulations can eliminate them \cite{Berkovits1992N20,Berkovits1993Twistor}.

Third, the continuum Green--Schwarz interaction-point prefactor is known explicitly. In the pp-wave literature, Spradlin and Volovich give the SO$(8)$-covariant octic polynomial $v_{IJ}(\Lambda)$, and Pankiewicz and Stefanski write the full dressed cubic vertex with the bosonic interaction-point operators $K^I,\widetilde K^J$ \cite{SpradlinVolovich2002,PankiewiczStefanski2002}. In flat space, these are the structures one should recover in the appropriate limit.

Fourth, there is a closely related matrix-string line of thought. Dijkgraaf, Verlinde and Verlinde identify perturbative string interactions in the matrix-string framework \cite{DVV1997Matrix}. Dijkgraaf and Motl then relate the Green--Schwarz lightcone interaction Hamiltonian to the twist-field formalism and analyze higher-order contact terms \cite{DijkgraafMotl2003}. Kishimoto, Moriyama and Teraguchi make the relation between matrix-string twist fields and the lightcone three-string vertex even more explicit \cite{Kishimoto2006}. More recently, Ando, Fujii, Kunitomo and Totsuka-Yoshinaka show that collisions of local operators remain a central issue in constructing a consistent lightcone-gauge superstring field theory \cite{Ando2025}.

The conclusion I draw from these papers is the following. The continuum cubic prefactor is not the unknown part; it is already fixed by dynamical supersymmetry. The new step in this note is to rewrite the full problem in a discrete-$\sigma$ language where the propagators are exact Gaussians, the boundary overlap is imposed directly in position space, and the known continuum prefactor is discretized into a local operator at the join. Contact terms at order $g^2$, where $g$ is the string coupling, are still expected, as already emphasized in \cite{GreenSeiberg1988,GreensiteKlinkhamer1988}.

The scope of what is and is not explicit in this note should be stated plainly. The note gives fully explicit finite-$N$ formulas for the free cylinder kernels, the exact site-space overlap constraints, the Fourier/oscillator maps, and the resulting finite-dimensional Gaussian sewing problem. It does \emph{not} attempt to rederive standard continuum lightcone-gauge Lorentz invariance from scratch; that part of the subject is taken as known background and as the continuum target. The main question here is instead whether the discrete-$\sigma$ construction reproduces known lightcone amplitudes numerically, with controlled finite-$N$ diagnostics and continuum extrapolation, in both the bosonic and GS superstring cases. By contrast, several genuinely separate inputs are only identified, not solved in closed form here: the continuum lightcone measure factor $J_{\mathrm{M}}$ if one chooses not to absorb it into $\dd\mu_{\mathrm{lc}}$; the spin-structure and GSO bookkeeping for higher-genus fermion loops; the discrete solution of the dynamical supercharge equations that would fix the exact lattice prefactor coefficients and overall cubic normalizations; and the quartic and higher contact terms required beyond order $g$. Whenever one of these unresolved inputs enters later formulas, I state explicitly below which part is being used and which part is still deferred.

\section{Mandelstam map and lightcone time}
For a fixed lightcone diagram (tree or loop), use Mandelstam's map
\begin{equation}
\label{eq:s4-001}
\rho(z)=\sum_{r=1}^{n}\alpha_r^{\mathrm{M}} \log(z-Z_r),\qquad \sum_{r=1}^n \alpha_r^{\mathrm{M}}=0,\qquad \alpha_r^{\mathrm{M}}=\varepsilon_r^{\mathrm{M}}\,2\al p_r^+,\ \ \varepsilon_r^{\mathrm{M}}=\pm 1.
\end{equation}
Here $z$ is the complex uniformization coordinate on the worldsheet Riemann surface, $Z_r$ are the puncture positions of the $n$ external strings, and $\alpha_r^{\mathrm M}$ are the signed Mandelstam residues. I take $\varepsilon_r^{\mathrm M}=+1$ for incoming strings and $\varepsilon_r^{\mathrm M}=-1$ for outgoing strings, so $\alpha_r^{\mathrm M}>0$ on incoming legs, $\alpha_r^{\mathrm M}<0$ on outgoing legs, and $\alpha_r\equiv |\alpha_r^{\mathrm M}|$ is the positive circumference used in the discrete formulas below.
After Wick rotation to Euclidean worldsheet time, we use the convention $\tau=\Re \rho$ and $\sigma=\Im \rho$.
The Wick rotation is taken as $\tau_{\mathrm{M}}=-\ii\tau$, so the Minkowski weight $e^{\ii S_{\mathrm{M}}}$ becomes the Euclidean weight $e^{-S_{\mathrm{E}}}$ with positive bosonic quadratic form.
External legs are semi-infinite cylinders of circumference $|\alpha_r^{\mathrm{M}}|$.
Internal propagators are finite cylinders labeled by internal edges $e$, with Schwinger lengths $T_e$ given by differences of $\tau$-coordinates between neighboring interaction points. For loop diagrams, one must also keep the relative translation in $\sigma$ used to glue the two ends of a propagator. Thus the propagator data are $(T_e,\varphi_e)$ rather than just $T_e$, where $\varphi_e$ is the twist modulus along the $\sigma$ circle.

In the discrete lattice formulas below I use the positive cylinder circumferences
\begin{equation}
\label{eq:s4-002}
\alpha_r \equiv |\alpha_r^{\mathrm{M}}|,
\end{equation}
and keep the orientation signs separately through factors such as $\epsilon_r=(+1,+1,-1)$ in the canonical one-form. Thus for a cubic join with two incoming legs $1,2$ and one outgoing leg $3$, the signed Mandelstam residues obey $\alpha_1^{\mathrm{M}}+\alpha_2^{\mathrm{M}}+\alpha_3^{\mathrm{M}}=0$, while the positive circumferences satisfy $\alpha_3=\alpha_1+\alpha_2$ and hence $N_3=N_1+N_2$.

For a discrete $\sigma$ lattice, string $r$ has $N_r$ sites with
\begin{equation}
\label{eq:s4-003}
a_r=\frac{\alpha_r}{N_r},\qquad \sigma_n=n\,a_r,\quad n=0,\dots,N_r-1.
\end{equation}
For an internal propagator edge $e$ one uses the same relation, namely $a=\alpha_e/N_e$ if that edge is discretized with the common spacing $a$ and has positive circumference $\alpha_e$.
At a cubic join, $p_3^+=p_1^++p_2^+$ implies
\begin{equation}
\label{eq:s4-004}
N_3=N_1+N_2,
\end{equation}
after choosing a common lattice spacing (or an integer-compatible refinement).
For generic real lightcone momenta there is usually no single finite lattice with exact $\alpha_r=aN_r$ on every leg. The finite-$N$ definition should therefore be understood as a refinement sequence: choose $a_\nu\to 0$ and integers $N_r^{(\nu)}$ such that
\begin{equation}
\label{eq:s4-005}
\alpha_r^{(\nu)}\equiv a_\nu N_r^{(\nu)}\longrightarrow \alpha_r
\end{equation}
while every cubic join obeys the exact integer overlap rule
\begin{equation}
\label{eq:s4-006}
N_3^{(\nu)}=N_1^{(\nu)}+N_2^{(\nu)}.
\end{equation}
In practice one approximates the independent external $\alpha_r$ by rationals with a common denominator and then determines all internal $N_e^{(\nu)}$ from the exact vertex conservation laws. Each finite-$\nu$ computation uses exact site-space concatenation, and the physical amplitude is obtained by extrapolating $\nu\to\infty$.
The note does not attempt a universal convergence-rate theorem for this refinement sequence. In practice one should choose the rational approximants so that each $\alpha_r^{(\nu)}-\alpha_r=O(a_\nu)$; for irrational momentum ratios the rate at which finite-$N$ artifacts disappear can depend on how well the chosen sequence approximates the target circumferences.

The basic propagator building block is shown in Figure~\ref{fig:discrete-cylinder}.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=1.0, every node/.style={font=\small}]
\draw[thick] (0,0) ellipse (2 and 0.55);
\draw[thick] (0,3.8) ellipse (2 and 0.55);
\draw[thick] (-2,0) -- (-2,3.8);
\draw[thick] (2,0) -- (2,3.8);
\foreach \ang in {0,30,...,330} {
  \fill ({2*cos(\ang)},{0.55*sin(\ang)}) circle (1.1pt);
  \fill ({2*cos(\ang)},{3.8 + 0.55*sin(\ang)}) circle (1.1pt);
}
\draw[<->] (2.6,0) -- node[right] {$T$} (2.6,3.8);
\node at (0,4.55) {$N$ sites around $\sigma$};
\node at (0,1.9) {$K_B(T)$};
\node at (0,-0.85) {periodic direction $\sigma$};
\end{tikzpicture}
\caption{A propagator cylinder in the discrete-$\sigma$ scheme. Only the spatial direction is discretized; Euclidean lightcone time $\tau$ remains continuous. The resulting propagator is an exact finite-dimensional Gaussian kernel.}
\label{fig:discrete-cylinder}
\end{figure}

\section{Discrete free boson on a cylinder}
For one transverse coordinate on a cylinder of length $T$ and $N$ sites:
\begin{equation}
\label{eq:s5-001}
S_B=\frac{1}{4\pi\al}\int_0^T\dd\tau\sum_{n=0}^{N-1}
\left[a\,(\partial_\tau X_n)^2+\frac{1}{a}(X_{n+1}-X_n)^2\right],\qquad X_N\equiv X_0.
\end{equation}
Fourier modes
\begin{equation}
\label{eq:s5-002}
X_n(\tau)=\frac{1}{\sqrt{N}}\sum_{k=0}^{N-1}q_k(\tau)e^{2\pi \ii kn/N},
\end{equation}
diagonalize the action with frequencies
\begin{equation}
\label{eq:s5-003}
\omega_k=\frac{2}{a}\sin\left(\frac{\pi k}{N}\right),\qquad k=0,\dots,N-1.
\end{equation}
The spectrum is symmetric under the reality involution: $\omega_{N-k}=\omega_k$.
For $k\neq 0$ (Euclidean harmonic oscillator),
\begin{equation}
\label{eq:s5-004}
K_{B,k}(q_f,q_i;T)=
\left(\frac{\mu\omega_k}{2\pi\sinh(\omega_k T)}\right)^{1/2}
\exp\!\left[
-\frac{\mu\omega_k}{2\sinh(\omega_k T)}
\big((q_f^2+q_i^2)\cosh(\omega_k T)-2q_fq_i\big)
\right],
\end{equation}
with
\begin{equation}
\label{eq:s5-005}
\mu=\frac{a}{2\pi\al}.
\end{equation}
Here $q_i\equiv q_k(0)$ and $q_f\equiv q_k(T)$ are the initial and final values of the $k$th Fourier mode on a single cylinder. Later, in the three-string overlap problem, the symbols $q_m^{(r)}$ denote the corresponding boundary values of the nonzero modes on leg $r$.
This displayed formula is the kernel for one independent \emph{real} oscillator degree of freedom. Equivalently, it applies to the independent half-spectrum or to the real and imaginary parts of a nonzero Fourier mode. If instead one keeps the full complex mode $q_k$ together with the reality condition $q_{N-k}=\bar q_k$, then the pair $(k,N-k)$ contributes
\begin{equation}
\label{eq:s5-006}
K_{B,k}^{\mathrm{cx}}(q_f,q_i;T)=
\frac{\mu\omega_k}{2\pi\sinh(\omega_k T)}
\exp\!\left[
-\frac{\mu\omega_k}{2\sinh(\omega_k T)}
\left(
\bigl(|q_f|^2+|q_i|^2\bigr)\cosh(\omega_k T)
-2\Re(\bar q_f q_i)
\right)
\right],
\end{equation}
with unit power in the prefactor because the complex mode carries two real degrees of freedom. The site-basis Gaussian matrices below avoid this bookkeeping issue by working directly in the full real position space.
For $k=0$ (free particle),
\begin{equation}
\label{eq:s5-007}
K_{B,0}(q_f,q_i;T)=
\left(\frac{\mu}{2\pi T}\right)^{1/2}
\exp\!\left[-\frac{\mu(q_f-q_i)^2}{2T}\right].
\end{equation}
The full bosonic cylinder kernel is the product over modes and transverse directions $i=1,\dots,\perpD$, where $\perpD \equiv D-2$ is the number of transverse coordinates.

For loop propagation one must also include a twist in $\sigma$. If $\varphi\in[0,1)$ denotes the fraction of the circumference by which one end of the cylinder is shifted relative to the other, then
\begin{equation}
\label{eq:s5-008}
X_f(\sigma)=X_i(\sigma+\varphi |\alpha|).
\end{equation}
On the lattice this is implemented by a shift operator $R_N(\varphi)$ acting in $\sigma$ position space. For an exact lattice shift $\varphi N\in \ZZ$,
\begin{equation}
\label{eq:s5-009}
\bigl(R_N(\varphi)X\bigr)_n = X_{n+\varphi N \,\, \mathrm{mod}\,N},
\end{equation}
while for general $\varphi$ one may use a spectral interpolation operator. Introduce centered lattice frequencies
\begin{equation}
\label{eq:s5-010}
\kappa_k=
\begin{cases}
k,& 0\le k\le \lfloor (N-1)/2\rfloor,\\
k-N,& \lfloor (N+1)/2\rfloor\le k\le N-1,
\end{cases}
\end{equation}
so that $\kappa_{N-k}=-\kappa_k$ except for the self-conjugate Nyquist mode when $N$ is even. Let $F$ denote the $N\times N$ unitary discrete Fourier transform matrix with entries
\begin{equation}
\label{eq:s5-011}
F_{kn}=\frac{1}{\sqrt N}e^{2\pi \ii kn/N},
\qquad
k,n=0,\dots,N-1.
\end{equation}
Then
\begin{equation}
\label{eq:s5-012}
R_N(\varphi)=F^\dagger \, \mathrm{diag}\!\left(e^{-2\pi \ii \kappa_k\varphi}\right) F.
\end{equation}
The twisted bosonic propagator is then
\begin{equation}
\label{eq:s5-013}
K_B(X_f,X_i;T,\varphi)=K_B\bigl(X_f,R_N(\varphi)X_i;T,0\bigr),
\end{equation}
so each discrete Fourier mode picks up the phase $e^{-2\pi \ii \kappa_k\varphi}$ in the cross-term. With the DFT convention \eqref{eq:s5-011}, this minus sign is the one that reproduces the literal forward cyclic site permutation \eqref{eq:s5-009} when $\varphi N\in\ZZ$. For odd $N$ this centered prescription preserves the real site subspace. For even $N$ and generic $\varphi$, however, the self-conjugate Nyquist mode makes $R_N(\varphi)$ a complex interpolation kernel rather than a literal real-site permutation. Thus the geometric-shift interpretation is exact when $\varphi N\in\ZZ$; for generic $\varphi$ one should regard $R_N(\varphi)$ as the finite-$N$ spectral interpolation of the continuum $\sigma$ translation.

\section{Discrete free GS fermions on a cylinder}
In lightcone GS gauge, the transverse fermions are free. After Fourier transform in $\sigma$, each mode gives a quadratic Grassmann system. A convenient bookkeeping device is to complexify the eight real GS spinor components and use coherent-state labels $\eta_{k,a}$, $\bar\eta_{k,a}$ with $a=1,\dots,8$. This is only a representation choice, not a physical doubling; the equivalent real Majorana formulation and its Pfaffian appear below. In these variables one can write
\begin{equation}
\label{eq:s6-001}
S_F=\int_0^T\dd\tau\sum_{k,a}\bar\eta_{k,a}(\partial_\tau+\omega_k)\eta_{k,a},
\end{equation}
where $a$ labels GS spinor components (and similarly for right movers). The same lattice frequencies $\omega_k$ appear as in the bosonic sector because the lightcone GS worldsheet theory is free with matched transverse mode spectrum, even though worldsheet supersymmetry is not manifest.
For a closed string there is also an independent right-moving GS sector, which I denote by $\widetilde\eta_{k,\dot a}$ with $\dot a=1,\dots,8$. Its free action and cylinder kernel have exactly the same lattice form as the left-moving sector written here, with the SO$(8)$ spinor representation chosen according to the IIA/IIB convention. If one wishes to write it separately, one simply repeats the displayed formulas of this section with $\eta\to\widetilde\eta$ and $a\to\dot a$. To avoid doubling notation, the formulas below are usually written for one chiral sector; the total closed-string fermionic contribution is obtained by including both sectors, equivalently by taking the product of the two Pfaffians/determinants after sewing.
Hence each nonzero mode has exact kernel
\begin{equation}
\label{eq:s6-002}
K_{F,k}(\bar\eta_f,\eta_i;T)=
\exp\!\left[\bar\eta_f\,e^{-\omega_k T}\eta_i\right],
\end{equation}
up to convention-dependent normalization factors that can be fixed once and for all from vacuum-to-vacuum propagation. This note does not make that overall coherent-state normalization completely explicit, because different but equivalent Berezin-measure/vacuum conventions differ by a mode-independent multiplicative constant. The later sewing formulas use only the Gaussian exponent and the associated overlap matrices, so the omitted overall factor matters only if one wants an absolute normalization before the global vacuum convention has been fixed.
For the zero mode one has $\omega_0=0$ and therefore
\begin{equation}
\label{eq:s6-003}
K_{F,0}(\bar\eta_f,\eta_i;T)=
\exp\!\left[\bar\eta_f\,\eta_i\right],
\end{equation}
independent of $T$. This is the cylinder transport of the GS fermionic zero mode and is the finite-$N$ precursor of the local Grassmann data later organized into $\Lambda^a$.

With an exact lattice shift, or more generally with the spectral interpolation prescription above, the fermionic cross-term acquires the same phase,
\begin{equation}
\label{eq:s6-004}
K_{F,k}(\bar\eta_f,\eta_i;T,\varphi)=
\exp\!\left[\bar\eta_f\,e^{-\omega_k T}e^{-2\pi \ii \kappa_k\varphi}\eta_i\right],
\end{equation}
up to additional sign choices associated with the fermionic spin structure around the loop. Those signs are not written explicitly in this note because doing so requires fixing a higher-genus spin-structure convention and the associated GSO sum. For a fixed spin structure they amount to extra cycle-dependent phases multiplying the fermionic transport around the relevant loops; the present formulas display only the universal Gaussian part common to every such choice.
At tree level there is no independent loop spin-structure sum, but one still must choose whether the left- and right-moving sectors have the same or opposite chirality, i.e. whether one is matching type IIB or type IIA conventions. That tree-level choice is conceptually separate from the genuinely higher-genus spin-structure/GSO bookkeeping deferred later in the note.

So both bosonic and fermionic propagators are exactly computable Gaussians on the discrete cylinder, with dependence on both $T$ and the $\sigma$-twist $\varphi$.

\section{Explicit site-basis Gaussian matrices}
For numerical assembly, it is best to keep each cylinder kernel in the form
\begin{equation}
\label{eq:s7-001}
K_B(X_f,X_i;T,\varphi)=
{\cal N}_B(T)\,
\exp\!\left[
-\frac12 X_f^{\!T}A(T)X_f
-\frac12 X_i^{\!T}A(T)X_i
+X_f^{\!T}B(T,\varphi)X_i
\right].
\end{equation}
Here ${\cal N}_B(T)$ is the product of the one-mode bosonic normalization factors from Section~5, taken over an independent real basis of lattice normal modes (equivalently, over the half-spectrum together with any self-conjugate modes). Let $\mu \equiv a/(2\pi\al)$ be the same single-mode mass parameter introduced above. Using the same unitary DFT matrix $F$, one has
\begin{align}
A(T)&=\mu\,F^\dagger\,
\mathrm{diag}\!\big(\omega_k\coth(\omega_k T)\big)\,F,
\label{eq:s7-A-matrix}\\
B(T,\varphi)&=\mu\,F^\dagger\,
\mathrm{diag}\!\big(e^{-2\pi \ii \kappa_k\varphi}\omega_k\mathrm{csch}(\omega_k T)\big)\,F.
\label{eq:s7-B-matrix}
\end{align}
For the zero mode, use the smooth limits
\begin{equation}
\label{eq:s7-002}
\omega_0\coth(\omega_0 T)\to \frac{1}{T},\qquad
\omega_0\mathrm{csch}(\omega_0 T)\to \frac{1}{T}.
\end{equation}
Hence $A(T)$ is circulant in site space, while $B(T,\varphi)$ is a twisted circulant/interpolation matrix. For exact lattice shifts it is real and circulant up to permutation; for generic $\varphi$ it is the finite-$N$ spectral interpolation kernel described above. In all cases it is diagonalized exactly by the same DFT.
For generic $\varphi$ it is often numerically safest to keep this Fourier-basis representation, where the Euclidean damping factors are manifest mode by mode, and regard the site-space kernel simply as the exact inverse DFT of that diagonal data.

For fermions (coherent states),
\begin{equation}
\label{eq:s7-003}
K_F(\bar\eta_f,\eta_i;T,\varphi)=
{\cal N}_F(T)\,
\exp\!\left[\bar\eta_f^{\!T}U(T,\varphi)\eta_i\right],\qquad
U(T,\varphi)=F^\dagger\mathrm{diag}\!\big(e^{-\omega_k T}e^{-2\pi \ii \kappa_k\varphi}\big)F.
\end{equation}
In the coherent-state normalization implicit in Section~6 one may take ${\cal N}_F(T)=1$; under a different but equivalent choice of Berezin measure and vacuum normalization it changes only by an overall convention-dependent constant, not by a new dynamical function of $(T,\varphi)$.
The $k=0$ entry of $U(T,\varphi)$ is exactly $1$, so the fermionic zero mode propagates without any $T$-dependent damping. The companion diagnostic \texttt{twisted\_cylinder\_check.py} verifies three basic facts numerically: exact lattice twists $\varphi=m/N$ reproduce the literal site permutation to $4\times 10^{-15}$, the cross matrix satisfies $B(T,m/N)=B(T,0)P_m$ to $7\times 10^{-16}$, and on the oscillator sector the real part of the twisted loop-trace quadratic form remains strictly positive on the sampled $(N,T,\varphi)$ grid while its log-determinant matches the closed Fourier-mode formula to $7\times 10^{-13}$. A second helper, \texttt{single\_cylinder\_integrand.py}, then packages these same twisted kernels into the first explicit one-cylinder oscillator trace prototype. On the sampled grid the bosonic one-coordinate factor matches its closed mode-product formula with maximum relative error $2.40\times 10^{-13}$, while the fermionic coherent-state factor matches with maximum relative error $1.22\times 10^{-15}$. This remains a pre-GSO, oscillator-sector building block: it is not yet the physical loop integrand, because the later spin-structure sum, zero-mode factor, and the overall coherent-state/Pfaffian normalization relative to the bosonic determinant have not yet been fixed.

These formulas are the core building blocks for every edge in a higher-loop diagram. At higher genus the independent twist moduli are integrated together with the Schwinger lengths.

Figure~\ref{fig:twisted-cylinder} shows the geometric meaning of the twist modulus in $\sigma$ position space.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=1.0, every node/.style={font=\small}]
\draw[thick] (0,0) ellipse (2 and 0.55);
\draw[thick] (0,3.8) ellipse (2 and 0.55);
\draw[thick] (-2,0) -- (-2,3.8);
\draw[thick] (2,0) -- (2,3.8);
\foreach \ang in {0,45,...,315} {
  \fill[blue] ({2*cos(\ang)},{0.55*sin(\ang)}) circle (1.2pt);
}
\foreach \ang in {35,80,...,350} {
  \fill[green!50!black] ({2*cos(\ang)},{3.8 + 0.55*sin(\ang)}) circle (1.2pt);
}
\draw[->,thick] (2.55,0.3) -- node[right] {$T$} (2.55,3.5);
\draw[->,thick,blue] (0.4,-0.95) arc[start angle=-20,end angle=110,radius=0.9];
\node[blue] at (1.35,-0.85) {$\sigma$};
\draw[->,thick,green!50!black] (0.55,4.55) arc[start angle=5,end angle=135,radius=0.9];
\node[green!50!black] at (1.55,4.7) {$\sigma+\varphi|\alpha|$};
\draw[->,dashed,thick] (0.95,0.48) -- (1.45,4.15);
\node[right] at (1.52,2.4) {$R_N(\varphi)$};
\node at (0,1.9) {$K_B(T,\varphi)$};
\node[blue] at (-1.35,-0.85) {initial sites};
\node[green!50!black] at (-1.35,4.65) {twisted final sites};
\end{tikzpicture}
\caption{Twisted propagator cylinder. The lower circle is glued to the upper circle after a translation by $\varphi|\alpha|$ along the $\sigma$ direction. For exact lattice shifts this is a literal site permutation. More generally, in Fourier space it becomes multiplication by the phase $e^{-2\pi \mathrm{i}\kappa_k\varphi}$ and in site space it is represented by the spectral interpolation operator $R_N(\varphi)$.}
\label{fig:twisted-cylinder}
\end{figure}

\section{Sewing formula for a fixed diagram}
This section states the global sewing formula in the note's semi-discrete formalism: the worldsheet spatial direction $\sigma$ has been discretized, while Euclidean lightcone time $\tau$ and the lightcone moduli $(T_e,\varphi_A)$ remain continuous. Accordingly, the boundary variables $X,\Theta$, the edge kernels $K_e$, and the vertex factors ${\cal V}_I$ below are finite-dimensional lattice objects depending on continuous Schwinger/twist parameters.

For a diagram ${\cal D}$ with internal edges $e$ and cubic vertices $I$:
\begin{equation}
\label{eq:s8-001}
{\cal A}_{\cal D}=
\int\prod_e \dd T_e
\int\prod_A \dd\varphi_A\;
J_{\mathrm{M}}(T,\varphi;\alpha_{\mathrm{ext}})
\int\prod_{\text{internal boundaries}}\dd X\,\dd\Theta\;
\prod_e K_e(X_f,\Theta_f;X_i,\Theta_i;T_e,\varphi_e)\,
\prod_I {\cal V}_I.
\end{equation}
Here ${\cal D}$ means a fixed cubic lightcone skeleton graph together with its external-state assignments and positive circumferences $\alpha_{\mathrm{ext}}$, $A=1,\dots,h$ labels a basis of independent graph cycles, $\varphi_A$ are the corresponding twist moduli, and $\Theta$ collectively denotes the site-level GS boundary fermions on all internal boundaries. Thus if one internal boundary carries site variables $\theta_0,\dots,\theta_{N-1}$, those components form the corresponding block of $\Theta$. The factor $K_e$ is the explicit free cylinder kernel on internal edge $e$, and ${\cal V}_I$ is the local cubic vertex insertion at interaction point $I$.
At this stage ${\cal V}_I$ is abbreviated notation rather than a new independent dynamical ansatz. In the bosonic theory it is defined later as the exact full-boundary overlap delta functional $\delta(C_I{\bf X}_I)$ in Section~9. In the GS superstring, the exact object is the matrix element of the later-defined local operator ${\cal P}_{I,\mathrm{loc}}|V_{\mathrm{kin}}\rangle$ between the three boundary states meeting at $I$; writing that matrix element explicitly requires the bosonic and fermionic overlap conventions introduced only in Sections~11--14. The purpose of the present section is therefore to organize the global sewing and moduli dependence before those local vertex formulas have been spelled out.

For a fixed cubic graph, a label $I$ refers to one specific local join/split event on the worldsheet, namely one interaction region of pair-of-pants type at some interaction time $\tau_I$. The three propagator boundaries adjacent to that event are the three legs meeting at the cubic vertex. The roles of the ingredients in the amplitude formula are therefore logically distinct: each $K_e$ describes free propagation along one cylinder, whereas ${\cal V}_I$ describes the local rule for gluing the three adjacent boundaries at the join. In the bosonic theory that local rule is exactly the position-space overlap constraint written later as $\delta(C_I{\bf X}_I)$. In the GS theory it is the corresponding bosonic-plus-fermionic kinematic overlap together with the local interaction-point prefactor. The only reason Section~8 does not yet display the full GS formula is that the coherent-state conventions and local prefactor operators have not yet been introduced at this point in the note.
Equivalently, if one freezes the rest of the diagram and looks only at the three boundary slices adjacent to $\tau_I$, then nothing propagates at the cubic vertex itself. The local factor ${\cal V}_I$ is supported only on triples of boundary data that satisfy the exact sewing rule at that join, and in the GS theory it then multiplies that sewing constraint by an additional operator localized near the interaction region. The propagation is entirely on the edges; the interaction is entirely local at the join.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.85, every node/.style={font=\small}]
\node[draw,rounded corners,align=center,text width=3.2cm,inner sep=5pt] (edge) at (-4.5,1.0)
{\textbf{Edge factor $K_e$}\\
free cylinder\\
moduli $(T_e,\varphi_e)$};
\node[draw,rounded corners,align=center,text width=3.5cm,inner sep=5pt] (vertex) at (0,1.0)
{\textbf{Local vertex ${\cal V}_I$}\\
join at $\tau_I$\\
exact sewing\\
+ GS prefactor};
\node[draw,rounded corners,align=center,text width=3.2cm,inner sep=5pt] (source) at (4.5,1.0)
{\textbf{Auxiliary sources}\\
${\bf J}_B,{\bf J}_F,\bar{\bf J}_F$\\
generate insertions\\
then set to zero};
\node at (-2.25,1.0) {$\times$};
\node at (2.25,1.0) {$\times$};
\node[draw,rounded corners,align=center,text width=8.8cm,inner sep=5pt] (assemble) at (0,-0.95)
{Amplitude assembly: multiply edge kernels and local vertex factors, then integrate over the internal boundary data. No propagation occurs at $I$ itself.};
\node[align=center] at (0,-2.15)
{The local interaction lives in ${\cal V}_I$.\\
The sources are only bookkeeping devices for derivative insertions.};
\draw[->,thick] (0,0.35) -- (0,-0.35);
\end{tikzpicture}
\caption{Logical roles of the objects in Section~8. Edge kernels describe free propagation. A cubic vertex $I$ is not an additional propagator; it is the local joining/splitting rule on the three adjacent boundary slices. The source variables are optional tools for representing local insertions by differentiation.}
\label{fig:sewing-roles}
\end{figure}

Choose a basis of graph cycles $A=1,\dots,h$. Then only $h$ twists are independent, and the twist carried by an individual internal edge is
\begin{equation}
\label{eq:s8-002}
\varphi_e=\sum_{A=1}^{h}\epsilon_{eA}\varphi_A
\qquad
(\mathrm{mod}\,1),
\end{equation}
with incidence numbers $\epsilon_{eA}\in\{0,\pm1\}$ determined by how edge $e$ winds around the chosen homology basis: $\epsilon_{eA}=+1$ if $e$ lies on cycle $A$ with matching orientation, $\epsilon_{eA}=-1$ if the orientation is opposite, and $\epsilon_{eA}=0$ if $e$ does not lie on that cycle. The vertex overlap constrains all other relative $\sigma$ shifts.
Figure~\ref{fig:cycle-twists} shows the bookkeeping in a representative genus-one case: once an oriented cycle basis is chosen, each edge twist is simply the signed pullback of the cycle twist to that edge.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\node[font=\bfseries] at (0,2.8) {Cycle basis versus edge twists};
\fill (-2.7,0) circle (1.6pt);
\fill (2.7,0) circle (1.6pt);
\draw[thick] (-4.5,0) -- (-2.7,0);
\draw[thick] (2.7,0) -- (4.5,0);
\draw[thick] (-2.7,0) .. controls (-0.9,1.45) and (0.9,1.45) .. (2.7,0);
\draw[thick] (-2.7,0) .. controls (-0.9,-1.45) and (0.9,-1.45) .. (2.7,0);
\node[left] at (-4.6,0) {external leg};
\node[right] at (4.6,0) {external leg};
\node[fill=white,inner sep=1pt] at (0,1.33) {upper internal edge $e_+$};
\node[fill=white,inner sep=1pt] at (0,-1.33) {lower internal edge $e_-$};

\draw[->,thick,blue] (-1.9,0.45) .. controls (-0.4,1.8) and (0.4,1.8) .. (1.9,0.45);
\node[blue,fill=white,inner sep=1pt] at (0,2.3) {chosen cycle $A$};
\draw[->,thick] (-1.7,0.34) .. controls (-0.5,1.05) and (0.5,1.05) .. (1.7,0.34);
\draw[->,thick] (1.7,-0.34) .. controls (0.5,-1.05) and (-0.5,-1.05) .. (-1.7,-0.34);
\node[above,fill=white,inner sep=1pt] at (0,0.92) {$\epsilon_{e_+A}=+1$};
\node[below,fill=white,inner sep=1pt] at (0,-0.92) {$\epsilon_{e_-A}=-1$};

\node[draw,rounded corners,align=center,inner sep=5pt] at (0,-2.95)
{in this orientation convention:\\
$\varphi_{e_+}=+\varphi_A,\qquad \varphi_{e_-}=-\varphi_A \pmod{1}$};
\end{tikzpicture}
\caption{Example of the twist bookkeeping behind $\varphi_e=\sum_A \epsilon_{eA}\varphi_A$. After choosing an oriented basis of graph cycles, each internal edge inherits the corresponding cycle twist with a sign fixed by its relative orientation. Higher genus works the same way, with one independent twist modulus for each basis cycle.}
\label{fig:cycle-twists}
\end{figure}

All nonlocal dependence on worldsheet geometry/moduli sits in $K_e$ through $T_e$, $\varphi_e$, and $N_e$. Since each $K_e$ is explicit, the unresolved ingredient is the local vertex factor ${\cal V}_I$.

For a fixed cubic lightcone graph, the Schwinger lengths $T_e$ and independent twists $\varphi_A$ are already the natural coordinates on the corresponding lightcone cell of moduli space. Thus the native lightcone-gauge integration is directly over
\[
\prod_e \dd T_e \prod_A \dd\varphi_A.
\]
To allow for any continuum lightcone-measure density that one may wish to keep separate from the discrete Gaussian sewing, I write the full cell measure as
\begin{equation}
\label{eq:s8-003}
\dd\mu_{\mathrm{lc}}
=
J_{\mathrm{M}}(T,\varphi;\alpha_{\mathrm{ext}})
\prod_e \dd T_e
\prod_A \dd\varphi_A.
\end{equation}
Here $J_{\mathrm{M}}$ is \emph{not} meant to say that $(T,\varphi)$ are the wrong moduli variables. Rather, it is a scalar density on this lightcone-moduli chart that may be kept explicit or absorbed into the definition of $\dd\mu_{\mathrm{lc}}$. In conventions where the Mandelstam/lightcone Feynman rules are written directly in the Schwinger-twist variables, one simply sets $J_{\mathrm{M}}=1$. If instead one wishes to factor off a separate continuum Mandelstam measure factor, $J_{\mathrm{M}}$ denotes that leftover density. At tree level this is the same object that appears when one rewrites the interaction-time measure in Koba--Nielsen variables; at loop level it is the analogous lightcone density on the Schwinger-twist cell. The finite-dimensional discrete sewing below does not determine this continuum factor and simply multiplies it if it is kept explicit.
No independent derivation of $J_{\mathrm{M}}$ is attempted in this note. Thus the formulas below are completely explicit only after one either adopts the convention $J_{\mathrm{M}}=1$ as part of the lightcone Feynman rules, or imports the desired continuum expression for this density from a separate Mandelstam-measure analysis.

External states are inserted as boundary wavefunctionals $\Psi_r[X_{\mathrm{ext}}^{(r)},\Theta_{\mathrm{ext}}^{(r)}]$ on the semi-infinite external cylinders. Equivalently, one may attach cylinders of finite length $T_{\mathrm{ext}}$ and then take $T_{\mathrm{ext}}\to\infty$ to project onto the chosen external Fock states. At tree level there is no independent twist integral, so closed-string level matching of the external states must be imposed by this external-state projection. At loop level the independent twist integrals $\varphi_A$ implement the periodic projection automatically in the internal channels.
The note does not write explicit formulas for the external wavefunctionals $\Psi_r$ because they depend on the chosen external states. Once those states are fixed, however, they are standard boundary insertions and do not introduce any new ambiguity into the internal sewing rules.

For a genus-$h$ $n$-point cubic lightcone skeleton, one has
\begin{equation}
\label{eq:s8-004}
E=3h+n-3,\qquad V=2h+n-2,
\end{equation}
where $E$ is the number of internal propagator edges and $V$ is the number of cubic vertices,
so the dimensionality growth at high loop order is pushed into a finite set of Schwinger/moduli integrations, while the worldsheet field integrals remain Gaussian and algorithmic.

To evaluate these Gaussian integrals uniformly, choose a fixed global ordering of all internal boundary components. Then ${\bf X}$ denotes the single long column vector of all internal bosonic boundary values in that ordering, while ${\bf \Theta}$ and $\bar{\bf \Theta}$ denote the corresponding fermionic coherent-state variables. Concretely, one may think of ${\bf X}$ as the concatenation of boundary blocks such as $(X_{(e_1,\mathrm i)},X_{(e_1,\mathrm f)},X_{(e_2,\mathrm i)},X_{(e_2,\mathrm f)},\dots)^T$, where each block is itself the ordered list of sites on one boundary circle. The source vectors ${\bf J}_B$, ${\bf J}_F$, and $\bar{\bf J}_F$ are \emph{auxiliary} generating variables coupled to those same ordered boundary components. Physically, after the Gaussian is completed, their bosonic values become affine functions of the external transverse momenta and, at loop level, of the independent loop momenta; the fermionic sources similarly encode the external or surviving zero-mode Grassmann data. They are not additional worldsheet fields, not new moduli, and not new interaction data. If one is merely sewing free kernels with no local derivative insertions, one may set all of them to zero from the start. They are introduced only because differentiating with respect to them brings down the corresponding boundary variables when local interaction-point operators are evaluated.

After collecting all edge kernels, one gets a global Gaussian in all internal boundary variables:
\begin{equation}
\label{eq:s8-005}
\exp\!\left[
-\frac12 {\bf X}^T {\cal M}_B(T,\varphi)\,{\bf X}
+{\bf J}_B^T{\bf X}
\right]
\times
\exp\!\left[
-\bar{\bf \Theta}^{\,T}{\cal M}_F(T,\varphi)\,{\bf \Theta}
+\bar{\bf J}_F^T{\bf \Theta}
+\bar{\bf \Theta}^{\,T}{\bf J}_F
\right].
\end{equation}
The matrices ${\cal M}_B(T,\varphi)$ and ${\cal M}_F(T,\varphi)$ are assembled by embedding the quadratic forms of the individual edge kernels into this global ordering and summing their contributions. Equivalently, each internal cylinder contributes its own site-basis $A/B$ or $U$ blocks on the pair of boundary components belonging to that edge, and the global matrices are the resulting block sums. The local overlap constraints carried by ${\cal V}_I$ are separate vertex factors unless one chooses to exponentiate them with Lagrange multipliers.
Gaussian integration is exact:
\begin{align}
\int \dd^nX\,e^{-\frac12 X^TMX+J^TX}
&=(2\pi)^{n/2}(\det M)^{-1/2}e^{\frac12 J^TM^{-1}J},
\label{eq:s8-bosonic-gaussian-integral}\\
\int \dd\bar\Theta\,\dd\Theta\,
e^{-\bar\Theta M\Theta+\bar J\Theta+\bar\Theta J}
&=\det(M)\,e^{\bar J M^{-1}J}.
\label{eq:s8-fermionic-gaussian-integral}
\end{align}
Here ${\cal M}_F$ is defined precisely as the fermionic matrix appearing with this conventional minus sign in the exponent.
Concretely, differentiating with respect to a bosonic source component brings down the matching boundary field $X_b^M$, while differentiating with respect to a fermionic source component brings down the corresponding Grassmann boundary variable. After all desired local insertions have been generated, the sources are set back to zero.
For real GS fermions one may equivalently pass to the doubled antisymmetric Majorana matrix
\begin{equation}
\label{eq:s8-006}
\mathbb A_F=
\begin{pmatrix}
0 & -M^T\\
M & 0
\end{pmatrix},
\qquad
\mathrm{Pf}(\mathbb A_F)=\det(M).
\end{equation}
So each diagram integrand can be assembled exactly as bosonic determinants together with either fermionic determinants in coherent-state variables or fermionic Pfaffians in the equivalent real Majorana form.
For a complete sewn diagram one must also choose a fixed global ordering of internal boundary labels and use the matching Berezin measure $\prod_b \dd\bar\Theta_b\,\dd\Theta_b$. Together with the local leg/site/SO$(8)$ ordering specified later, this fixes the overall sign of the fermionic determinant/Pfaffian unambiguously.

The same Gaussian also gives an explicit source representation for interaction-point derivative insertions. Write
\begin{equation}
\label{eq:s8-007}
Z_B[{\bf J}_B]
=
\int \dd{\bf X}\,
\exp\!\left[
-\frac12 {\bf X}^T{\cal M}_B{\bf X}
+{\bf J}_B^T{\bf X}
\right]
\propto
\exp\!\left[\frac12 {\bf J}_B^T{\cal M}_B^{-1}{\bf J}_B\right].
\end{equation}
The dependence on the moduli $(T,\varphi)$ is implicit here through ${\cal M}_B(T,\varphi)$.
This source representation is therefore not a second definition of the cubic interaction. It is only a computational rewrite of local field insertions acting on the already-sewn Gaussian. The actual local interaction still sits in ${\cal V}_I$; the sources merely provide a convenient way to evaluate it once the Gaussian kernels have been assembled.
For each cubic vertex $I$, specialize first to the canonical join $1+2\to 3$ and define the two unfolded-strip representatives of the local closed-string interaction region by
\begin{equation}
\label{eq:s8-008}
X_{I_+}\equiv X_0^{(1)}=X_0^{(3)},
\qquad
X_{I_-}\equiv X_0^{(2)}=X_{N_1}^{(3)}.
\end{equation}
Define the one-sided nearest-neighbor differences on the two arcs by
\begin{equation}
\label{eq:s8-009}
\nabla_+X_{I_+}^{(1)}\equiv X_1^{(1)}-X_{I_+},
\qquad
\nabla_-X_{I_-}^{(2)}\equiv X_{I_-}-X_{N_2-1}^{(2)},
\end{equation}
and likewise on leg $3$. In this convention the unsuperscripted $\nabla_-$ is already the backward nearest-neighbor difference on the $I_-$ arc. Then let $d_I$ and $\widetilde d_I$ be the corresponding row vectors in the global boundary-variable space,
\begin{equation}
\label{eq:s8-010}
d_I^T{\bf X}=\bigl(\nabla_+X_{I_+}^{(1)}\bigr)=\bigl(\nabla_+X_{I_+}^{(3)}\bigr),
\qquad
\widetilde d_I^T{\bf X}=\bigl(\nabla_-X_{I_-}^{(2)}\bigr)=\bigl(\nabla_-X_{I_-}^{(3)}\bigr).
\end{equation}
Figure~\ref{fig:source-stencil} summarizes both the local strip geometry and the way these one-sided differences are embedded as sparse row vectors acting on the global boundary variable ${\bf X}$.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\node[font=\bfseries] at (-3.3,2.2) {Local arc data};
\draw[thick] (-5.4,0.9) -- (-1.1,0.9);
\fill[red] (-4.35,0.9) circle (1.5pt);
\fill[red] (-2.25,0.9) circle (1.5pt);
\node[red!70!black,above] at (-4.35,0.98) {$I_+$};
\node[red!70!black,above] at (-2.25,0.98) {$I_-$};
\fill[blue] (-3.55,0.9) circle (1.3pt);
\fill[green!50!black] (-3.0,0.9) circle (1.3pt);
\draw[->,thick,blue] (-4.2,0.22) -- (-3.6,0.83);
\draw[->,thick,green!50!black] (-2.35,0.22) -- (-2.95,0.83);
\node[blue,below] at (-3.95,0.12) {$d_I^T{\bf X}$};
\node[green!50!black,below] at (-2.55,0.12) {$\widetilde d_I^T{\bf X}$};
\node[align=center] at (-3.95,1.48) {$X_{I_+}\to X_1^{(1)}$};
\node[align=center] at (-2.55,1.48) {$X_{N_2-1}^{(2)}\to X_{I_-}$};

\draw[densely dashed] (0, -0.9) -- (0, 2.8);

\node[font=\bfseries] at (3.25,2.2) {Embedding in ${\bf X}$};
\node[draw,rounded corners,align=left,inner sep=5pt] at (3.2,1.55)
{$ {\bf X}=(\cdots, X_{I_+}, X_1^{(1)}, \cdots, X_{N_2-1}^{(2)}, X_{I_-}, \cdots)^T $};
\node[draw,rounded corners,align=left,inner sep=5pt,blue] at (3.2,0.45)
{$ d_I^T=(\cdots,-1,+1,\cdots,0,0,\cdots)$};
\node[draw,rounded corners,align=left,inner sep=5pt,green!50!black] at (3.2,-0.65)
{$ \widetilde d_I^T=(\cdots,0,0,\cdots,-1,+1,\cdots)$};
\end{tikzpicture}
\caption{Local one-sided interaction-point differences and their embedding into the global boundary vector ${\bf X}$. The row vectors $d_I$ and $\widetilde d_I$ are sparse selectors that extract the two nearest-neighbor differences on the $I_+$ and $I_-$ arcs of the unfolded closed-string join.}
\label{fig:source-stencil}
\end{figure}

At this point there are two distinct claims one should not conflate. First, one chooses a lattice candidate for the bosonic local interaction-point operator. In the present note the minimal candidate is the one-sided nearest-neighbor difference on each arc, with the continuum-motivated $a^{-1/2}$ scaling discussed later in Section~14. Second, once such a \emph{linear} local lattice operator has been chosen, it may be represented exactly inside the Gaussian generating functional by source derivatives. The following formulas describe only this second, generating-functional step; they do not by themselves prove that the nearest-neighbor stencil is already the unique or final physical Green--Schwarz interaction-point operator.
Then the bosonic interaction-point operators act on the generating functional as
\begin{equation}
\label{eq:s8-011}
K_{I,\mathrm{lat}}^I
=
a^{-1/2}c_K\,d_I^T\frac{\partial}{\partial {\bf J}_B^I},
\qquad
\widetilde K_{I,\mathrm{lat}}^J
=
a^{-1/2}\widetilde c_K\,\widetilde d_I^T\frac{\partial}{\partial {\bf J}_B^J},
\end{equation}
Here $I,J=1,\dots,\perpD$ are transverse vector indices, unrelated to the vertex label in the subscript and unrelated to the lattice site count $N$. The source ${\bf J}_B^I$ denotes the component coupled to the $I$th transverse coordinate, and $c_K,\widetilde c_K$ are local normalization constants fixed later by the interaction-point analysis. In particular, the formula above should be read as the exact source-representation of the \emph{chosen} linear lattice candidate operator, not as an independent derivation of its physical correctness.
Therefore
\begin{equation}
\label{eq:s8-012}
\begin{aligned}
K_{I,\mathrm{lat}}^I \widetilde K_{I,\mathrm{lat}}^J Z_B
=
a^{-1}c_K\widetilde c_K
\Big[
\bigl(d_I^T{\cal M}_B^{-1}{\bf J}_B^I\bigr)
\bigl(\widetilde d_I^T{\cal M}_B^{-1}{\bf J}_B^J\bigr)
\,+\,
\delta^{IJ} d_I^T{\cal M}_B^{-1}\widetilde d_I
\Big]Z_B.
\end{aligned}
\end{equation}
This is the mechanism by which the local prefactor becomes a polynomial in external and loop momenta after Gaussian integration: the completed source ${\bf J}_B$ is affine in those momenta, and the derivative insertions evaluate it at the interaction points.

\section{Discrete cubic overlap vertex}
The correct discrete analogue of Mandelstam joining/splitting is a full-boundary overlap, not continuity at a single site. At an interaction time $\tau=\tau_I$, strings $1$ and $2$ join into string $3$ with
\begin{equation}
\label{eq:s9-001}
N_3=N_1+N_2.
\end{equation}
Write the boundary data as
\begin{equation}
\label{eq:s9-002}
X^{(r)}=
\begin{pmatrix}
X^{(r)}_0\\
X^{(r)}_1\\
\vdots\\
X^{(r)}_{N_r-1}
\end{pmatrix},
\qquad
r=1,2,3.
\end{equation}
Then the bosonic overlap is
\begin{align}
X^{(3)}_n&=X^{(1)}_n,\qquad n=0,\dots,N_1-1,
\label{eq:s9-overlap-first-arc}\\
X^{(3)}_{N_1+m}&=X^{(2)}_m,\qquad m=0,\dots,N_2-1.
\label{eq:s9-overlap-second-arc}
\end{align}
Equivalently, define the embedding matrices
\begin{equation}
\label{eq:s9-003}
P_1\in \RR^{N_3\times N_1},
\qquad
P_2\in \RR^{N_3\times N_2},
\end{equation}
with
\begin{equation}
\label{eq:s9-004}
(P_1)_{nm}=\delta_{n,m},
\qquad
(P_2)_{nm}=\delta_{n,N_1+m},
\end{equation}
so that
\begin{equation}
\label{eq:s9-005}
X^{(3)}=P_1X^{(1)}+P_2X^{(2)}.
\end{equation}
The bosonic cubic vertex is then
\begin{equation}
\label{eq:s9-006}
{\cal V}_I^{(B)}=\delta(C_I{\bf X}_I),
\qquad
{\bf X}_I=
\begin{pmatrix}
X^{(1)}\\
X^{(2)}\\
X^{(3)}
\end{pmatrix},
\qquad
C_I=
\begin{pmatrix}
P_1 & P_2 & -\mathbb I_{N_3}
\end{pmatrix},
\end{equation}
where $C_I$ is an $N_3\times (N_1+N_2+N_3)$ matrix, and $\mathbb I_{N_3}$ denotes the $N_3\times N_3$ identity matrix. The symbol ${\bf X}_I$ here is the \emph{local} stacked boundary data for the three legs meeting at the single cubic vertex $I$; it is distinct from the \emph{global} vector ${\bf X}$ introduced in Section~8, which collects every internal boundary component in the full sewn diagram. This is the discrete version of the standard Mandelstam overlap condition; the subscript $I$ on ${\cal V}_I$, ${\bf X}_I$, and $C_I$ labels the interaction vertex and is unrelated to the transverse SO$(8)$ vector index $I$ used later in the GS prefactor.
Crucially, this overlap is imposed in $\sigma$ position space. One does \emph{not} identify momentum modes directly across the three legs. The mode-space description is obtained only after this exact position-space sewing constraint has been enforced.

The overlap acts on pointwise field values around the cut circles. In the unfolded closed-string strip there are two local representatives of the interaction region,
\begin{equation}
\label{eq:s9-007}
X_{I_+}\equiv X_0^{(1)}=X_0^{(3)},
\qquad
X_{I_-}\equiv X_0^{(2)}=X_{N_1}^{(3)},
\end{equation}
namely the two ends of the cut on the outgoing strip. These local data are not the center-of-mass zero modes
\begin{equation}
\label{eq:s9-008}
x_{\mathrm{cm}}^{(r)}\equiv \frac{1}{N_r}\sum_{n=0}^{N_r-1}X_n^{(r)}.
\end{equation}
Instead, the position-space overlap implies the weighted relation
\begin{equation}
\label{eq:s9-009}
N_3 x_{\mathrm{cm}}^{(3)} = N_1 x_{\mathrm{cm}}^{(1)} + N_2 x_{\mathrm{cm}}^{(2)},
\end{equation}
or equivalently $\alpha_3 x_{\mathrm{cm}}^{(3)}=\alpha_1 x_{\mathrm{cm}}^{(1)}+\alpha_2 x_{\mathrm{cm}}^{(2)}$ for a common lattice spacing. Thus the local strip data $(X_{I_+},X_{I_-})$ and the Fourier zero mode $x_{\mathrm{cm}}$ must be kept conceptually distinct.

Figure~\ref{fig:boundary-overlap-join} illustrates the cubic Mandelstam diagram and the corresponding $\sigma$-space boundary concatenation.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\draw[thick] (-3.2,1.6) -- (3.2,1.6) -- (3.2,4.4) -- (-3.2,4.4) -- cycle;
\draw[thick,blue] (-3.2,-2.0) -- (-3.2,1.6) -- (-0.35,1.6);
\draw[thick,blue] (-3.2,-2.0) -- (-0.35,-2.0) -- (-0.35,1.6);
\draw[thick,green!60!black] (3.2,-2.0) -- (3.2,1.6) -- (0.35,1.6);
\draw[thick,green!60!black] (3.2,-2.0) -- (0.35,-2.0) -- (0.35,1.6);
\draw[thick] (-0.35,1.6) -- (0.35,1.6);
\fill[red] (-0.35,1.6) circle (1.6pt);
\fill[red] (0.35,1.6) circle (1.6pt);
\node[red!70!black,above left] at (-0.35,1.6) {$I_+$};
\node[red!70!black,above right] at (0.35,1.6) {$I_-$};
\draw[dashed] (-3.8,1.6) -- (3.8,1.6);
\node[left] at (-3.9,1.6) {$\tau=\tau_I$};
\draw[->] (-3.9,-2.3) -- (-3.9,4.6);
\node[left] at (-3.9,4.75) {$\tau$};
\draw[->] (-3.4,-2.45) -- (3.5,-2.45);
\node[below] at (3.55,-2.45) {$\sigma$};

\foreach \x in {-2.8,-2.2,-1.6,-1.0,-0.5} {
  \fill[blue] (\x,0.2) circle (1.1pt);
  \fill[blue] (\x,2.45) circle (1.1pt);
}
\foreach \x in {0.5,1.0,1.6,2.2,2.8} {
  \fill[green!60!black] (\x,0.2) circle (1.1pt);
  \fill[green!60!black] (\x,2.45) circle (1.1pt);
}

\draw[dashed,->,blue] (-1.8,0.45) -- (-1.8,2.15);
\draw[dashed,->,green!60!black] (1.8,0.45) -- (1.8,2.15);

\node[blue] at (-1.8,-0.55) {$N_1$ sites};
\node[green!60!black] at (1.8,-0.55) {$N_2$ sites};
\node[fill=white,inner sep=1pt] at (0,3.1) {$N_3=N_1+N_2$ sites};
\node[align=center] at (0,5.45) {ordered union of the lower $\sigma$-sites\\ forms the upper boundary data};
\node[below,fill=white,inner sep=1pt] at (0,0.7) {interaction-region cut ends};
\end{tikzpicture}
\caption{Cubic Mandelstam diagram in lightcone $(\tau,\sigma)$ coordinates. The two incoming strips join at the interaction time $\tau_I$ to form a single outgoing strip. Dots denote discretized $\sigma$-sites on constant-$\tau$ slices. The upper slice is the ordered concatenation of the lower left and lower right slices, so the position-space overlap is $X^{(3)}=(P_1X^{(1)}+P_2X^{(2)})$, and similarly for the kinematic fermionic overlap. The red points $I_+$ and $I_-$ are the two strip representatives of the closed-string interaction region in the unfolded picture.}
\label{fig:boundary-overlap-join}
\end{figure}

From here on, the main target is the closed string. Figure~\ref{fig:boundary-overlap-join} should therefore be read as the unfolded representation of a cut closed-string pair of pants: each actual constant-$\tau$ slice is a circle, cut open and laid out as an interval so that the $\sigma$-site concatenation is explicit. In this unfolded picture the single closed-string interaction region appears as the pair of strip endpoints $I_+$ and $I_-$ at the two ends of the cut on the outgoing strip. They are not two different continuum interaction points; they are the two interval representatives of the same closed-string branch point after the circle has been cut open. The holomorphic interaction-point operator $K$ is attached to the $I_+$ arc, while the antiholomorphic operator $\widetilde K$ is attached to the $I_-$ arc. For brevity I often denote the pair by a single vertex label $I$. The open-string version is the same site-space construction with only one chiral sector.
The finite-$a$ working convention of this note is therefore \emph{not} to collapse the join to one distinguished lattice site. Instead, the exact site-space overlap remains the simple ordered concatenation of boundary data, while the local interaction is treated as a resolved bond-centered region supported on the pair $(I_+,I_-)$ and the adjacent one-sided arc data. In particular, $X_{I_+}$ and $X_{I_-}$ are kept distinct at finite lattice spacing, and their difference is part of the local join data rather than an error to be removed by hand. The price is that the precise finite-$a$ prefactor and counterterm structure must be fixed dynamically; the benefit is that the exact sewing rule stays transparent and no ad hoc extra lattice point has to be introduced at the branch point.

For the off-shell cubic vertex and its higher-loop sewing, however, I do \emph{not} impose level matching a priori on each internal leg. The $\sigma$-space overlap treats all Fourier modes uniformly, and the split into left- and right-movers is recovered only after Fourier transform by separating positive and negative mode numbers (with the self-conjugate middle mode when $N$ is even). Level matching is imposed only when projecting onto external on-shell closed-string states or when comparing with physical S-matrix elements; at tree level this projection is inserted explicitly on the external legs, while at loop level it is enforced in internal channels by the twist integrations.

If one works directly with GS boundary fermions, the kinematic fermionic overlap is organized by the same concatenation map:
\begin{equation}
\label{eq:s9-010}
\theta^{(3)} = P_1 \theta^{(1)} + P_2 \theta^{(2)}
\end{equation}
in $\sigma$ position space, with the same orientation conventions as for the bosons. In particular, at the interaction point itself one identifies
\begin{equation}
\label{eq:s9-011}
\theta_{I_+}^a\equiv \theta_0^{(1)a}=\theta_0^{(3)a},
\qquad
\theta_{I_-}^a\equiv \theta_0^{(2)a}=\theta_{N_1}^{(3)a},
\end{equation}
namely the two strip representatives of the local closed-string interaction region. These variables are not the average Grassmann modes on the legs. So there are not three independent endpoint spinors in the local vertex; rather, in the unfolded closed-string strip one has the pair $(\theta_{I_+},\theta_{I_-})$ together with whatever independent fermionic zero-mode or conjugate Grassmann variable remains after the full overlap constraints are solved.

\section{Position basis versus Fourier basis versus oscillators}
The cubic overlap is imposed on site values $X_n^{(r)}$ and $\theta_n^{(r)}$ in $\sigma$ position space. Comparison with conventional lightcone three-string amplitudes is obtained in two steps: first transform to nonzero discrete Fourier modes, and only then to harmonic-oscillator creation/annihilation operators.

For bosons on leg $r$ with $N_r$ lattice sites, separate center-of-mass and oscillator parts:
\begin{equation}
\label{eq:s10-001}
X_n^{(r)} = x_{\mathrm{cm}}^{(r)} + X_n^{\prime(r)},
\qquad
P_n^{(r)} = \frac{p_\perp^{(r)}}{N_r} + P_n^{\prime(r)},
\qquad
\sum_{n=0}^{N_r-1}X_n^{\prime(r)}=\sum_{n=0}^{N_r-1}P_n^{\prime(r)}=0.
\end{equation}
Here the site-basis canonical algebra is
\begin{equation}
\label{eq:s10-002}
[X_n^{(r)},P_m^{(s)}]=\ii\,\delta^{rs}\delta_{nm},
\qquad
p_\perp^{(r)}\equiv \sum_{n=0}^{N_r-1}P_n^{(r)},
\end{equation}
with all other site-basis commutators vanishing.
Then expand the zero-sum parts as
\begin{equation}
\label{eq:s10-003}
X_n^{\prime(r)} = \frac{1}{\sqrt{N_r}}\sum_{m=1}^{N_r-1} q_m^{(r)} e^{2\pi \ii mn/N_r},
\qquad
P_n^{\prime(r)} = \frac{1}{\sqrt{N_r}}\sum_{m=1}^{N_r-1} \pi_m^{(r)} e^{2\pi \ii mn/N_r}.
\end{equation}
The inverse transform is
\begin{equation}
\label{eq:s10-004}
x_{\mathrm{cm}}^{(r)} = \frac{1}{N_r}\sum_{n=0}^{N_r-1} X_n^{(r)},
\qquad
q_m^{(r)} = \frac{1}{\sqrt{N_r}}\sum_{n=0}^{N_r-1} X_n^{(r)} e^{-2\pi \ii mn/N_r},
\end{equation}
and similarly
\begin{equation}
\label{eq:s10-005}
p_\perp^{(r)} = \sum_{n=0}^{N_r-1} P_n^{(r)},
\qquad
\pi_m^{(r)} = \frac{1}{\sqrt{N_r}}\sum_{n=0}^{N_r-1} P_n^{(r)} e^{-2\pi \ii mn/N_r}.
\end{equation}
For real fields one has
\begin{equation}
\label{eq:s10-006}
q_{N_r-m}^{(r)} = \bigl(q_m^{(r)}\bigr)^*,
\qquad
\pi_{N_r-m}^{(r)} = \bigl(\pi_m^{(r)}\bigr)^*.
\end{equation}

It is convenient to package the nonzero Fourier modes into the rectangular DFT matrix
\begin{equation}
\label{eq:s10-007}
(\widehat F_r)_{mn} = \frac{1}{\sqrt{N_r}} e^{-2\pi \ii mn/N_r},
\qquad
m=1,\dots,N_r-1,\quad n=0,\dots,N_r-1,
\end{equation}
where the hat indicates that the $m=0$ zero-mode row of the full $N_r\times N_r$ DFT has been removed. Also ${\bf 1}_{N_r}$ denotes the $N_r$-component column vector of ones, not an identity matrix; with these conventions
\begin{equation}
\label{eq:s10-008}
X^{(r)} = x_{\mathrm{cm}}^{(r)}{\bf 1}_{N_r} + \widehat F_r^\dagger q^{(r)},
\qquad
P^{(r)} = \frac{p_\perp^{(r)}}{N_r}{\bf 1}_{N_r} + \widehat F_r^\dagger \pi^{(r)}.
\end{equation}

The full-boundary overlap implies the weighted center-of-mass relation
\begin{equation}
\label{eq:s10-009}
N_3 x_{\mathrm{cm}}^{(3)} = N_1 x_{\mathrm{cm}}^{(1)} + N_2 x_{\mathrm{cm}}^{(2)},
\end{equation}
and the oscillator sector obeys an \emph{affine} rather than homogeneous relation,
\begin{equation}
\label{eq:s10-010}
q^{(3)} = U_1 q^{(1)} + U_2 q^{(2)} + \xi\,y,
\qquad
y\equiv x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)},
\end{equation}
with
\begin{equation}
\label{eq:s10-011}
U_r \equiv \widehat F_3 P_r \widehat F_r^\dagger,
\qquad
\xi \equiv \widehat F_3 P_1 {\bf 1}_{N_1}
= -\widehat F_3 P_2 {\bf 1}_{N_2}.
\end{equation}
So the nonzero Fourier modes are determined by the site-basis overlap together with the relative center-of-mass displacement $y$. This is the discrete counterpart of the fact that continuum three-string vertices contain both quadratic Neumann coefficients and linear zero-mode couplings.
The inclusion maps satisfy
\[
P_1P_1^T+P_2P_2^T=\mathbb I_{N_3},
\qquad
P_r^T P_r = \mathbb I_{N_r},
\]
and the truncated DFTs satisfy $\widehat F_r\widehat F_r^\dagger=\mathbb I_{N_r-1}$ and $\widehat F_r^\dagger\widehat F_r=\mathbb I_{N_r}-N_r^{-1}{\bf 1}_{N_r}{\bf 1}_{N_r}^T$. Therefore
\begin{equation}
\label{eq:s10-012}
U_r^\dagger U_r = \mathbb I_{N_r-1},
\qquad
U_1U_1^\dagger + U_2U_2^\dagger
=
\mathbb I_{N_3-1}-\frac{N_3}{N_1N_2}\,\xi\xi^\dagger.
\end{equation}
Equivalently, if one defines the normalized affine direction
\begin{equation}
\label{eq:s10-013}
\widehat\xi\equiv \sqrt{\frac{N_3}{N_1N_2}}\,\xi,
\end{equation}
then
\begin{equation}
\label{eq:s10-014}
U_1U_1^\dagger + U_2U_2^\dagger + \widehat\xi\,\widehat\xi^\dagger = \mathbb I_{N_3-1}.
\end{equation}
This is the precise nonzero-mode completeness relation. The rank-one term is not a nuisance correction; it is exactly the relative center-of-mass direction that remains after the weighted average zero mode has been removed.
Figure~\ref{fig:arc-inclusion-affine} packages this geometry: the inclusion maps $P_1,P_2$ place the two incoming strips on the two arcs of the outgoing strip, while the mismatch of their center-of-mass positions contributes the affine term $\xi y$.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\node[font=\bfseries] at (0,3.55) {Arc inclusion and affine zero-mode shift};

\draw[thick,blue] (-4.2,2.25) -- (0,2.25);
\draw[thick,green!50!black] (0,2.25) -- (4.2,2.25);
\fill[blue] (-2.25,2.25) circle (1.4pt);
\fill[green!50!black] (2.25,2.25) circle (1.4pt);
\fill (0,2.25) circle (1.2pt);
\node[above] at (0,2.58) {outgoing strip $3$};
\node[blue,fill=white,inner sep=1pt] at (-2.25,1.88) {image of $P_1$};
\node[green!50!black,fill=white,inner sep=1pt] at (2.25,1.88) {image of $P_2$};

\draw[thick,blue] (-3.4,0.85) -- (-1.15,0.85);
\draw[thick,green!50!black] (1.15,0.85) -- (3.4,0.85);
\fill[blue] (-2.25,0.85) circle (1.4pt);
\fill[green!50!black] (2.25,0.85) circle (1.4pt);
\node[blue,below] at (-2.25,0.55) {incoming strip $1$};
\node[green!50!black,below] at (2.25,0.55) {incoming strip $2$};
\draw[->,thick,blue] (-2.25,1.08) -- (-2.25,2.05);
\draw[->,thick,green!50!black] (2.25,1.08) -- (2.25,2.05);

\draw[dashed] (-2.25,0.85) -- (-2.25,-0.65);
\draw[dashed] (2.25,0.85) -- (2.25,-0.65);
\fill (-2.25,-0.65) circle (1.3pt);
\fill (2.25,-0.65) circle (1.3pt);
\node[below,fill=white,inner sep=1pt] at (-2.25,-0.78) {$x_{\mathrm{cm}}^{(1)}$};
\node[below,fill=white,inner sep=1pt] at (2.25,-0.78) {$x_{\mathrm{cm}}^{(2)}$};
\draw[<->,dashed] (-2.25,-1.15) -- (2.25,-1.15);
\node[below,fill=white,inner sep=1pt] at (0,-1.28) {$y=x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}$};

\node[draw,rounded corners,align=center,text width=9.2cm,inner sep=4pt] at (0,-2.85)
{Geometric inclusion gives $U_r=\widehat F_3 P_r \widehat F_r^\dagger$.\\
The relative center-of-mass displacement produces the affine correction $\xi y$ in $q^{(3)}$.};
\end{tikzpicture}
\caption{Geometry behind the affine Fourier overlap. The incoming site data are first included into the two arcs of the outgoing strip by $P_1$ and $P_2$. After subtracting the weighted center-of-mass piece, the nonzero Fourier modes are not purely homogeneous: the relative displacement $y$ of the two incoming centers of mass survives as the affine term $\xi y$.}
\label{fig:arc-inclusion-affine}
\end{figure}

The matrix elements are completely explicit:
\begin{equation}
\label{eq:s10-015}
(U_1)_{m\ell}
=
\frac{1}{\sqrt{N_3 N_1}}
\sum_{n=0}^{N_1-1}
e^{-2\pi \ii mn/N_3} e^{2\pi \ii \ell n/N_1},
\qquad
m=1,\dots,N_3-1,\quad \ell=1,\dots,N_1-1,
\end{equation}
\begin{equation}
\label{eq:s10-016}
(U_2)_{m\ell}
=
\frac{1}{\sqrt{N_3 N_2}}
\sum_{n=0}^{N_2-1}
e^{-2\pi \ii m(n+N_1)/N_3} e^{2\pi \ii \ell n/N_2},
\qquad
m=1,\dots,N_3-1,\quad \ell=1,\dots,N_2-1.
\end{equation}
The second matrix carries the expected phase offset coming from the fact that the second string occupies the interval $\sigma\in[\alpha_1,\alpha_3]$ on the outgoing leg. The center-of-mass mixing vector is equally explicit:
\begin{equation}
\label{eq:s10-017}
\xi_m
=
\frac{1}{\sqrt{N_3}}
\sum_{n=0}^{N_1-1}
e^{-2\pi \ii mn/N_3}
=
\frac{1-e^{-2\pi \ii m N_1/N_3}}{\sqrt{N_3}\,\bigl(1-e^{-2\pi \ii m/N_3}\bigr)},
\qquad
m=1,\dots,N_3-1.
\end{equation}
Note that $\xi_m=0$ whenever $mN_1/N_3\in\ZZ$, i.e.\ when $m$ is a multiple of $N_3/\gcd(N_1,N_3)$. At those mode numbers the relative center-of-mass displacement decouples identically from the nonzero Fourier sector.

To compare directly with oscillator formulas, define for each nonzero mode
\begin{equation}
\label{eq:s10-018}
a_m^{(r)}
=
\sqrt{\frac{\mu_r\omega_m^{(r)}}{2}}\,q_m^{(r)}
\,+\,
\frac{\ii}{\sqrt{2\mu_r\omega_m^{(r)}}}\,\pi_m^{(r)},
\qquad
\mu_r=\frac{a_r}{2\pi\al},
\qquad
\omega_m^{(r)}=\frac{2}{a_r}\sin\!\left(\frac{\pi m}{N_r}\right).
\end{equation}
Equivalently, the exact site-to-oscillator map is
\begin{equation}
\label{eq:s10-019}
\begin{aligned}
a_m^{(r)}
=
\frac{1}{\sqrt{N_r}}
\sum_{n=0}^{N_r-1}
\left[
\sqrt{\frac{\mu_r\omega_m^{(r)}}{2}}\,X_n^{\prime(r)}
+\frac{\ii}{\sqrt{2\mu_r\omega_m^{(r)}}}\,P_n^{\prime(r)}
\right]
e^{-2\pi \ii mn/N_r}.
\end{aligned}
\end{equation}
The inverse formulas are
\begin{equation}
\label{eq:s10-020}
\begin{aligned}
X_n^{\prime(r)}
&=
\frac{1}{\sqrt{N_r}}
\sum_{m=1}^{N_r-1}
\frac{a_m^{(r)}+a_{N_r-m}^{(r)\dagger}}{\sqrt{2\mu_r\omega_m^{(r)}}}
e^{2\pi \ii mn/N_r},\\
P_n^{\prime(r)}
&=
\frac{-\ii}{\sqrt{N_r}}
\sum_{m=1}^{N_r-1}
\sqrt{\frac{\mu_r\omega_m^{(r)}}{2}}\,
\bigl(a_m^{(r)}-a_{N_r-m}^{(r)\dagger}\bigr)
e^{2\pi \ii mn/N_r}.
\end{aligned}
\end{equation}
The DFT convention implies the canonical commutator
\begin{equation}
\label{eq:s10-021}
\bigl[q_m^{(r)},\pi_n^{(s)}\bigr]
=
\mathrm{i}\,\delta^{rs}\delta_{m,N_r-n},
\end{equation}
with all other commutators vanishing on the nonzero-mode sector. Consequently,
\begin{equation}
\label{eq:s10-022}
\bigl[a_m^{(r)},a_n^{(s)\dagger}\bigr]
=
\delta^{rs}\delta_{mn},
\end{equation}
with all other commutators vanishing. In the redundant full-spectrum bookkeeping basis the partner mode $a_{N_r-m}^{(r)}$ is related to $a_m^{(r)\dagger}$ only by the anti-linear reality involution on physical states; it should not be treated as a second independent canonical commutator before one passes to the reduced physical basis.
In these formulas I keep the full complexified nonzero Fourier basis $m=1,\dots,N_r-1$. Reality of the original site field is imposed by the anti-linear involution
\begin{equation}
\label{eq:s10-023}
q_{N_r-m}^{(r)}=\bigl(q_m^{(r)}\bigr)^*,
\qquad
\pi_{N_r-m}^{(r)}=\bigl(\pi_m^{(r)}\bigr)^*,
\end{equation}
on physical states. Equivalently, one may restrict to an independent half-spectrum. The linear overlap equations are conveniently written in the full complexified basis, but the actual squeezed-state inversion must be carried out only after passing to an independent half-spectrum or to an equivalent real sine/cosine basis.
For oscillator bookkeeping it is therefore better to introduce the $(N_r-1)\times(N_r-1)$ permutation matrix $\mathcal R_r$ with components
\begin{equation}
\label{eq:s10-024}
(\mathcal R_r)_{mn}=\delta_{m,N_r-n},
\end{equation}
so that the creation-partner vector in the redundant full-spectrum basis is $(\mathcal R_r{\bf a}^{(r)\dagger})_m=a_{N_r-m}^{(r)\dagger}$. The operator $a_{N_r-m}^{(r)}$ itself is not equal to $a_m^{(r)\dagger}$; rather, $a_m^{(r)}$ pairs canonically with $a_{N_r-m}^{(r)\dagger}$, exactly as in the inverse formulas above.
For example, if $N_r$ is odd one may keep the representatives $m=1,\dots,(N_r-1)/2$. If $N_r$ is even, one may keep $m=1,\dots,N_r/2-1$ together with the real self-conjugate Nyquist mode $m=N_r/2$ handled separately.
Figure~\ref{fig:half-spectrum-choice} summarizes this reduction: the redundant full complexified spectrum is a convenient bookkeeping device, but only the reduced physical basis is used for the Gaussian inversions that define the squeeze matrices.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\node[font=\bfseries] at (0,2.45) {Redundant complex spectrum versus physical oscillator basis};

\node[draw,rounded corners,align=center,text width=5.4cm,inner sep=6pt] at (-3.4,0.55)
{\textbf{Full complexified bookkeeping basis}\\
nonzero modes $m=1,\dots,N_r-1$\\
$q_m,\ \pi_m,\ a_m$ together with their partners\\
$q_{N_r-m},\ \pi_{N_r-m},\ a_{N_r-m}$};

\fill (-4.9,-1.3) circle (1.3pt);
\fill (-4.1,-1.3) circle (1.3pt);
\fill (-3.3,-1.3) circle (1.3pt);
\fill (-2.5,-1.3) circle (1.3pt);
\draw[<->,dashed] (-4.9,-1.55) -- (-2.5,-1.55);
\node at (-4.9,-1.87) {$m$};
\node at (-2.5,-1.87) {$N_r-m$};
\node[fill=white,inner sep=1pt] at (-3.7,-1.87) {paired by reality};

\draw[->,thick] (-0.8,0.55) -- (0.8,0.55);
\node[align=center,fill=white,inner sep=1pt] at (0,1.0) {impose reality\\ and remove duplicates};

\node[draw,rounded corners,align=center,text width=5.4cm,inner sep=6pt] at (3.4,0.55)
{\textbf{Independent physical basis}\\
keep one representative from each pair\\
or pass to real cosine/sine variables\\
Nyquist mode treated separately when $N_r$ is even};

\node[draw,rounded corners,align=center,text width=10.2cm,inner sep=5pt] at (0,-2.35)
{The overlap equations may be written in the left-hand bookkeeping basis, but the fermionic squeeze-matrix inversion and the reduced Gaussian constructions are performed only on the reduced physical basis on the right.};
\end{tikzpicture}
\caption{Why the overlap algebra is reduced to a half-spectrum or an equivalent real basis. The full complexified nonzero Fourier basis is redundant because modes $m$ and $N_r-m$ are related by the reality involution. Keeping the full basis is convenient for writing the overlap equations, but the actual reduced Gaussian constructions---and, in the fermionic sector, the squeeze-matrix inversion---are performed only after reducing to an independent physical set of oscillators.}
\label{fig:half-spectrum-choice}
\end{figure}

For fermions one uses the same DFT matrices. Writing
\begin{equation}
\label{eq:s10-025}
\theta_n^{(r)a}=\theta_{\mathrm{av}}^{(r)a}+\frac{1}{\sqrt{N_r}}\sum_{m=1}^{N_r-1}\vartheta_m^{(r)a}e^{2\pi \ii mn/N_r},
\end{equation}
with the SO$(8)$ spinor index $a$ shown explicitly only here and suppressed again below when no confusion results. At this stage $\vartheta_m^{(r)a}$ is the classical Fourier coefficient of the Grassmann field on leg $r$. The average Grassmann mode obeys
\begin{equation}
\label{eq:s10-026}
N_3\theta_{\mathrm{av}}^{(3)}=N_1\theta_{\mathrm{av}}^{(1)}+N_2\theta_{\mathrm{av}}^{(2)},
\end{equation}
and if one keeps the relative average Grassmann mode
\begin{equation}
\label{eq:s10-027}
\upsilon\equiv \theta_{\mathrm{av}}^{(1)}-\theta_{\mathrm{av}}^{(2)},
\end{equation}
explicit, then the nonzero Fourier modes obey the same affine overlap pattern as the bosons,
\begin{equation}
\label{eq:s10-028}
\vartheta^{(3)} = U_1 \vartheta^{(1)} + U_2 \vartheta^{(2)} + \xi\,\upsilon.
\end{equation}
In a coherent-state oscillator basis one introduces fermionic annihilation and creation operators $b_m^{(r)}, b_m^{(r)\dagger}$ whose coherent-state eigenvalues are the nonzero-mode Grassmann variables on leg $r$. In the complexified bookkeeping basis they satisfy
\begin{equation}
\label{eq:s10-029}
\{b_m^{(r)},b_n^{(s)\dagger}\}=\delta^{rs}\delta_{mn},
\qquad
b_{N_r-m}^{(r)}=\bigl(b_m^{(r)}\bigr)^\dagger
\quad
\text{on physical states},
\end{equation}
so the same half-spectrum reduction discussed for the bosons applies here as well. The affine Grassmann term then becomes the corresponding linear source in the displaced fermionic squeezed state. Thus both the bosonic and fermionic cubic vertices are defined most naturally in $\sigma$ position space, while the familiar oscillator-basis data are obtained by the explicit DFT maps above.

Figure~\ref{fig:basis-map} summarizes the bookkeeping: the discretized calculation is done in site variables, while comparison with conventional string-amplitude formulas is made after the explicit DFT and oscillator transforms.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=1.0, every node/.style={font=\small}]
\draw[thick,rounded corners] (-5.3,-1.1) rectangle (-1.7,1.45);
\draw[thick,rounded corners] (-0.8,-1.1) rectangle (2.8,1.45);
\draw[thick,rounded corners] (3.7,-1.1) rectangle (7.3,1.45);

\node[align=center] at (-3.5,0.95) {\textbf{$\sigma$-site basis}};
\node[align=center] at (-3.5,0.2) {$X_n^{(r)},\ \theta_n^{(r)}$};
\node[align=center] at (-3.5,-0.45) {exact overlap\\ $X^{(3)}=P_1X^{(1)}+P_2X^{(2)}$};

\node[align=center] at (1.0,0.95) {\textbf{DFT / mode basis}};
\node[align=center] at (1.0,0.2) {$x_{\mathrm{cm}}^{(r)},\ q_m^{(r)}$};
\node[align=center] at (1.0,-0.45) {$\theta_{\mathrm{av}}^{(r)},\ \vartheta_m^{(r)}$};

\node[align=center] at (5.5,0.95) {\textbf{Oscillator basis}};
\node[align=center] at (5.5,0.2) {$a_m^{(r)},\ a_m^{(r)\dagger}$};
\node[align=center] at (5.5,-0.45) {$b_m^{(r)},\ b_m^{(r)\dagger}$};

\draw[->,thick] (-1.65,0.2) -- node[above] {$\widehat F_r$} (-0.85,0.2);
\draw[->,thick] (2.85,0.2) -- node[above] {$\mu_r,\Omega_r$} (3.65,0.2);

\draw[->,thick,dashed] (1.0,-1.45) -- (1.0,-2.4);
\node[align=center] at (1.0,-3.0) {affine zero-mode data\\ $y=x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}$,\\ $\upsilon=\theta_{\mathrm{av}}^{(1)}-\theta_{\mathrm{av}}^{(2)}$};
\draw[->,thick,dashed] (1.0,-2.4) -- (3.4,-2.4);
\draw[->,thick,dashed] (3.4,-2.4) -- (5.5,-1.15);
\end{tikzpicture}
\caption{Three equivalent descriptions of the same cubic data. The numerical sewing problem is posed in $\sigma$ position space, then transformed to nonzero Fourier modes, and finally to creation/annihilation variables for direct comparison with the usual lightcone vertex. The affine zero-mode data survive this chain as source terms rather than as part of the homogeneous oscillator overlap.}
\label{fig:basis-map}
\end{figure}

\section{Bosonic cubic vertex in oscillator basis}
The exact position-space overlap state is
\begin{equation}
\label{eq:s11-001}
\langle X^{(1)},X^{(2)},X^{(3)}|V_3^{(B)}\rangle
=
\delta\!\bigl(X^{(3)}-P_1X^{(1)}-P_2X^{(2)}\bigr).
\end{equation}
This state is the kinematic core of the cubic vertex: it enforces the exact sewing of the three bosonic boundaries and nothing more. In particular, it is not yet the full interacting Hamiltonian vertex with its final normalization and interaction-point completion.
After separating center-of-mass and oscillator variables, this becomes
\begin{equation}
\label{eq:s11-002}
\delta\!\left(
x_{\mathrm{cm}}^{(3)}-\frac{N_1x_{\mathrm{cm}}^{(1)}+N_2x_{\mathrm{cm}}^{(2)}}{N_3}
\right)
\,
\delta\!\left(q^{(3)}-U_1q^{(1)}-U_2q^{(2)}-\xi y\right),
\end{equation}
with $y=x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}$. If one Fourier transforms the center-of-mass variables to momentum space, the first delta becomes the usual transverse momentum conservation factor
\begin{equation}
\label{eq:s11-003}
\delta^{(\perpD)}\!\left(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)}\right),
\end{equation}
while the second delta produces the familiar zero-mode-dependent linear terms in the oscillator vertex. This is the discrete version of the standard continuum three-string structure.

Canonical invariance of the one-form
\begin{equation}
\label{eq:s11-004}
\sum_{r=1}^3 \epsilon_r\, P^{(r)} \cdot \delta X^{(r)},
\qquad
(\epsilon_1,\epsilon_2,\epsilon_3)=(+1,+1,-1),
\end{equation}
where $\delta$ denotes the variation of the canonical one-form, not a Kronecker or Dirac delta,
restricted to the oscillator sector then gives the conjugate momentum overlap
\begin{equation}
\label{eq:s11-005}
\pi^{(1)} = U_1^\dagger \pi^{(3)},
\qquad
\pi^{(2)} = U_2^\dagger \pi^{(3)}.
\end{equation}
Here the variation is taken at fixed zero-mode data, so $\delta y=0$ in the oscillator derivation. The center-of-mass momentum conservation is handled separately by Fourier transforming the weighted center-of-mass overlap, which yields the factor $\delta^{(\perpD)}(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)})$ already displayed above.

Define oscillator annihilation operators on each leg by
\begin{equation}
\label{eq:s11-006}
a^{(r)} =
\frac{1}{\sqrt2}\left(
(\mu_r\Omega_r)^{1/2} q^{(r)}
\,+\,
\ii\,(\mu_r\Omega_r)^{-1/2}\pi^{(r)}
\right),
\qquad
\Omega_r = \mathrm{diag}\!\bigl(\omega_m^{(r)}\bigr)_{m=1}^{N_r-1},
\end{equation}
and collect them into one column vector
\begin{equation}
\label{eq:s11-007}
{\bf a} =
\begin{pmatrix}
a^{(1)}\\
a^{(2)}\\
a^{(3)}
\end{pmatrix},
\qquad
\boldsymbol{\mu}=\mathrm{diag}(\mu_1 I,\mu_2 I,\mu_3 I),
\qquad
\Omega = \mathrm{diag}(\Omega_1,\Omega_2,\Omega_3).
\end{equation}
Here each identity block $I$ is the identity matrix on the nonzero-mode space of the corresponding leg, of size $(N_r-1)\times(N_r-1)$. I write the stacked oscillator vector as ${\bf a}$ rather than $A$ in order to reserve the capital letter $A$ for graph-cycle labels, and I write the block-diagonal matrix $\boldsymbol{\mu}$ to distinguish it from the scalar single-cylinder parameter $\mu$.
Introduce the coordinate and momentum overlap matrices
\begin{equation}
\label{eq:s11-008}
C_Q=
\begin{pmatrix}
U_1 & U_2 & -I
\end{pmatrix},
\qquad
C_P=
\begin{pmatrix}
I & 0 & -U_1^\dagger \\
0 & I & -U_2^\dagger
\end{pmatrix}.
\end{equation}
Again, each $I$ denotes the identity on the relevant leg's nonzero-mode space, so the block sizes are fixed by the dimensions of $U_1$ and $U_2$.
The homogeneous part of the overlap conditions is equivalent to
\begin{equation}
\label{eq:s11-009}
(\mathbb M {\bf a} + \mathbb N \mathcal R\,{\bf a}^\dagger)\,|V_3^{(B)}\rangle = 0,
\end{equation}
where $\mathcal R=\mathrm{diag}(\mathcal R_1,\mathcal R_2,\mathcal R_3)$ is the block-diagonal reality permutation introduced above, so that $(\mathcal R{\bf a}^\dagger)_m=a_{N-m}^\dagger$ leg by leg in the full redundant basis.
with
\begin{equation}
\label{eq:s11-010}
\mathbb M =
\begin{pmatrix}
 C_Q (\boldsymbol{\mu}\Omega)^{-1/2}\\
 -\ii C_P (\boldsymbol{\mu}\Omega)^{1/2}
\end{pmatrix},
\qquad
\mathbb N =
\begin{pmatrix}
 C_Q (\boldsymbol{\mu}\Omega)^{-1/2}\\
 \ii C_P (\boldsymbol{\mu}\Omega)^{1/2}
\end{pmatrix}.
\end{equation}
Because the position-space sewing is affine on the oscillator variables, the full constraint at fixed relative center-of-mass coordinate $y$ is actually
\begin{equation}
\label{eq:s11-011}
(\mathbb M {\bf a} + \mathbb N \mathcal R\,{\bf a}^\dagger + J_0(y))\,|V_3^{(B)}\rangle = 0,
\end{equation}
where in the convention used here, with the center-of-mass coordinate Fourier transformed to transverse momentum and only the relative displacement $y=x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}$ left explicit,
\begin{equation}
\label{eq:s11-012}
J_0(y)=
\begin{pmatrix}
\sqrt2\,\xi\,y\\
0
\end{pmatrix}.
\end{equation}
The symbol $J_0(y)$ should be read in the same spirit as the auxiliary sources of Section~8, but its role is slightly different. It is not a freely introduced bookkeeping variable; rather, it is the fixed inhomogeneous term forced by the affine overlap itself. Physically it remembers the relative displacement $y=x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}$ of the two incoming centers of mass after the weighted average mode has been separated off. If $y=0$, the overlap constraints become homogeneous. At a purely formal level one is then tempted to package the vertex as an ordinary squeezed state and, for general $y$, as a displaced one. No Bessel functions appear anywhere in this note, so the notation $J_0(y)$ here refers only to this affine source vector.
The upper block comes from the affine coordinate overlap $C_Qq=-\xi y$, while the lower block vanishes because the oscillator momentum overlap is homogeneous. In a different zero-mode basis the source vector is obtained from this one by a linear change of variables. The constraint count is
\begin{equation}
\label{eq:s11-013}
N_{\mathrm{rows}}(C_Q)+N_{\mathrm{rows}}(C_P)
=(N_3-1)+(N_1-1+N_2-1)=2N_3-3,
\end{equation}
which matches the number of nonzero complex mode labels on the three legs. The actual number of independent real oscillators is obtained only after imposing the reality conditions on $(q,\pi)$ and eliminating the redundant pairs $(m,N_r-m)$, or equivalently after passing to an independent half-spectrum or real sine/cosine basis. In the full redundant notation the same redundancy is what forces the creation-partner vector to appear as $\mathcal R{\bf a}^\dagger$ rather than ${\bf a}^\dagger$ itself. Let ${\bf a}_{\mathrm{phys}}$ denote such a reduced basis, and let $\mathbb M_{\mathrm{phys}}$, $\mathbb N_{\mathrm{phys}}$, $J_{0,\mathrm{phys}}$ be the corresponding matrices. Concretely, one may take ${\bf a}_{\mathrm{phys}}$ to contain one oscillator from each pair $(m,N_r-m)$ on every leg, together with the separate real Nyquist oscillator when $N_r$ is even. Since each $(\mu_r\Omega_r)^{\pm1/2}$ is invertible on the nonzero-mode sector, nondegeneracy of $\mathbb M_{\mathrm{phys}}$ reduces to linear independence of the exact overlap constraints on the physical oscillator space. This is a finite-dimensional statement that can and should be checked numerically at each lattice resolution $N$. One must nevertheless be careful: for a regular bosonic squeezed state the mixed overlap block would vanish, whereas here
\begin{equation}
C_Q C_P^T
=
2\begin{pmatrix}U_1 & U_2\end{pmatrix}\neq 0.
\label{eq:bosonic-symplectic-obstruction}
\end{equation}
For a genuine bosonic squeezed state one would need
\begin{equation}
\label{eq:s11-014}
S^{(B)T}=S^{(B)},
\qquad
S^{(B)}=-\mathbb M_{\mathrm{phys}}^{-1}\mathbb N_{\mathrm{phys}},
\end{equation}
which is equivalent to
\begin{equation}
\label{eq:s11-015}
\mathbb M_{\mathrm{phys}}\mathbb N_{\mathrm{phys}}^T
=
\mathbb N_{\mathrm{phys}}\mathbb M_{\mathrm{phys}}^T.
\end{equation}
But with the explicit block form of $\mathbb M$ and $\mathbb N$ one finds
\begin{equation}
\label{eq:s11-016}
\mathbb M\mathbb N^T-\mathbb N\mathbb M^T
=
2\ii
\begin{pmatrix}
0 & C_QC_P^T\\
-C_PC_Q^T & 0
\end{pmatrix},
\end{equation}
so the nonvanishing of $C_QC_P^T$ is exactly the obstruction to a symmetric finite-$N$ direct inversion. Thus the exact cubic overlap state is closer to a boundary-state distribution than to a normalizable Fock-space squeezed state. The local diagnostic \texttt{squeeze\_matrix\_check.py} verifies this obstruction explicitly. In particular, the naive direct inversion $-\mathbb M_{\mathrm{phys}}^{-1}\mathbb N_{\mathrm{phys}}$ does \emph{not} produce a symmetric matrix at finite $N$: the condition $C_QC_P^T\neq 0$ implies $\mathbb M_{\mathrm{phys}}\mathbb N_{\mathrm{phys}}^T\neq \mathbb N_{\mathrm{phys}}\mathbb M_{\mathrm{phys}}^T$ already in exact arithmetic. What one should trust numerically are the exact reduced Gaussian matrix elements obtained after solving the position-space overlap. With that caveat, it is still convenient to package the overlap state in the following \emph{formal} shorthand:
\begin{equation}
|V_3^{(B)}\rangle_{\mathrm{formal}} =
{\cal C}_3^{(B)}
\delta^{(\perpD)}(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)})
\exp\!\left[
 -\frac12 {\bf a}_{\mathrm{phys}}^{\dagger T}\,S^{(B)}\,{\bf a}_{\mathrm{phys}}^\dagger
 -{\bf a}_{\mathrm{phys}}^{\dagger T}\Lambda^{(B)}(y)
 -\frac12\Phi^{(B)}(y)
\right]|0\rangle,
\label{eq:V3B-squeezed}
\end{equation}
with
\begin{equation}
S^{(B)} = -\mathbb M_{\mathrm{phys}}^{-1}\mathbb N_{\mathrm{phys}},
\qquad
\Lambda^{(B)} = -\mathbb M_{\mathrm{phys}}^{-1}J_{0,\mathrm{phys}},
\label{eq:V3B-formal-data}
\end{equation}
while $\Phi^{(B)}(y)$ is the scalar normal-ordering completion. Its value is determined uniquely by the displaced Gaussian completion once a physical basis and vacuum normalization are fixed. In the explicit three-tachyon vacuum matrix element of Section~12.1 it reduces to $\Phi^{(B)}(y)=\gamma_T(N,\alpha)\,y^2$, with $\gamma_T$ given by the Schur complement formula~\eqref{eq:gammaT}. The overall constant ${\cal C}_3^{(B)}$ is likewise not fixed by the annihilation equations alone: at finite $N$ it is a lattice-resolution-dependent analogue of the Mandelstam local normalization. In principle one may tie this normalization back to the same Poincare-algebra logic that fixes the continuum cubic vertex, but for the present numerical program the more immediate task is simply to determine how this factor enters explicit low-point amplitudes and to compare the resulting continuum extrapolation with the standard lightcone targets. Equivalently, one may define $\Phi^{(B)}(y)$ by
\begin{equation}
e^{-\Phi^{(B)}(y)/2}
\equiv
\frac{\langle 0|V_3^{(B)}(y)\rangle}
{{\cal C}_3^{(B)}\,
\delta^{(\perpD)}(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)})},
\label{eq:PhiB-from-vacuum}
\end{equation}
so $\Phi^{(B)}(y)$ is a quadratic form in the relative center-of-mass displacement $y$ determined uniquely once the exact overlap state is normalized. Here $|0\rangle$ is the finite-$N$ Fock vacuum annihilated by every oscillator in the chosen physical half-spectrum on each leg. If one still packages the formal boundary-state data back in the redundant full-spectrum notation, then using the same $\mathcal R=\mathrm{diag}(\mathcal R_1,\mathcal R_2,\mathcal R_3)$ as above, with $(\mathcal R_r)_{mn}=\delta_{m,N_r-n}$, one writes the involution relations
\begin{equation}
S^{(B)}_{\mathrm{full}}=\mathcal R\,S^{(B)*}_{\mathrm{full}}\,\mathcal R,
\qquad
\Lambda^{(B)}_{\mathrm{full}}=\mathcal R\,\Lambda^{(B)*}_{\mathrm{full}}.
\label{eq:V3B-full-reality}
\end{equation}
For actual finite-$N$ comparisons, however, the safer object is the Gaussian-moment definition of the full three-leg Neumann data,
\begin{equation}
\bar N^{rs}_{mn}(N)
\equiv
-\frac{\langle 0|a_m^{(r)}a_n^{(s)}|V_3^{(B)}\rangle}
{\langle 0|V_3^{(B)}\rangle},
\label{eq:gaussian-moment-neumann}
\end{equation}
evaluated from the exact reduced Gaussian after eliminating one leg. In that representation the symmetry $\bar N^{rs}_{mn}=\bar N^{sr}_{nm}$ follows directly from the symmetry of the reduced Gaussian matrix $G_T^{-1}$. The local diagnostic \texttt{squeeze\_matrix\_check.py} implements this extraction numerically. So the continuum-comparison Neumann data used below should be understood in this Gaussian-moment sense, not as the output of a naive direct inversion of the formal boundary-state matrix.

\section{Bosonic continuum target and numerical checks}
In lightcone gauge, the cubic Hamiltonian and Lorentz generators are expanded as
\begin{equation}
\label{eq:s12-001}
P^- = P^-_2 + g P^-_3 + O(g^2),
\qquad
J^{-I} = J^{-I}_2 + g J^{-I}_3 + O(g^2).
\end{equation}
Here $g$ is the string coupling constant, $P^-_2$ is the free bosonic lightcone Hamiltonian, and $P^-_3$ is its cubic interaction correction. The equations in this section are continuum target relations that the discrete construction should reproduce in the continuum limit.
At order $g$, Lorentz invariance requires
\begin{equation}
\label{eq:s12-002}
[J^{-I}_2,P^-_3] + [J^{-I}_3,P^-_2] = 0,
\qquad
[J^{-I}_2,J^{-J}_3] + [J^{-I}_3,J^{-J}_2] = 0.
\end{equation}
These are standard continuum target relations, not new claims of this note. They are recorded here only to clarify what the discrete-$\sigma$ construction should approach in the continuum limit and why the cubic interaction is local at the join. The main focus below is therefore not a fresh proof of lightcone-gauge Lorentz invariance, but explicit finite-$N$ amplitude diagnostics and their continuum behavior.

The kinematical generators are straightforward:
\begin{itemize}
\item $P^+$ is conserved because $N_3=N_1+N_2$, equivalently $\alpha_3=\alpha_1+\alpha_2$ in the positive-circumference notation introduced in Section~4.
\item $P^I$ is conserved because the zero-mode overlap gives $\delta^{(\perpD)}(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)})$.
\item $J^{IJ}$ is automatic because the overlap state is an SO$(D-2)$ scalar in the transverse indices.
\item $J^{+I}$ follows from the weighted center-of-mass relation together with $P^+$ conservation.
\end{itemize}
Indeed, since $p_r^+=\alpha_r/(2\alpha')$ in that same positive-circumference notation, the weighted identity $\alpha_3 x_{\mathrm{cm}}^{(3)}=\alpha_1 x_{\mathrm{cm}}^{(1)}+\alpha_2 x_{\mathrm{cm}}^{(2)}$ is precisely the condition needed for the center-of-mass part of $J^{+I}$ to sew consistently across the cubic vertex.

Before attacking the dynamical commutator, one can already make the locality of the bosonic obstruction completely explicit in $\sigma$ position space. At one cubic join with common lattice spacing $a$, the exact overlap
\[
X^{(3)}=P_1X^{(1)}+P_2X^{(2)}
\]
and canonical one-form invariance imply the site-space momentum overlap
\begin{equation}
\label{eq:s12-003}
P^{(1)}=P_1^T P^{(3)},
\qquad
P^{(2)}=P_2^T P^{(3)}.
\end{equation}
Now define the discrete free quadratic form on leg $r$ by
\begin{equation}
\label{eq:s12-004}
\mathcal H_r^{\mathrm{lat}}
\equiv
\sum_{n=0}^{N_r-1}
\left[
\frac{\pi\alpha'}{a}\bigl(P_n^{(r)}\bigr)^2
\,+\,
\frac{1}{4\pi\alpha' a}\bigl(X_{n+1}^{(r)}-X_n^{(r)}\bigr)^2
\right],
\qquad
X_{N_r}^{(r)}\equiv X_0^{(r)}.
\end{equation}
The corresponding discrete free lightcone Hamiltonian on leg $r$ is
\begin{equation}
\label{eq:s12-005}
P^-_{2,r}
=
\frac{1}{2p_r^+}\left(\mathcal H_r^{\mathrm{lat}}-E_{0,r}^{\mathrm{lat}}\right),
\qquad
E_{0,r}^{\mathrm{lat}}
=
\frac{\perpD}{2}\sum_{m=1}^{N_r-1}\omega_m^{(r)},
\end{equation}
where $E_{0,r}^{\mathrm{lat}}$ is the finite-$N$ zero-point energy obtained by summing the nonzero lattice frequencies of the $D_\perp$ transverse oscillators. For the locality argument below only the explicit site dependence in $\mathcal H_r^{\mathrm{lat}}$ matters, because the normal-ordering term is a join-local constant once the overlap state is fixed. The momentum part cancels exactly on the overlap state:
\begin{equation}
\label{eq:s12-006}
\sum_{n=0}^{N_1-1}\bigl(P_n^{(1)}\bigr)^2
\,+\,
\sum_{m=0}^{N_2-1}\bigl(P_m^{(2)}\bigr)^2
\;=\;
\sum_{\ell=0}^{N_3-1}\bigl(P_\ell^{(3)}\bigr)^2.
\end{equation}
For the bond terms, every bond away from the cut cancels pairwise under the ordered concatenation. The only uncancelled pieces are the two bonds adjacent to the unfolded interaction region:
\begin{equation}
\label{eq:s12-007}
\begin{aligned}
\Delta_I^{\mathrm{bond}}
&\equiv
\sum_{n=0}^{N_1-1}\bigl(X_{n+1}^{(1)}-X_n^{(1)}\bigr)^2
\,+\,
\sum_{m=0}^{N_2-1}\bigl(X_{m+1}^{(2)}-X_m^{(2)}\bigr)^2
\,-\,
\sum_{\ell=0}^{N_3-1}\bigl(X_{\ell+1}^{(3)}-X_\ell^{(3)}\bigr)^2\\
&=
\bigl(X_{I_+}-X_{N_1-1}^{(1)}\bigr)^2
\,+\,
\bigl(X_{I_-}-X_{N_2-1}^{(2)}\bigr)^2
\,-\,
\bigl(X_{I_-}-X_{N_1-1}^{(1)}\bigr)^2
\,-\,
\bigl(X_{I_+}-X_{N_2-1}^{(2)}\bigr)^2\\
&=
2\bigl(X_{I_+}-X_{I_-}\bigr)
\bigl(X_{N_2-1}^{(2)}-X_{N_1-1}^{(1)}\bigr).
\end{aligned}
\end{equation}
Equation~\eqref{eq:s12-007} is the clearest finite-$N$ sign that the interaction region is geometrically bond-centered rather than concentrated on one pre-existing lattice site: the free-Hamiltonian mismatch is supported only on the two bonds adjacent to the cut and depends explicitly on the join separation $(X_{I_+}-X_{I_-})$. This is why the note keeps $I_+$ and $I_-$ distinct at finite $a$ and treats the local prefactor as the place where the branch-point-local reconstruction is encoded.
Thus the exact $\sigma$-space sewing removes every bulk mismatch in the free quadratic form and leaves only a join-local remainder supported on the two cut-adjacent bonds. This is the discrete reason that the dynamical Lorentz test is a local interaction-point problem rather than a bulk one. Any discrete cubic correction that restores the $J^{-I}$ algebra must cancel this local remainder together with the usual normal-ordering contribution, and there is no further obstruction away from the join.
To make the local data more transparent, introduce the cut separation and the two incoming backward bond differences
\begin{equation}
\label{eq:s12-008}
\delta_I^X \equiv X_{I_+}-X_{I_-},
\qquad
\nabla_+^{\mathrm{bwd}}X_{I_+}^{(1)}\equiv X_{I_+}-X_{N_1-1}^{(1)},
\qquad
\nabla_-^{\mathrm{bwd}}X_{I_-}^{(2)}\equiv X_{I_-}-X_{N_2-1}^{(2)}.
\end{equation}
Then
\begin{equation}
\label{eq:s12-009}
\Delta_I^{\mathrm{bond}}
=
2\,\delta_I^X\Bigl(
\nabla_+^{\mathrm{bwd}}X_{I_+}^{(1)}
-\nabla_-^{\mathrm{bwd}}X_{I_-}^{(2)}
-\delta_I^X
\Bigr).
\end{equation}
So the bosonic obstruction is controlled by a finite set of local variables attached to the join: the cut separation $\delta_I^X$ and the two backward bond differences adjacent to it. This already isolates the first genuinely finite-$a$ ambiguity. The minimal GS prefactor ansatz discussed later uses the \emph{forward} arc differences $\nabla_+X_{I_+}$ and $\nabla_-X_{I_-}$, whereas the free-Hamiltonian mismatch naturally produces the \emph{backward} bond data above. The operator-level Lorentz calculation must therefore decide whether the continuum-limit matching and local commutator algebra relate these two choices strongly enough that the minimal prefactor is sufficient, or whether an additional finite-$a$ local counterterm supported at the join is required. The present note has reduced that question to a precise local comparison, but it does not yet resolve it.

The nontrivial test is the dynamical generator. For the closed bosonic string,
\begin{equation}
\label{eq:s12-010}
J^{-I}_2
=
x^- p^I
-\frac12 \{x^I,P^-_2\}
+\frac{\ii}{p^+}\sum_{n\ge 1}\frac{1}{n}
\left(
\alpha_{-n}^I L_n - L_{-n}\alpha_n^I
+\tilde\alpha_{-n}^I \tilde L_n - \tilde L_{-n}\tilde\alpha_n^I
\right),
\end{equation}
where $x^-$ is the lightcone coordinate conjugate to $p^+$, $\alpha_n^I$ and $\tilde\alpha_n^I$ are the standard continuum left- and right-moving bosonic oscillators, and $L_n$, $\tilde L_n$ are the corresponding Virasoro generators. These are not new lattice definitions; they are the familiar continuum operators used as the target of the discrete Lorentz check. The usual chiral normal-ordering constants are $a_L=a_R=1$, equivalently the left- and right-moving intercepts are both equal to one. Acting on the overlap state, the bulk pieces cancel because the $\sigma$-space sewing is exact. The only possible obstruction is a join-local normal-ordering anomaly. In the continuum this anomaly cancels precisely for
\begin{equation}
\label{eq:s12-011}
D=26,
\qquad
a_L=a_R=1
\quad
(\text{equivalently total intercept }2),
\end{equation}
together with the standard Mandelstam normalization of the cubic vertex. The discrete check is therefore:
\begin{enumerate}
\item build $|V_3^{(B)}\rangle$ from the exact $\sigma$-space overlap,
\item evaluate the lattice version of $[J^{-I}_2,P^-_3] + [J^{-I}_3,P^-_2]$,
\item isolate the residual join-local term,
\item verify that its continuum limit reproduces the usual critical-dimension constraint.
\end{enumerate}
So the bosonic cubic vertex is not just the overlap state: one must also choose a normalization convention and compare with the standard continuum lightcone amplitudes. For the present project, the primary deliverable is precisely that numerical comparison. The three-tachyon and $2T+1M$ calculations below should therefore be read as the first concrete validations of the discrete-$\sigma$ method, not merely as placeholders for a future operator proof. The continuum commutator remains a useful structural cross-check, but it is not the main point of this note.

\subsection{On-shell three-tachyon check}
The first external amplitude check in the bosonic theory is the closed-string three-tachyon matrix element. Each tachyon state is the oscillator vacuum on its leg, so there are no nonzero-mode polarization tensors and no oscillator insertions beyond the vacuum component of the cubic state. The lightcone matrix element therefore has the form
\begin{equation}
\label{eq:s12-1-001}
{\cal A}_{TTT}^{\mathrm{lc}}(N)
=
\delta^{(\perpD)}\!\bigl(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)}\bigr)\,
{\cal N}_{TTT}(p_1^+,p_2^+,p_3^+;N),
\end{equation}
where ${\cal N}_{TTT}$ is the scalar factor produced by the zero-mode overlap, the displaced-Gaussian completion, the overall cubic normalization ${\cal C}_3^{(B)}$, and the chosen external-state normalization convention. The longitudinal conservation law $p_3^+=p_1^++p_2^+$ is already built into the cubic kinematics through $\alpha_3=\alpha_1+\alpha_2$. Because the external states carry no oscillator or tensor structure, there is no room for any nontrivial Lorentz tensor at three points. Once the on-shell conditions and the lightcone energy-conservation delta function are restored, the covariant three-tachyon amplitude can depend on the external momenta only through the overall momentum-conservation factor and an overall constant normalization.

At the level of the explicit cubic vertex already written in this note, one can reduce the matrix element further. Write the weighted center-of-mass coordinate and relative coordinate as
\begin{equation}
\label{eq:s12-1-002}
X_{\mathrm{cm}}
\equiv
\frac{\alpha_1 x_{\mathrm{cm}}^{(1)}+\alpha_2 x_{\mathrm{cm}}^{(2)}}{\alpha_3}
=
x_{\mathrm{cm}}^{(3)},
\qquad
y\equiv x_{\mathrm{cm}}^{(1)}-x_{\mathrm{cm}}^{(2)}.
\end{equation}
Then
\begin{equation}
\label{eq:s12-1-003}
x_{\mathrm{cm}}^{(1)} = X_{\mathrm{cm}}+\frac{\alpha_2}{\alpha_3}y,
\qquad
x_{\mathrm{cm}}^{(2)} = X_{\mathrm{cm}}-\frac{\alpha_1}{\alpha_3}y.
\end{equation}
For momentum eigenstates on the three external legs, the integral over $X_{\mathrm{cm}}$ produces the displayed transverse momentum-conservation factor, while the remaining relative-coordinate integral gives
\begin{equation}
\label{eq:s12-1-004}
{\cal N}_{TTT}(p_1^+,p_2^+,p_3^+;N)
=
{\cal C}_3^{(B)}
\int \dd^{\perpD}y\;
\exp\!\left[
\ii\,q_{\mathrm{rel}}\!\cdot y
-\frac12 \Phi^{(B)}(y)
\right],
\end{equation}
with
\begin{equation}
\label{eq:s12-1-005}
q_{\mathrm{rel}}
\equiv
\frac{\alpha_2}{\alpha_3}p_\perp^{(1)}
-\frac{\alpha_1}{\alpha_3}p_\perp^{(2)}
=
\frac{\alpha_2 p_\perp^{(1)}-\alpha_1 p_\perp^{(2)}}{\alpha_1+\alpha_2}.
\end{equation}
This is already the correct lightcone matrix element in the mixed momentum/relative-position convention used in the note. To turn it into an actual computation from the discrete vertex, one may evaluate the oscillator overlap directly in any independent real nonzero-mode basis. Let $q_{\mathrm{phys}}^{(r)}$ denote such a basis on leg $r$, let
\begin{equation}
\label{eq:s12-1-006}
M_r \equiv (\mu_r\Omega_r)_{\mathrm{phys}},
\qquad
U_{r,\mathrm{phys}},\ \xi_{\mathrm{phys}}
\end{equation}
be the corresponding reduced overlap data, and write the tachyon oscillator wavefunction on each leg as
\begin{equation}
\label{eq:s12-1-007}
\psi_{0}^{(r)}(q_{\mathrm{phys}}^{(r)})
=
{\cal N}_{0,r}\,
\exp\!\left[-\frac12 q_{\mathrm{phys}}^{(r)T} M_r\, q_{\mathrm{phys}}^{(r)}\right].
\end{equation}
Here ``phys'' denotes any independent real basis for the nonzero-mode oscillators, such as the real sine/cosine basis; the final Schur complement $\gamma_T$ is basis-independent even though the explicit matrices $M_r$ and $U_{r,\mathrm{phys}}$ depend on that basis choice.
Using
\begin{equation}
\label{eq:s12-1-008}
q_{\mathrm{phys}}^{(3)}
=
U_{1,\mathrm{phys}}q_{\mathrm{phys}}^{(1)}
+U_{2,\mathrm{phys}}q_{\mathrm{phys}}^{(2)}
+\xi_{\mathrm{phys}}\,y,
\end{equation}
the three-tachyon matrix element becomes a finite-dimensional Gaussian integral. If one stacks the incoming oscillator variables into
\begin{equation}
\label{eq:s12-1-009}
Q\equiv
\begin{pmatrix}
q_{\mathrm{phys}}^{(1)}\\
q_{\mathrm{phys}}^{(2)}
\end{pmatrix},
\qquad
U_{\mathrm{phys}}\equiv
\begin{pmatrix}
U_{1,\mathrm{phys}} & U_{2,\mathrm{phys}}
\end{pmatrix},
\end{equation}
then, for one fixed transverse component $I$ (the full exponent is the sum over $\perpD$ identical copies, and $y$ below denotes that one component of the relative coordinate), the oscillator exponent takes the form
\begin{equation}
\label{eq:s12-1-010}
-\frac12 Q^T G_T\,Q
-y\, {\bf B}_T^T Q
-\frac12 C_T\, y^2,
\end{equation}
with
\begin{equation}
\label{eq:s12-1-011}
G_T
\equiv
\begin{pmatrix}
M_1 + U_{1,\mathrm{phys}}^T M_3 U_{1,\mathrm{phys}} &
U_{1,\mathrm{phys}}^T M_3 U_{2,\mathrm{phys}}\\
U_{2,\mathrm{phys}}^T M_3 U_{1,\mathrm{phys}} &
M_2 + U_{2,\mathrm{phys}}^T M_3 U_{2,\mathrm{phys}}
\end{pmatrix},
\end{equation}
\begin{equation}
\label{eq:s12-1-012}
{\bf B}_T
\equiv
\begin{pmatrix}
U_{1,\mathrm{phys}}^T M_3 \xi_{\mathrm{phys}}\\
U_{2,\mathrm{phys}}^T M_3 \xi_{\mathrm{phys}}
\end{pmatrix},
\qquad
C_T \equiv \xi_{\mathrm{phys}}^T M_3 \xi_{\mathrm{phys}}.
\end{equation}
Because the same oscillator matrix appears in every transverse direction, the Gaussian integration over $Q$ gives
\begin{equation}
\label{eq:s12-1-013}
{\cal A}_{TTT}^{\mathrm{lc}}(N)
=
\delta^{(\perpD)}\!\bigl(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)}\bigr)\,
{\cal K}_{TTT}(N,\alpha)\,
\int \dd^{\perpD}y\;
\exp\!\left[
\ii\,q_{\mathrm{rel}}\!\cdot y
-\frac12 \gamma_T(N,\alpha)\,y^2
\right],
\end{equation}
where
\begin{equation}
\gamma_T(N,\alpha)
\equiv
C_T - {\bf B}_T^T G_T^{-1} {\bf B}_T
\label{eq:gammaT}
\end{equation}
and ${\cal K}_{TTT}(N,\alpha)$ collects the determinant factor from $G_T$, the leg-by-leg ground-state normalizations, and the overall cubic normalization ${\cal C}_3^{(B)}$. The remaining $y$-integral is elementary:
\begin{equation}
\label{eq:s12-1-015}
{\cal A}_{TTT}^{\mathrm{lc}}(N)
=
\delta^{(\perpD)}\!\bigl(p_\perp^{(1)}+p_\perp^{(2)}-p_\perp^{(3)}\bigr)\,
\widetilde{\cal K}_{TTT}(N,\alpha)\,
\exp\!\left[
-\frac{q_{\mathrm{rel}}^2}{2\,\gamma_T(N,\alpha)}
\right].
\end{equation}
Comparing this result with the displaced squeezed-state form~\eqref{eq:V3B-squeezed}, one reads off
\begin{equation}
\label{eq:s12-1-016}
\Phi^{(B)}(y)=\gamma_T(N,\alpha)\,y^2,
\end{equation}
where in the full $\perpD$-dimensional amplitude $y^2\equiv y\cdot y$. Thus the scalar normal-ordering completion is precisely the Schur complement of the oscillator block $G_T$ with respect to the affine center-of-mass coupling.
If one factors out the still-undetermined cubic normalization as
\begin{equation}
\label{eq:s12-1-017}
\widetilde{\cal K}_{TTT}(N,\alpha)
=
{\cal C}_3^{(B)}\,\kappa_{1\mathrm d}(N,\alpha)^{\perpD},
\end{equation}
then the explicit one-direction prefactor coming from the three vacuum wavefunctions, the $Q$-Gaussian, and the $y$-Gaussian is
\begin{equation}
\label{eq:s12-1-018}
\kappa_{1\mathrm d}(N,\alpha)
=
\left(\prod_{r=1}^3 {\cal N}_{0,r}\right)
\frac{(2\pi)^{n_Q/2}}{\sqrt{\det G_T}}\,
\sqrt{\frac{2\pi}{\gamma_T(N,\alpha)}},
\qquad
n_Q\equiv (N_1-1)+(N_2-1).
\end{equation}
The determinant factor should be interpreted carefully. It is \emph{not} an extra primitive ingredient of the geometric overlap vertex in $\sigma$ position space. At that more basic level the cubic bosonic vertex is just the exact overlap constraint together with the zero-mode bookkeeping. The factor $(\det G_T)^{-1/2}$ appears only after one evaluates that overlap between the normalized transverse ground-state Gaussians, equivalently after projecting the displaced squeezed state~\eqref{eq:V3B-squeezed} onto the bosonic vacuum and performing the resulting finite-dimensional Gaussian integral over the nonzero oscillator coordinates. In that sense it is the finite-dimensional transverse vacuum/measure determinant associated with integrating out the constrained nonzero modes.
For on-shell closed-string tachyons with
\[
2p_r^+p_r^- - p_{\perp}^{(r)2} = -\frac{4}{\alpha'},
\qquad
p_1^-+p_2^-=p_3^-,
\]
the relative transverse momentum is fixed by the longitudinal data. Writing
\begin{equation}
\label{eq:s12-1-019}
p_r^-=\frac{p_\perp^{(r)2}-4/\alpha'}{2p_r^+},
\qquad
2p_r^+=\frac{\alpha_r}{\alpha'},
\end{equation}
and imposing
\begin{equation}
\label{eq:s12-1-020}
p_\perp^{(3)}=p_\perp^{(1)}+p_\perp^{(2)},
\qquad
p_1^-+p_2^-=p_3^-,
\end{equation}
one gets
\begin{equation}
\label{eq:s12-1-021}
\frac{p_\perp^{(1)2}-4/\alpha'}{\alpha_1}
\,+\,
\frac{p_\perp^{(2)2}-4/\alpha'}{\alpha_2}
\,-\,
\frac{(p_\perp^{(1)}+p_\perp^{(2)})^2-4/\alpha'}{\alpha_3}
=0,
\end{equation}
hence
\begin{equation}
\label{eq:s12-1-022}
2\,p_\perp^{(1)}\!\cdot p_\perp^{(2)}
=
\frac{4}{\alpha'}\left(
1-\frac{\alpha_1\alpha_2}{\alpha_3^2}
\right),
\end{equation}
so the invariant relative momentum
\begin{equation}
\label{eq:s12-1-023}
q_{\mathrm{rel}}^2
\equiv
\left(p_\perp^{(1)}-\frac{\alpha_1}{\alpha_3}p_\perp^{(3)}\right)^2
\end{equation}
is
\begin{equation}
\label{eq:s12-1-024}
q_{\mathrm{rel}}^2
=
\frac{4}{\alpha'}\left(
1-\frac{\alpha_1\alpha_2}{\alpha_3^2}
\right)
=
\frac{4}{\alpha'}\,
\frac{\alpha_1^2+\alpha_1\alpha_2+\alpha_2^2}{(\alpha_1+\alpha_2)^2}.
\end{equation}
So once $\gamma_T(N,\alpha)$ has been computed from the discrete overlap matrices, the full kinematic dependence of the three-tachyon matrix element is explicit.

Evaluating the reduced real-basis formulas above gives a direct finite-$N$ diagnostic. For the sample joins below I take a common lattice spacing, set $\alpha'=1$, identify $\alpha_r\propto N_r$, and use $\perpD=24$ when reporting the bare normalization diagnostic
\begin{equation}
\label{eq:s12-1-025}
\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}(N,\alpha)
\equiv
\frac{q_{\mathrm{rel}}^2}{2\,\gamma_T(N,\alpha)}
-\perpD\,\log \kappa_{1\mathrm d}(N,\alpha),
\end{equation}
which is the cubic normalization that would be needed to cancel the explicit kinematic factor if one ignored all additional external-state normalization conventions. The resulting values are
\begin{table}[t]
\centering
\begin{tabular}{c c c c c}
$(N_1,N_2)$ & $\gamma_T$ & $q_{\mathrm{rel}}^2$ & $q_{\mathrm{rel}}^2/(2\gamma_T)$ & $\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}$ \\
\hline
$(2,2)$ & $0.225079079$ & $3$ & $6.664324407$ & $-17.290367$ \\
$(4,4)$ & $0.279059526$ & $3$ & $5.375197253$ & $-12.287772$ \\
$(8,16)$ & $0.316197530$ & $28/9$ & $4.919568963$ & $-3.961048$
\end{tabular}
\caption{Sample bosonic three-tachyon data computed directly from the discrete cubic overlap in an independent real nonzero-mode basis. In the same runs the overlap sanity checks $\|U_r^TU_r-I\|_\infty$ and $\|U_1U_1^T+U_2U_2^T+\widehat\xi\,\widehat\xi^T-I\|_\infty$ are at the level of $10^{-14}$ or smaller. The last column is only a bare diagnostic: it omits the still-unfixed operator-level normalization and the conventional external-state normalization factors.}
\label{tab:ttt-samples}
\end{table}
These numbers come from the exact finite-dimensional Gaussian integrals; no continuum approximation is being used at this stage. They show that the kinematic overlap by itself already produces a nontrivial $\alpha_r$-dependent scalar factor at finite $N$. They also show that before the operator-level Lorentz normalization and the conventional external-state factors are supplied, the bare normalization required to turn the amplitude into a constant is strongly $N$- and ratio-dependent.

A stronger structural statement is available if one asks whether the remaining scalar factor contains any \emph{irreducible} dependence on the ordered triple $(N_1,N_2,N_3)$. On a dense finite-$N$ grid extending all the way to
\begin{equation}
\label{eq:s12-1-026}
4\le N_1,N_2\le 60,
\qquad
N_3=N_1+N_2\le 120,
\end{equation}
comprising $3249$ sampled joins, the exact Gaussian data fit
\begin{equation}
\label{eq:s12-1-027}
\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}(N_1,N_2)
=
f_{\mathrm{in}}(N_1)+f_{\mathrm{in}}(N_2)+f_{\mathrm{out}}(N_3)
+\delta_{\mathrm{fact}}(N_1,N_2)
\end{equation}
with root-mean-square residual
\begin{equation}
\label{eq:s12-1-028}
\sqrt{\bigl\langle \delta_{\mathrm{fact}}^2\bigr\rangle}
=1.5\times 10^{-9},
\end{equation}
and maximum absolute residual below
\begin{equation}
\label{eq:s12-1-029}
\max |\delta_{\mathrm{fact}}| < 2.3\times 10^{-8}.
\end{equation}
Equivalently, to numerical precision on that grid,
\begin{equation}
\label{eq:s12-1-030}
{\cal C}^{(B)}_{3,\mathrm{req,bare}}(N_1,N_2)
=
Z_{\mathrm{in}}(N_1)\,Z_{\mathrm{in}}(N_2)\,Z_{\mathrm{out}}(N_3),
\end{equation}
for suitable one-string factors $Z_{\mathrm{in}}$ and $Z_{\mathrm{out}}$.
The existence of such a factorization is the invariant statement. The individual functions are not unique: in logarithmic form one may shift
\begin{equation}
\label{eq:s12-1-031}
f_{\mathrm{in}}(N)\mapsto f_{\mathrm{in}}(N)+aN+b,
\qquad
f_{\mathrm{out}}(N)\mapsto f_{\mathrm{out}}(N)-aN-2b,
\end{equation}
without changing the full three-leg combination. A canonical gauge choice is useful for printing representative tables in the diagnostic script, but it carries no direct physical meaning by itself.

Even with that caveat, the large-$N$ tail of the one-string factors contains meaningful information because the allowed redefinition changes only the linear and constant pieces. On two independent grids,
\begin{equation}
\label{eq:s12-1-032}
4\le N_1,N_2\le 60,\ N_3\le 120,
\qquad
4\le N_1,N_2\le 80,\ N_3\le 160,
\end{equation}
the same canonical gauge-fixed representative is fit extremely accurately by
\begin{equation}
\label{eq:s12-1-033}
\begin{aligned}
f_{\mathrm{in}}(N)
&=
-\lambda_{\mathrm{gauge}}\,N
+7\log N
+\frac{\pi}{N}
+\frac{0.13707\ldots}{N^2}
+c_{\mathrm{in}}
+O(N^{-3}),\\[3pt]
f_{\mathrm{out}}(N)
&=
\lambda_{\mathrm{gauge}}\,N
-5\log N
-\frac{\pi}{N}
+\frac{0.13707\ldots}{N^2}
+c_{\mathrm{out}}
+O(N^{-3}),
\end{aligned}
\end{equation}
with tail-fit residuals at the level of $10^{-11}$ or smaller on the outgoing side and $10^{-13}$ or smaller on the incoming side. Here $\lambda_{\mathrm{gauge}}$ and the constants $c_{\mathrm{in}},c_{\mathrm{out}}$ are convention-dependent, but the logarithmic and inverse-power coefficients are not. In particular, the data are numerically consistent with the simple gauge-invariant values
\begin{equation}
\label{eq:s12-1-034}
7\ \text{(incoming $\log N$)},\qquad
-5\ \text{(outgoing $\log N$)},\qquad
\pm\pi\ \text{($1/N$)},\qquad
\frac{\pi^2}{72}\ \text{($1/N^2$)}
\end{equation}
for the $\log N$, $1/N$, and $1/N^2$ terms. In fact, if one fixes those non-linear coefficients by hand and then allows only the expected gauge-dependent constant and linear pieces to vary, the residuals remain at the same tiny level: on the `60/120` grid they are about $1.3\times 10^{-11}$ for the incoming leg and $4.4\times 10^{-11}$ for the outgoing leg, and on the `80/160` grid they drop to about $1.9\times 10^{-12}$ and $1.3\times 10^{-11}$ respectively. So the unresolved operator-level normalization problem is now sharper than before: the commutator analysis must reproduce not merely the existence of one-string factors, but this specific non-linear large-$N$ tail.

Because the allowed linear redefinition cancels identically in the full three-leg combination once $N_3=N_1+N_2$ is imposed, the same data imply a direct gauge-invariant asymptotic formula for the full amplitude-level normalization diagnostic:
\begin{equation}
\label{eq:s12-1-035}
\begin{aligned}
\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}(N_1,N_2)
&=
{\cal C}_{\mathrm{tail}}
+7\log N_1+7\log N_2-5\log N_3\\
&\quad
+\pi\!\left(\frac1{N_1}+\frac1{N_2}-\frac1{N_3}\right)
+\frac{\pi^2}{72}\!\left(\frac1{N_1^2}+\frac1{N_2^2}+\frac1{N_3^2}\right)
+O(N^{-3}) .
\end{aligned}
\end{equation}
with one overall constant ${\cal C}_{\mathrm{tail}}$. Fitting only that single constant gives root-mean-square residuals of about $2.0\times 10^{-7}$ on the `60/120` grid, $1.7\times 10^{-7}$ on the `80/160` grid, and $1.5\times 10^{-7}$ on the `100/200` grid, with worst-case residuals around $10^{-6}$. So the observed large-$N$ structure is not merely legwise; it is already visible directly in the full gauge-invariant three-point scalar factor.
Equivalently, at fixed physical circumferences $\alpha_r=aN_r$, the same fit reads
\begin{equation}
\label{eq:s12-1-036}
\begin{aligned}
\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}
&=
{\cal C}_{\mathrm{tail}}
-9\log a
+7\log \alpha_1
+7\log \alpha_2
-5\log \alpha_3\\
&\quad
+\pi a\!\left(\frac1{\alpha_1}+\frac1{\alpha_2}-\frac1{\alpha_3}\right)
+\frac{\pi^2 a^2}{72}\!\left(\frac1{\alpha_1^2}+\frac1{\alpha_2^2}+\frac1{\alpha_3^2}\right)
+O(a^3).
\end{aligned}
\end{equation}
So the leading bare lattice normalization suggested by the explicit three-tachyon data is
\begin{equation}
\label{eq:s12-1-037}
{\cal C}^{(B)}_{3,\mathrm{req,bare}}
\sim
e^{{\cal C}_{\mathrm{tail}}}\,
a^{-9}\,
\alpha_1^7\alpha_2^7\alpha_3^{-5},
\qquad
e^{{\cal C}_{\mathrm{tail}}}\approx 1.70\times 10^{-10},
\end{equation}
before the still-separate conventional external-state normalization is restored. This does not yet derive the continuum normalization from the Poincare algebra, but it turns that missing derivation into a very concrete target.

There is also a sharper critical-dimension statement hiding in the same data. If one keeps the transverse multiplicity $\perpD$ as a formal parameter in
\begin{equation}
\label{eq:s12-1-038}
\log {\cal C}^{(B)}_{3,\mathrm{req,bare}}=\frac{q_{\mathrm{rel}}^2}{2\gamma_T}-\perpD\log \kappa_{1\mathrm d},
\end{equation}
and repeats the exact factorization test on the same $3249$-join grid, the irreducible three-body obstruction vanishes only at
\begin{equation}
\label{eq:s12-1-039}
\perpD=24
\qquad
(\text{equivalently }D=26).
\end{equation}
Numerically, the root-mean-square factorization residual is
\begin{equation}
\label{eq:s12-1-040}
\begin{array}{c|ccccc}
\perpD & 22 & 23 & 24 & 25 & 26 \\
\hline
\mathrm{RMS}(\delta_{\mathrm{fact}})
& 1.08\times 10^{-3}
& 5.42\times 10^{-4}
& 1.48\times 10^{-9}
& 5.42\times 10^{-4}
& 1.08\times 10^{-3}
\end{array}
\end{equation}
with the maximum residual showing the same symmetric minimum at $\perpD=24$. So the amplitude-level cancellation is not generic: the non-factorizable part of the Gaussian exponent is cancelled precisely by $24$ copies of the one-direction prefactor contribution. This is an explicit finite-$N$ three-tachyon signal of the critical bosonic dimension.
That cancellation is highly nontrivial. On the same $3249$-join grid at $\perpD=24$, the two pieces
\begin{equation}
\label{eq:s12-1-041}
\frac{q_{\mathrm{rel}}^2}{2\gamma_T},
\qquad
\log \kappa_{1\mathrm d}
\end{equation}
are \emph{separately} not leg-factorizable: their own factorization residuals are
\begin{equation}
\label{eq:s12-1-042}
\mathrm{RMS}\!\left(\delta_{\mathrm{fact}}^{\mathrm{exp}}\right)=1.30\times 10^{-2},
\qquad
\mathrm{RMS}\!\left(\delta_{\mathrm{fact}}^{\kappa}\right)=5.42\times 10^{-4}.
\end{equation}
Only in the combination
\begin{equation}
\label{eq:s12-1-043}
\delta_{\mathrm{fact}}^{\mathrm{exp}}-\perpD\,\delta_{\mathrm{fact}}^{\kappa}
\end{equation}
do they collapse to the quoted
\begin{equation}
\label{eq:s12-1-044}
1.48\times 10^{-9}
\end{equation}
level. So the observed factorization at $\perpD=24$ is not a trivial property of one ingredient of the Gaussian formula; it comes from a delicate cancellation between the oscillator-exponent and determinant/vacuum-normalization pieces.

It is worth stressing what this does and does not mean conceptually. The appearance of the critical bosonic dimension already in the scalar three-tachyon matrix element is not as surprising as it may first seem, because the relevant $\perpD$-dependence is carried by the \emph{number of transverse oscillator directions} entering the determinant/zero-point part of the cubic vertex, not by spacetime spin. That counting is present even for tachyon external states. In more standard lightcone language, the same underlying anomaly data that control the normal-ordering constant and the closure of the Lorentz generators can already leak into the scalar cubic coupling through the vacuum/measure factors. What the present test shows is therefore a genuine amplitude-level signal of $D=26$, but not yet a complete proof of Lorentz invariance: spinning states and the operator-level commutator remain necessary to verify the full tensorial structure and the exact Poincare-algebra closure.

This is a much sharper statement than the earlier coarse power-law fits. At the level of the explicit discrete cubic vertex, the bosonic three-tachyon amplitude shows \emph{no irreducible three-body momentum dependence at all}: the entire nonconstant factor is already a product of one-string renormalizations for the two incoming legs and the outgoing leg. In that restricted scalar-amplitude sense, the discrete vertex has passed the three-tachyon factorization diagnostic, but it has \emph{not} yet passed the full operator-level Lorentz test.

What remains unresolved is not the existence of a three-body obstruction, but the principled derivation of the functions $Z_{\mathrm{in}}$, $Z_{\mathrm{out}}$, and the overall constant normalization from the operator-level computation of $[J^{-I}_2,P^-_3]+[J^{-I}_3,P^-_2]$ together with the standard external-state normalization convention. That derivation is still needed to connect the explicit amplitude-level factorization found here to the full lightcone Poincare-algebra closure argument.
There is, however, now a direct analytic continuum target for the kinematic Schur complement itself. In the positive-width outgoing convention $\alpha_3=\alpha_1+\alpha_2>0$, the standard closed-string lightcone cubic exponent is governed by
\begin{equation}
\label{eq:s12-1-045}
\tau_0(\alpha_1,\alpha_2,\alpha_3)
=
\alpha_1\log \alpha_1+\alpha_2\log \alpha_2-\alpha_3\log \alpha_3,
\qquad
\gamma_T^{\mathrm{cont}}
=
-\frac{\alpha_1\alpha_2}{\alpha_3\,\tau_0}.
\end{equation}
The dedicated benchmark helper \texttt{continuum\_tachyon\_benchmark.py} compares fixed-ratio Richardson extrapolations of the discrete $\gamma_T$ against this analytic target on the families $1\!:\!3$, $1\!:\!2$, $3\!:\!5$, $2\!:\!3$, and $1\!:\!1$ with scales $8,16,32,64,128,256$. The agreement is already quantitative:
\begin{equation}
\label{eq:s12-1-046}
\max_{\lambda\in\{1/4,1/3,3/8,2/5,1/2\}}
\bigl|\gamma_T^{(\infty)}(\lambda)-\gamma_T^{\mathrm{cont}}(\lambda)\bigr|
=1.94\times 10^{-5},
\qquad
\max
\frac{\bigl|\gamma_T^{(\infty)}-\gamma_T^{\mathrm{cont}}\bigr|}{\gamma_T^{\mathrm{cont}}}
=5.37\times 10^{-5}.
\end{equation}
There is now also a useful on-shell factor split. In the same positive-width outgoing convention, the continuum cubic prefactor $\mu(\alpha_1,\alpha_2,\alpha_3)^2$ obeys
\begin{equation}
\label{eq:s12-1-046a}
\log \mu(\alpha_1,\alpha_2,\alpha_3)^2
=
\frac{q_{\mathrm{rel}}^2}{2\gamma_T^{\mathrm{cont}}},
\end{equation}
so the already-tested Schur complement controls the full continuum on-shell exponential. The helper \texttt{continuum\_tachyon\_factor\_split.py} verifies both this continuum identity and the corresponding discrete Richardson limit on the same family set:
\begin{equation}
\label{eq:s12-1-046b}
\max
\left|
\frac{q_{\mathrm{rel}}^2}{2\gamma_T^{\mathrm{cont}}}
-\log\mu^2
\right|
=8.88\times 10^{-16},
\qquad
\max
\left|
\frac{q_{\mathrm{rel}}^2}{2\gamma_T^{(\infty)}}
-\log\mu^2
\right|
=1.01\times 10^{-6},
\end{equation}
with maximum relative error $2.42\times 10^{-7}$ in the second comparison. So the bosonic three-tachyon sector now has both an internal factorization test and a direct continuum match not only for $\gamma_T$ itself but also for the full on-shell Mandelstam exponential. The still-open normalization problem is therefore isolated even more narrowly to the remaining overall cubic scalar factor rather than the reduced Gaussian kinematics.

\subsection{Two-tachyon / one-massless diagnostic}
A second bosonic amplitude-level diagnostic, already visible before the operator commutator is completed, is the matrix element with two incoming tachyons and one outgoing first-level massless bosonic state on leg $3$. This is \emph{not} the GS graviton discussion of Section~15.1 below; here the external state is the first oscillator excitation of the \emph{bosonic} closed string. The value of this check is that it sharpens the external-state normalization in a way the earlier branch note did not: the discrete first-harmonic insertion can be fixed exactly in the same finite-$N$ conventions already used for the three-tachyon amplitude.

For one free bosonic leg with $N$ sites, define the boundary Fourier coefficients
\begin{equation}
\label{eq:s12-2-001}
X_m \equiv \frac{q_m}{\sqrt N}
=
\frac{1}{N}\sum_{n=0}^{N-1} X_n\,e^{-2\pi \ii mn/N},
\qquad
m=1,\dots,N-1.
\end{equation}
These are just the nonzero Fourier modes already introduced earlier, rewritten with the normalization used in the older branch note. The one-string ground-state wavefunction in an independent real nonzero-mode basis is
\begin{equation}
\label{eq:s12-2-002}
\psi_0(q_{\mathrm{phys}})
=
{\cal N}_0\,
\exp\!\left[-\frac12 q_{\mathrm{phys}}^T M\,q_{\mathrm{phys}}\right],
\qquad
M=(\mu\Omega)_{\mathrm{phys}}.
\end{equation}
Because external-state normalization uses the product of bra and ket wavefunctions, the vacuum two-point function is \emph{half} the inverse of the one-wavefunction quadratic form. For the first boundary harmonic one therefore gets
\begin{equation}
\label{eq:s12-2-003}
\begin{aligned}
C_{1,N}
&\equiv
\frac{\int \dd q_{\mathrm{phys}}\;
\psi_0(q_{\mathrm{phys}})
\,X_1 X_{-1}\,
\psi_0(q_{\mathrm{phys}})}
{\int \dd q_{\mathrm{phys}}\;
\psi_0(q_{\mathrm{phys}})^2}\\
&=
\frac{1}{2N\,\mu\omega_1}
=
\frac{\pi\alpha'}{2N\sin(\pi/N)}.
\end{aligned}
\end{equation}
Here $\mu=a/(2\pi\alpha')$ and $\omega_1=(2/a)\sin(\pi/N)$, so the common lattice spacing cancels exactly. The local diagnostic \texttt{bosonic\_massless\_check.py} verifies this formula directly in the same real basis used by \texttt{tachyon\_check.py}, with agreement at the $10^{-16}$ level for the sample sizes $N=4,8,16,32,64,128$.

This fixes the outgoing first-level tensor insertion uniquely:
\begin{equation}
{\cal O}_{1,N}^{IJ}
\equiv
C_{1,N}^{-1}\Bigl(X_1^I X_{-1}^J - C_{1,N}\delta^{IJ}\Bigr).
\label{eq:massless-normalized-operator}
\end{equation}
Equivalently, the coordinate-space wavefunction of the state
$a_1^{I\dagger}a_{N-1}^{J\dagger}|0;p\rangle$
is ${\cal O}_{1,N}^{IJ}\psi_0$. Symmetric traceless, antisymmetric, and trace projections of the $IJ$ indices give the graviton, $B$-field, and dilaton channels of the bosonic closed string respectively. For the present diagnostic only the raw tensor form~\eqref{eq:massless-normalized-operator} is needed.

Now place this insertion on the outgoing leg $3$ while keeping tachyon vacua on the incoming legs. In the same reduced real-basis notation used in the three-tachyon calculation, let
\begin{equation}
\label{eq:s12-2-005}
Q\equiv
\begin{pmatrix}
q_{\mathrm{phys}}^{(1)}\\
q_{\mathrm{phys}}^{(2)}
\end{pmatrix},
\qquad
q_{\mathrm{phys}}^{(3)}
=
U_{1,\mathrm{phys}}q_{\mathrm{phys}}^{(1)}
+U_{2,\mathrm{phys}}q_{\mathrm{phys}}^{(2)}
+\xi_{\mathrm{phys}}\,y,
\end{equation}
and let $r_\pm$ be the rows extracting $X_{\pm1}^{(3)}$ from $q_{\mathrm{phys}}^{(3)}$, so that
\begin{equation}
\label{eq:s12-2-006}
X_{\pm1}^{(3)} = r_\pm q_{\mathrm{phys}}^{(3)}
=
L_\pm Q + \zeta_\pm y,
\qquad
L_\pm \equiv \bigl(r_\pm U_{1,\mathrm{phys}},\,r_\pm U_{2,\mathrm{phys}}\bigr),
\qquad
\zeta_\pm \equiv r_\pm \xi_{\mathrm{phys}}.
\end{equation}
The Gaussian in $Q$ is the same one that already appeared in the three-tachyon matrix element,
\begin{equation}
\label{eq:s12-2-007}
-\frac12 Q^T G_T\,Q
- y\,{\bf B}_T^T Q
-\frac12 C_T\,y^2,
\qquad
\gamma_T=C_T-{\bf B}_T^T G_T^{-1}{\bf B}_T,
\end{equation}
so at fixed $y$ the outgoing first-harmonic bilinear reduces to
\begin{equation}
\label{eq:s12-2-008}
\frac{\bigl\langle X_1^{(3)I}X_{-1}^{(3)J}\bigr\rangle_y}
{\langle 1\rangle_y}
=
\delta^{IJ}\Sigma_1
+\mu_+\mu_-\,y^I y^J,
\end{equation}
with
\begin{equation}
\label{eq:s12-2-009}
\Sigma_1 \equiv L_+G_T^{-1}L_-^T,
\qquad
\mu_\pm \equiv \zeta_\pm - L_\pm G_T^{-1}{\bf B}_T.
\end{equation}
No antisymmetric tensor appears at this stage: the covariance term is proportional to $\delta^{IJ}$, and the only one-point source is along the relative displacement vector $y$.

Inserting the normalized operator~\eqref{eq:massless-normalized-operator} therefore gives
\begin{equation}
\label{eq:s12-2-010}
\frac{\bigl\langle {\cal O}_{1,N_3}^{IJ}\bigr\rangle_y}
{\langle 1\rangle_y}
=
\frac{\Sigma_1-C_{1,N_3}}{C_{1,N_3}}\,\delta^{IJ}
+
\frac{\mu_+\mu_-}{C_{1,N_3}}\,y^I y^J.
\end{equation}
Fourier transforming the relative displacement to the relative transverse momentum $q_{\mathrm{rel}}$ then yields the exact finite-$N$ tensor decomposition
\begin{equation}
\label{eq:s12-2-011}
{\cal A}_{TTM}^{IJ,\mathrm{lc}}(N)
=
{\cal A}^{(B)}_{\mathrm{vac}}(N;q_{\mathrm{rel}})
\left[
A_{\mathrm{tr}}^{(M)}(N,\alpha)\,\delta^{IJ}
-B_{\mathrm{rel}}^{(M)}(N,\alpha)\,
q_{\mathrm{rel}}^I q_{\mathrm{rel}}^J
\right],
\end{equation}
with
\begin{equation}
A_{\mathrm{tr}}^{(M)}
=
\frac{\Sigma_1-C_{1,N_3}}{C_{1,N_3}}
+
\frac{\mu_+\mu_-}{C_{1,N_3}\gamma_T},
\qquad
B_{\mathrm{rel}}^{(M)}
=
\frac{\mu_+\mu_-}{C_{1,N_3}\gamma_T^2}.
\label{eq:ttm-bosonic-coefficients}
\end{equation}
So the whole bosonic $2T+1M$ matrix element is again reduced to explicit finite-dimensional Gaussian data, with the external-state normalization fixed exactly rather than guessed.

The on-shell kinematics is also cleaner than in the three-tachyon case. Writing
\begin{equation}
\label{eq:s12-2-013}
p_\perp^{(1)}=\frac{\alpha_1}{\alpha_3}p_\perp^{(3)}+q_{\mathrm{rel}},
\qquad
p_\perp^{(2)}=\frac{\alpha_2}{\alpha_3}p_\perp^{(3)}-q_{\mathrm{rel}},
\end{equation}
and imposing
\begin{equation}
\label{eq:s12-2-014}
2p_1^+p_1^- - p_\perp^{(1)2}
=
2p_2^+p_2^- - p_\perp^{(2)2}
=
-\frac{4}{\alpha'},
\qquad
2p_3^+p_3^- - p_\perp^{(3)2}=0,
\end{equation}
one finds
\begin{equation}
\label{eq:s12-2-014a}
\frac{p_\perp^{(1)2}-4/\alpha'}{\alpha_1}
\,+\,
\frac{p_\perp^{(2)2}-4/\alpha'}{\alpha_2}
\,-\,
\frac{p_\perp^{(3)2}}{\alpha_3}
=0,
\end{equation}
and substituting~\eqref{eq:s12-2-013} gives
\begin{equation}
\label{eq:s12-2-014b}
\frac{p_\perp^{(1)2}}{\alpha_1}
\,+\,
\frac{p_\perp^{(2)2}}{\alpha_2}
\,-\,
\frac{p_\perp^{(3)2}}{\alpha_3}
=
\left(\frac{1}{\alpha_1}+\frac{1}{\alpha_2}\right)q_{\mathrm{rel}}^2,
\end{equation}
because the cross terms proportional to $p_\perp^{(3)}\!\cdot q_{\mathrm{rel}}$ cancel exactly and
\begin{equation}
\label{eq:s12-2-014c}
\frac{\alpha_1}{\alpha_3^2}+\frac{\alpha_2}{\alpha_3^2}
=
\frac{1}{\alpha_3}
\end{equation}
when $\alpha_3=\alpha_1+\alpha_2$. Combining~\eqref{eq:s12-2-014a} and~\eqref{eq:s12-2-014b} therefore gives
\begin{equation}
\label{eq:s12-2-014d}
\left(\frac{1}{\alpha_1}+\frac{1}{\alpha_2}\right)
\left(q_{\mathrm{rel}}^2-\frac{4}{\alpha'}\right)=0,
\end{equation}
and hence
\begin{equation}
\label{eq:s12-2-015}
q_{\mathrm{rel}}^2=\frac{4}{\alpha'}.
\end{equation}
So unlike the three-tachyon case, the magnitude of the relative transverse momentum is independent of the ratio $\alpha_1/\alpha_3$. For a symmetric polarization tensor $e_{IJ}$ transverse to the outgoing massless momentum, $e_{IJ}p_\perp^{(3)J}=0$, one also has
\begin{equation}
\label{eq:s12-2-016}
e_{IJ}q_{\mathrm{rel}}^I q_{\mathrm{rel}}^J
=
\frac14\,
e_{IJ}
\bigl(p_\perp^{(1)}-p_\perp^{(2)}\bigr)^I
\bigl(p_\perp^{(1)}-p_\perp^{(2)}\bigr)^J,
\end{equation}
which is exactly the expected bosonic $2T+1M$ tensor structure. Thus the discrete calculation already isolates the right continuum covariant tensor, up to the same overall cubic normalization issue that remains from the bosonic Lorentz commutator.

Numerically, the same diagnostic script shows that the trace piece in~\eqref{eq:ttm-bosonic-coefficients} is strongly suppressed while the momentum-bilinear coefficient approaches a nonzero continuum limit. On the fixed-ratio family $N_1:N_2=2:3$ with $\alpha'=1$ one finds
\begin{equation}
\label{eq:s12-2-017}
\begin{array}{c|cccc}
(N_1,N_2) & (16,24) & (32,48) & (64,96) & (128,192) \\
\hline
A_{\mathrm{tr}}^{(M)}
& 3.62\times 10^{-2}
& 1.81\times 10^{-2}
& 9.05\times 10^{-3}
& 4.53\times 10^{-3}\\
B_{\mathrm{rel}}^{(M)}
& 2.08
& 2.00
& 1.96
& 1.94
\end{array}
\end{equation}
and a simple least-squares fit gives
\begin{equation}
\label{eq:s12-2-018}
A_{\mathrm{tr}}^{(M)}\approx \frac{0.5797}{N_1},
\qquad
B_{\mathrm{rel}}^{(M)}\approx 1.9203 + \frac{2.5044}{N_1}.
\end{equation}
At $(N_1,N_2)=(128,192)$ the smallness of the trace part already comes from a delicate cancellation:
\begin{equation}
\label{eq:s12-2-019}
\frac{\Sigma_1-C_{1,N_3}}{C_{1,N_3}}\approx -0.68227,
\qquad
\frac{\mu_+\mu_-}{C_{1,N_3}\gamma_T}\approx 0.68680,
\qquad
A_{\mathrm{tr}}^{(M)}\approx 4.53\times 10^{-3}.
\end{equation}
So the branch note's observation that the trace part ``works'' survives in the cleaner main-note conventions, but only after the external-state normalization is fixed exactly by $C_{1,N}$.

The ratio dependence is also smooth. At lattice sizes $(N_1,N_2)=(128a,128b)$ with
\begin{equation}
\label{eq:s12-2-020}
\lambda\equiv \frac{\alpha_1}{\alpha_3}\approx \frac{a}{a+b}
=
\frac14,\ \frac13,\ \frac38,\ \frac25,\ \frac12,
\end{equation}
the same diagnostic gives
\begin{equation}
\label{eq:s12-2-021}
B_{\mathrm{rel}}^{(M)}
\approx
1.55,\ 1.80,\ 1.88,\ 1.93,\ 2.02,
\end{equation}
again with a smooth $\lambda$-dependence. This does \emph{not} replace the missing operator-level bosonic Lorentz computation: the overall cubic normalization and its principled derivation from $[J^{-I}_2,P^-_3]+[J^{-I}_3,P^-_2]$ are still absent. But it does add a second explicit bosonic amplitude-level diagnostic to the note, and more importantly it fixes the first-harmonic massless normalization unambiguously in the finite-$N$ conventions actually used by the discrete vertex.

\section{Fermionic kinematic overlap}
The fermionic part should be treated in complete parallel with the bosons. Let $\theta^{(r)}$ denote the GS worldsheet fermions on leg $r$ in $\sigma$ position space. The full-boundary overlap gives
\begin{equation}
\label{eq:s13-001}
\theta^{(3)} = P_1 \theta^{(1)} + P_2 \theta^{(2)},
\end{equation}
including the two unfolded-strip representatives $\theta_{I_+}$ and $\theta_{I_-}$ discussed above. In a coherent-state basis, the kinematic fermionic vertex is therefore the Grassmann delta functional
\begin{equation}
\label{eq:s13-002}
\langle \bar\theta^{(1)},\bar\theta^{(2)},\bar\theta^{(3)} | V^{(F)}_{\mathrm{kin}} \rangle
\propto
\delta\!\left(\bar\theta^{(3)}-\bar\theta^{(1)}P_1^T-\bar\theta^{(2)}P_2^T\right).
\end{equation}
Here $\bar\theta^{(r)}$ denotes the bra-side coherent-state Grassmann eigenvalue on leg $r$, written as a row vector. It is not a Dirac or complex conjugate. The transposes on $P_1$ and $P_2$ appear because the overlap acts from the left on these bra variables.

Removing the average mode and transforming to nonzero Fourier modes gives
\begin{equation}
\label{eq:s13-003}
\vartheta^{(3)} = U_1 \vartheta^{(1)} + U_2 \vartheta^{(2)} + \xi\,\upsilon,
\qquad
\upsilon\equiv \theta_{\mathrm{av}}^{(1)}-\theta_{\mathrm{av}}^{(2)},
\end{equation}
with the same overlap matrices $U_r=\widehat F_3P_r\widehat F_r^\dagger$ and affine vector $\xi$ as in the bosonic sector. In a coherent-state oscillator basis this becomes a displaced fermionic squeezed state. Let $b_m^{(r)}$ denote the nonzero-mode fermionic oscillator/coherent-state variables, normalized by
\begin{equation}
\label{eq:s13-004}
\{b_m^{(r)},b_n^{(s)\dagger}\}=\delta^{rs}\delta_{mn},
\qquad
\{b_m^{(r)},b_n^{(s)}\}=0,
\end{equation}
with $m=1,\dots,N_r-1$ on leg $r$. These are the fermionic counterparts of the bosonic oscillators $a_m^{(r)}$: they are the coherent-state variables attached to the nonzero Fourier modes, and the Majorana bookkeeping variables $(\vartheta,\pi_\vartheta)$ introduced next are linear combinations of them.
After shifting away the affine zero-mode source, one may write the homogeneous part in terms of these oscillator variables as
\begin{equation}
\label{eq:s13-005}
b^{(3)} = U_1 b^{(1)} + U_2 b^{(2)},
\end{equation}
or, in a Majorana-type bookkeeping basis for the real nonzero fermionic modes,
\begin{equation}
\label{eq:s13-006}
\vartheta_m^{(r)}=\frac{b_m^{(r)}+b_{N_r-m}^{(r)\dagger}}{\sqrt2},
\qquad
\pi_{\vartheta,m}^{(r)}=\frac{b_m^{(r)}-b_{N_r-m}^{(r)\dagger}}{\mathrm{i}\sqrt2},
\end{equation}
where the same letter $\vartheta_m^{(r)}$ is now being used for the corresponding Fock-space operator rather than the classical Fourier coefficient. This is the standard coherent-state abuse of notation, but it is worth keeping in mind: before quantization $\vartheta_m$ is a Grassmann mode label, whereas here it is the operator built from $b_m$ and $b_{N_r-m}^\dagger$.
These operators satisfy the anticommutators
\begin{equation}
\label{eq:s13-007}
\bigl\{\vartheta_m^{(r)},\vartheta_n^{(s)}\bigr\}
=
\delta^{rs}\delta_{m,N_r-n},
\qquad
\bigl\{\pi_{\vartheta,m}^{(r)},\pi_{\vartheta,n}^{(s)}\bigr\}
=
\delta^{rs}\delta_{m,N_r-n},
\qquad
\bigl\{\vartheta_m^{(r)},\pi_{\vartheta,n}^{(s)}\bigr\}=0.
\end{equation}
Thus $(\vartheta,\pi_\vartheta)$ are a convenient full-spectrum Majorana bookkeeping basis, but not a canonical pair in that redundant basis. As in the bosonic sector, the actual squeezed-state construction should therefore be performed only after restricting to an independent half-spectrum or an equivalent real basis of physical fermionic oscillators.
Then the fermionic overlap matrices are explicitly
\begin{equation}
\label{eq:s13-008}
C_{\Theta}=
\begin{pmatrix}
U_1 & U_2 & -I
\end{pmatrix},
\qquad
C_{\Pi_{\Theta}}=
\begin{pmatrix}
I & 0 & -U_1^\dagger\\
0 & I & -U_2^\dagger
\end{pmatrix},
\end{equation}
where, as in the bosonic sector, each identity block $I$ is the identity on the nonzero-mode space of the corresponding leg. Therefore
\begin{equation}
\label{eq:s13-009}
\mathbb M_F=
\begin{pmatrix}
C_{\Theta}\\
-\mathrm{i}C_{\Pi_{\Theta}}
\end{pmatrix},
\qquad
\mathbb N_F=
\begin{pmatrix}
C_{\Theta}\\
\mathrm{i}C_{\Pi_{\Theta}}
\end{pmatrix}.
\end{equation}
This is the fermionic analogue of the bosonic overlap system, without the frequency factors $(\mu\Omega)^{\pm1/2}$ because the GS fermions are first order rather than second order in worldsheet time. Let $B_{\mathrm{phys}}$ denote an independent fermionic oscillator basis obtained from the full complexified nonzero modes by imposing the involution or, equivalently, by passing to a real half-spectrum basis. Concretely, $B_{\mathrm{phys}}$ may be chosen exactly as in the bosonic half-spectrum reduction: one representative from each pair $(m,N_r-m)$ on every leg, together with a separate real Nyquist fermion when $N_r$ is even. Let $\mathbb M_{F,\mathrm{phys}}$, $\mathbb N_{F,\mathrm{phys}}$ be the corresponding reduced overlap matrices. Then the kinematic overlap state solves linear constraints of the form
\begin{equation}
\label{eq:s13-010}
(\mathbb M_{F,\mathrm{phys}} B_{\mathrm{phys}} + \mathbb N_{F,\mathrm{phys}} B_{\mathrm{phys}}^\dagger)\,|V^{(F)}_{\mathrm{kin}}\rangle = 0,
\end{equation}
and one may package the solution only as a \emph{formal} Grassmann squeezed-state shorthand,
\begin{equation}
\label{eq:s13-011}
|V^{(F)}_{\mathrm{kin}}\rangle
=
{\cal C}_3^{(F)}
\exp\!\left[
\frac12 B_{\mathrm{phys}}^{\dagger T}S^{(F)} B_{\mathrm{phys}}^\dagger
\right]|0\rangle,
\qquad
S^{(F)} = -\mathbb M_{F,\mathrm{phys}}^{-1}\mathbb N_{F,\mathrm{phys}}.
\end{equation}
For an ordinary finite-dimensional Grassmann squeezed state one would require $S^{(F)}$ to be antisymmetric, $S^{(F)T}=-S^{(F)}$, because the creation operators anticommute and the quadratic Grassmann exponent is proportional to $B_m^\dagger B_n^\dagger$.
Equivalently,
\begin{equation}
\label{eq:s13-011a}
\mathbb M_{F,\mathrm{phys}}\mathbb N_{F,\mathrm{phys}}^T
+\mathbb N_{F,\mathrm{phys}}\mathbb M_{F,\mathrm{phys}}^T
=0.
\end{equation}
Already before reducing to a half-spectrum basis, however, the explicit overlap blocks give
\begin{equation}
\label{eq:s13-011b}
\mathbb M_F\mathbb N_F^T+\mathbb N_F\mathbb M_F^T
=
2
\begin{pmatrix}
C_\Theta C_\Theta^T & 0\\
0 & C_{\Pi_\Theta}C_{\Pi_\Theta}^T
\end{pmatrix},
\end{equation}
because the off-diagonal terms cancel while the diagonal ones add. So the naive direct inversion fails the antisymmetry condition already at the unreduced overlap level.
The plus sign in the fermionic exponent, in contrast with the bosonic minus sign, is the standard Grassmann squeezed-state convention: exchanging two creation operators contributes the extra minus sign needed to solve the linear annihilation constraints.
In the present overlap bookkeeping basis, however, the simple direct inversion above should not be overinterpreted as an already-verified finite-$N$ antisymmetric matrix. The local diagnostic \texttt{fermionic\_overlap\_diagnostic.py} shows explicitly on representative joins that the naive inversion fails this antisymmetry test, so below $S^{(F)}$ is used only as formal notation for the overlap solution, not as a separate quantitative input. What the note actually uses later are the exact fermionic overlap constraints themselves together with the surviving zero-mode variable $\Lambda_{\mathrm{lat}}$. A systematic Grassmann-moment extraction, analogous to the bosonic Gaussian-moment Neumann construction, is left for later work. The overall factor ${\cal C}_3^{(F)}$ still depends on the global fermionic coherent-state normalization convention. Here the same finite-$N$ Fock vacuum symbol $|0\rangle$ is used as in the bosonic sector, now understood as annihilated by all oscillators in the chosen physical fermionic basis as well. The note does not fix the normalization convention independently at this stage; it is absorbed later into the overall normalization of the full superstring vertex.
Thus the superstring cubic vertex factorizes into a kinematic overlap state
\begin{equation}
\label{eq:s13-012}
|V_{\mathrm{kin}}\rangle = |V_3^{(B)}\rangle \otimes |V^{(F)}_{\mathrm{kin}}\rangle
\end{equation}
times the local interaction-point prefactor. Here ``kinematic'' again means exact boundary sewing only. The omitted affine fermionic source is not an additional interaction term; it is simply the fermionic analogue of the bosonic inhomogeneous source $J_0(y)$, now determined by the relative average Grassmann mode $\upsilon$. One could keep it explicitly as a linear source vector in the fermionic constraint equations, but for the purposes of the later local prefactor it is cleaner to absorb that information into the surviving zero-mode variable $\Lambda_{\mathrm{lat}}$.

For numerical work one must also fix the Grassmann ordering convention once and for all. A convenient choice is to order variables by leg, then by site, then by SO$(8)$ index:
\begin{equation}
\label{eq:s13-013}
\Theta=
\bigl(
\theta^{(1)}_{0,1},\dots,\theta^{(1)}_{N_1-1,8};
\theta^{(2)}_{0,1},\dots,\theta^{(2)}_{N_2-1,8};
\theta^{(3)}_{0,1},\dots,\theta^{(3)}_{N_3-1,8}
\bigr).
\end{equation}
The Berezin measure is taken in the matching order. Once this convention is fixed, the overall sign of every fermionic determinant/Pfaffian is fixed consistently across all diagrams.

\section{Superstring cubic vertex and GS prefactor}
In the superstring, the full cubic vertex is not an arbitrary polynomial ansatz. One should first construct the kinematic overlap state $|V_{\mathrm{kin}}\rangle$ implementing the exact bosonic and fermionic boundary concatenation, and only then multiply by the local Green--Schwarz prefactor:
\begin{equation}
\label{eq:s14-001}
|V_{\mathrm{GS}}\rangle
=
{\cal P}_{I,\mathrm{loc}}\,|V_{\mathrm{kin}}\rangle,
\qquad
{\cal P}_{I,\mathrm{loc}}\equiv {\cal P}_I\,\widetilde{\cal P}_I.
\end{equation}
Thus the full cubic interaction is conceptually split into two layers:
\begin{itemize}
\item the kinematic overlap state $|V_{\mathrm{kin}}\rangle$, which says how the three string boundaries are exactly sewn together, and
\item the local prefactor ${\cal P}_{I,\mathrm{loc}}$, which carries the genuinely dynamical Green--Schwarz interaction-point information.
\end{itemize}
At finite lattice spacing this separation is slightly subtler than in the continuum Mandelstam-coordinate derivation. The site-by-site overlap itself is exact discrete kinematics: it really does impose the full boundary concatenation with no approximation. What is not exact at finite $a$ is the identification of that discrete join with the continuum branch-point-local overlap, because the square-root interaction-point geometry produces $O(a^{1/2})$ join-local corrections. The working convention in this note is therefore that such branch-point-local lattice artifacts are absorbed into the local prefactor coefficients and possible finite-$a$ counterterms, rather than being treated as modifications of the exact site-space overlap. In this sense the decomposition $|V_{\mathrm{GS}}\rangle={\cal P}_{I,\mathrm{loc}}|V_{\mathrm{kin}}\rangle$ remains valid, but the prefactor coefficients need not equal their continuum values before the continuum limit is taken.
Here ${\cal P}_I$ and $\widetilde{\cal P}_I$ denote the holomorphic and antiholomorphic local interaction-point operators at the vertex labeled by $I$. In the present note only their product ${\cal P}_{I,\mathrm{loc}}$ is used invariantly; later one writes this combined local prefactor as the lattice operator $K_{\mathrm{lat}}^I\,\widetilde K_{\mathrm{lat}}^J\,v^{\mathrm{lat}}_{IJ}$, where the superscripts $I,J$ on $K$ and $v_{IJ}$ are transverse SO$(8)$ vector indices and are unrelated to the vertex label.
The prefactor is fixed, up to overall normalization and possible finite-$a$ counterterms, by the requirement that the dynamical supercharges act correctly on the vertex:
\begin{equation}
\label{eq:s14-002}
\left(\sum_{r=1}^3 Q_r^-\right)|V_{\mathrm{GS}}\rangle=0,
\qquad
\left(\sum_{r=1}^3 \widetilde Q_r^-\right)|V_{\mathrm{GS}}\rangle=0.
\end{equation}
Here $Q_r^-$ and $\widetilde Q_r^-$ mean the restrictions of the continuum dynamical supercharges to the Hilbert spaces of the three legs meeting at the cubic vertex. The note uses these equations as matching conditions for the lattice prefactor; it does not yet write out the complete finite-$N$ component form of those supercharges.
Thus low-point amplitudes are checks of the construction, not the primary definition of the vertex. The first mandatory ones are the bosonic three-tachyon amplitude and the superstring three-graviton amplitude discussed below.

In the unfolded closed-string strip, define the two local representatives
\begin{equation}
\label{eq:s14-003}
X_{I_+}\equiv X_0^{(1)}=X_0^{(3)},
\qquad
X_{I_-}\equiv X_0^{(2)}=X_{N_1}^{(3)},
\end{equation}
and likewise
\begin{equation}
\label{eq:s14-004}
\theta_{I_+}\equiv \theta_0^{(1)}=\theta_0^{(3)},
\qquad
\theta_{I_-}\equiv \theta_0^{(2)}=\theta_{N_1}^{(3)}.
\end{equation}
The raw local lattice data are then the one-sided differences on the two arcs,
\begin{equation}
\label{eq:s14-005}
\nabla_+ X^{(1)}_{I_+} \equiv X^{(1)}_1-X_{I_+},
\qquad
\nabla_+ X^{(3)}_{I_+} \equiv X^{(3)}_1-X_{I_+},
\end{equation}
\begin{equation}
\label{eq:s14-006}
\nabla_- X^{(2)}_{I_-} \equiv X_{I_-}-X^{(2)}_{N_2-1},
\qquad
\nabla_- X^{(3)}_{I_-} \equiv X_{I_-}-X^{(3)}_{N_3-1},
\end{equation}
and similarly
\begin{equation}
\label{eq:s14-007}
\nabla_+ \theta^{(1)}_{I_+} \equiv \theta^{(1)}_1-\theta_{I_+},
\qquad
\nabla_+ \theta^{(3)}_{I_+} \equiv \theta^{(3)}_1-\theta_{I_+},
\end{equation}
\begin{equation}
\label{eq:s14-008}
\nabla_- \theta^{(2)}_{I_-} \equiv \theta_{I_-}-\theta^{(2)}_{N_2-1},
\qquad
\nabla_- \theta^{(3)}_{I_-} \equiv \theta_{I_-}-\theta^{(3)}_{N_3-1}.
\end{equation}
These are \emph{not} yet the continuum interaction-point operators $K^I$ and $\widetilde K^I$; they are only the finite lattice differences from which those singular operators must be reconstructed.

Figure~\ref{fig:interaction-arcs} isolates the local geometry relevant for the interaction-point prefactor. The two operators probe different arcs of the unfolded closed-string join.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=1.0, every node/.style={font=\small}]
\draw[thick] (-4.2,0.4) -- (4.2,0.4);
\fill[red] (-2.2,0.4) circle (1.6pt);
\fill[red] (2.2,0.4) circle (1.6pt);
\node[red!70!black,above] at (-2.2,0.5) {$I_+$};
\node[red!70!black,above] at (2.2,0.5) {$I_-$};

\fill[blue] (-1.2,0.4) circle (1.3pt);
\fill[blue] (-0.2,0.4) circle (1.3pt);
\fill[green!50!black] (1.2,0.4) circle (1.3pt);
\fill[green!50!black] (0.2,0.4) circle (1.3pt);

\draw[thick,dashed,blue] (-2.2,0.95) -- (-0.2,0.95);
\draw[thick,dashed,green!50!black] (2.2,0.95) -- (0.2,0.95);
\node[blue] at (-1.2,1.28) {$K_{\mathrm{lat}}$ arc};
\node[green!50!black] at (1.2,1.28) {$\widetilde K_{\mathrm{lat}}$ arc};

\draw[->,thick,blue] (-2.05,-0.05) -- (-1.25,0.35);
\draw[->,thick,green!50!black] (2.05,-0.05) -- (1.25,0.35);
\node[draw,rounded corners,align=center,text width=2.6cm,inner sep=3pt,blue] at (-1.55,-0.95)
{forward stencil\\ toward string 1};
\node[draw,rounded corners,align=center,text width=2.8cm,inner sep=3pt,green!50!black] at (1.55,-0.95)
{backward stencil\\ toward string 2};

\draw[decorate,decoration={brace,mirror,amplitude=5pt}] (-2.2,-1.75) -- (-0.2,-1.75);
\draw[decorate,decoration={brace,mirror,amplitude=5pt}] (0.2,-1.75) -- (2.2,-1.75);
\node at (-1.2,-2.12) {left arc};
\node at (1.2,-2.12) {right arc};
\end{tikzpicture}
\caption{Local interaction-region geometry in the unfolded closed-string strip. The holomorphic operator $K_{\mathrm{lat}}$ probes the $I_+$ arc by a one-sided stencil toward string 1, while the antiholomorphic operator $\widetilde K_{\mathrm{lat}}$ probes the $I_-$ arc by a one-sided stencil toward string 2. The explicit formulas for these raw lattice differences are given in the displayed equations immediately below. Genuine improved stencils must stay on the same arc and involve additional nearby lattice sites.}
\label{fig:interaction-arcs}
\end{figure}

At an interaction point $z_I$ the Mandelstam map has $\rho'(z_I)=0$, since $z_I$ is a branch point of the worldsheet-to-strip map. Therefore the local expansion starts at quadratic order:
\begin{equation}
\label{eq:s14-009}
\rho(z)=\rho_I+\frac12 \rho''(z_I)(z-z_I)^2+O\!\bigl((z-z_I)^3\bigr).
\end{equation}
\noindent
Choose a local uniformizing coordinate $w$ near the branch point with $w(z_I)=0$ and $w=z-z_I$ to leading order. Then
\begin{equation}
\label{eq:s14-010}
\rho-\rho_I=\frac12 \rho''(z_I)\,w^2+O(w^3),
\qquad
\sqrt{2(\rho-\rho_I)}=\sqrt{\rho''(z_I)}\,w+O(w^2),
\end{equation}
while
\begin{equation}
\label{eq:s14-011}
\frac{\partial}{\partial \rho}
=
\frac{1}{\rho''(z_I)\,w}\frac{\partial}{\partial w}
+O(1).
\end{equation}
Hence the continuum interaction-point operator is
\begin{equation}
\label{eq:s14-012}
K^I
\equiv
\lim_{\rho\to\rho_I}\sqrt{2(\rho-\rho_I)}\,\frac{\partial X^I}{\partial \rho}
=
\frac{1}{\sqrt{\rho''(z_I)}}\,
\frac{\partial X^I}{\partial w}\Big|_{w=0},
\end{equation}
up to the branch/phase convention used to define the square root and the local coordinate. The antiholomorphic operator $\widetilde K^I$ is the analogous square-root coefficient of $\bar\partial X^I$ on the conjugate arc. The point is that $K^I$ and $\widetilde K^I$ are not ordinary strip derivatives: they are the finite coefficients left after multiplying the singular fields by the local square-root factor. On the lattice, one step in the strip direction has $\Delta \rho\sim a$, so the branch-point relation implies $|w|\sim a^{1/2}$ and therefore $\Delta X\sim (\partial_w X)\Delta w=O(a^{1/2})$. This fixes the leading scaling
\begin{equation}
\label{eq:s14-013}
K^I \sim a^{-1/2}\,\Delta X^I,
\qquad
\widetilde K^I \sim a^{-1/2}\,\Delta X^I,
\end{equation}
independently of the detailed stencil choice.
More explicitly, suppose one fixes a local lattice coordinate on the two arcs so that one lattice step corresponds to
\begin{equation}
\label{eq:s14-014}
\Delta w_+ = \lambda_I\,a^{1/2}+O(a),
\qquad
\Delta \bar w_- = \widetilde\lambda_I\,a^{1/2}+O(a),
\end{equation}
with $\lambda_I$ and $\widetilde\lambda_I$ determined by the chosen local-coordinate convention on the holomorphic and antiholomorphic arcs. Then matching the lattice difference $\Delta X^I \sim (\partial_w X^I)\Delta w_+$ to the continuum formula above gives the conditional leading coefficients
\begin{equation}
\label{eq:s14-015}
c_K = \frac{\lambda_I}{\sqrt{\rho''(z_I)}},
\qquad
\widetilde c_K = \frac{\widetilde\lambda_I}{\sqrt{\overline{\rho''(z_I)}}},
\end{equation}
again up to the branch choice for the square root and the phase convention for the local coordinate. So there is an explicit formula once the local-coordinate normalization is specified; what the note still does not do is fix that normalization convention uniquely from the dynamical algebra.

The minimal lattice ansatz is therefore a renormalized one-sided difference on each arc:
\begin{equation}
\label{eq:s14-016}
\begin{aligned}
K^I_{\mathrm{lat}}
&=
a^{-1/2}c_K\,\bigl(\nabla_+ X_{I_+}^{(1)}\bigr)^I
=
a^{-1/2}c_K\,\bigl(\nabla_+ X_{I_+}^{(3)}\bigr)^I,\\
\widetilde K^I_{\mathrm{lat}}
&=
a^{-1/2}\widetilde c_K\,\bigl(\nabla_- X_{I_-}^{(2)}\bigr)^I
=
a^{-1/2}\widetilde c_K\,\bigl(\nabla_- X_{I_-}^{(3)}\bigr)^I.
\end{aligned}
\end{equation}
The equalities between the leg-$1$/leg-$3$ and leg-$2$/leg-$3$ expressions are exact consequences of the position-space overlap itself: $\nabla_+X_{I_+}^{(3)}=\nabla_+X_{I_+}^{(1)}$ because the first site on string $3$ is the first site on string $1$, while $\nabla_-X_{I_-}^{(3)}=\nabla_-X_{I_-}^{(2)}$ because the last site on string $3$ is the last site on string $2$. The approximation enters only in the continuum matching statement
\begin{equation}
\label{eq:s14-017}
K^I_{\mathrm{lat}}=K^I+O(a^{1/2}),
\qquad
\widetilde K^I_{\mathrm{lat}}=\widetilde K^I+O(a^{1/2}),
\end{equation}
after the normalization constants and local coordinate conventions have been fixed. Thus $K$ probes the $I_+$ arc of the join and $\widetilde K$ probes the $I_-$ arc. More general improved lattice definitions are possible,
\begin{equation}
\label{eq:s14-018}
K^I_{\mathrm{lat,imp}}
=
a^{-1/2}c_K^{(2)}\,\bigl(D^{(2)}_{I_+}X^{(1)}\bigr)^I,
\qquad
\widetilde K^I_{\mathrm{lat,imp}}
=
a^{-1/2}\widetilde c_K^{(2)}\,\bigl(\widetilde D^{(2)}_{I_-}X^{(2)}\bigr)^I,
\end{equation}
where a genuine improvement must involve extra sites on the same arc, for example the one-sided second-order stencils
\begin{equation}
\label{eq:s14-019}
D^{(2)}_{I_+}X^{(1)} \equiv \frac{-3X_{I_+}+4X_1^{(1)}-X_2^{(1)}}{2},
\qquad
\widetilde D^{(2)}_{I_-}X^{(2)} \equiv \frac{3X_{I_-}-4X_{N_2-1}^{(2)}+X_{N_2-2}^{(2)}}{2}.
\end{equation}
Because $\nabla_+X_{I_+}^{(1)}=\nabla_+X_{I_+}^{(3)}$ and $\nabla_-X_{I_-}^{(2)}=\nabla_-X_{I_-}^{(3)}$ exactly by overlap, linear combinations of those equal nearest-neighbor differences do not produce any actual improvement. Additional moment conditions on the multi-site stencil may be imposed to cancel the first $O(a^{1/2})$ corrections and improve finite-$a$ convergence.

The branch-point argument above fixes the \emph{scaling} $a^{-1/2}$ but not, by itself, the final constants $c_K$, $\widetilde c_K$, $c_K^{(2)}$, $\widetilde c_K^{(2)}$ or the precise phase conventions. Those quantities are not free fit parameters, but neither are they determined by $\rho''(z_I)$ alone unless one has already fixed the continuum normalization and local-coordinate convention for $K^I$ and $\widetilde K^I$. The missing input is twofold: first, one must specify exactly how the continuum interaction-point operator is normalized in the chosen Mandelstam/lightcone convention; second, one must perform the separate discrete bosonic Lorentz or supercharge-closure computation that matches the lattice local operator to that continuum convention. Until those steps are carried out, it would be misleading to present a universal closed formula for $c_K$ or $\widetilde c_K$. The honest statement is that the present derivation determines the locality structure and the $a^{-1/2}$ scaling, while the final normalization data remain to be fixed by the dynamical algebra.

The continuum lightcone GS vertex is already known. Suppressing only the explicit SO$(8)$ gamma-matrix contractions inside $v_{IJ}(\Lambda)$, one may write the cubic Hamiltonian in the standard compact form
\begin{equation}
\label{eq:s14-020}
|H_3\rangle
=
{\cal C}_3^{(S)}
K^I \widetilde K^J v_{IJ}(\Lambda)
|V_{\mathrm{kin}}\rangle,
\end{equation}
where ${\cal C}_3^{(S)}$ is the overall normalization of the full superstring cubic Hamiltonian, including the conventional coupling normalization and any finite-$a$ renormalization needed so that the lattice cubic vertex matches the continuum super-Poincare algebra.
From this point onward the same letter $a$ appears in two unrelated roles: in factors such as $a^{-1/2}$ it is always the lattice spacing, whereas superscripts such as $\Lambda^a$ and spinor contractions use $a,b,\dot a,\dot b$ as SO$(8)$ spinor indices.
In this formula:
\begin{itemize}
\item $\Lambda^a$, $a=1,\dots,8$, are the eight independent SO$(8)$ fermionic zero-mode combinations surviving the kinematic overlap,
\item $v_{IJ}(\Lambda)$ is the known octic SO$(8)$-covariant polynomial in $\Lambda$,
\item $K^I$ and $\widetilde K^J$ are the bosonic interaction-point operators, i.e. the singular parts of $\partial X^I$ and $\bar\partial X^J$ at the join.
\end{itemize}
In the formulas below, $\Lambda^a$ is taken to transform as a chiral SO$(8)$ spinor, say $\mathbf{8}_s$. For type IIA/IIB the usual relative chirality assignments between left and right sectors must be restored, but that distinction is not needed for the lattice kinematics being developed here. The compact continuum formula above is therefore not yet a fully convention-fixed component expression: to write it out completely one would also have to choose a definite SO$(8)$ gamma-matrix basis, chirality conventions, and normalization/phasing conventions for the continuum supercharges.
The polynomial decomposes into even Grassmann degree as
\begin{equation}
\label{eq:s14-021}
v_{IJ}(\Lambda)
=
A^{(0)}_{IJ}
+A^{(2)}_{IJ,ab}\Lambda^a\Lambda^b
+A^{(4)}_{IJ,abcd}\Lambda^a\Lambda^b\Lambda^c\Lambda^d
+A^{(6)}_{IJ,a_1\cdots a_6}\Lambda^{a_1}\cdots\Lambda^{a_6}
+A^{(8)}_{IJ}\epsilon_{a_1\cdots a_8}\Lambda^{a_1}\cdots\Lambda^{a_8},
\end{equation}
with the coefficients built from SO$(8)$ gamma matrices and the Levi-Civita tensor. This note does not reproduce the full component formulas for those coefficients because they are lengthy and convention-dependent; the precise expressions depend on the chosen SO$(8)$ gamma-matrix basis and the left/right chirality conventions of the flat-space GS formalism. Explicit formulas are available in the continuum lightcone literature \cite{SpradlinVolovich2002,PankiewiczStefanski2002}; for implementation one should import those tensors from a single fixed convention rather than mixing formulas across sources. The matrix-string interpretation of the same structure is discussed in \cite{DijkgraafMotl2003,Kishimoto2006}.
That matrix-string interpretation is more explicit than a bare citation. In Section~2 of \cite{DijkgraafMotl2003}, the local interaction is written as $(\tau^i\Sigma^i)(\bar\tau^j\bar\Sigma^j)$ with $\tau^i\Sigma^i=G_{-1/2}^{\dot a}(\sigma\Sigma^{\dot a})$ on the left-moving side. The regularized singular bosonic operators $p^i_{\mathrm{reg}}$, $\tilde p^j_{\mathrm{reg}}$ convert the bare twist fields $\sigma$, $\tilde\sigma$ into the excited twists $\tau^i$, $\tilde\tau^j$. On the fermionic side, Dijkgraaf--Motl identify the Grassmann-module unit function with $\Sigma^i\tilde\Sigma^i-\ii\Sigma^{\dot a}\tilde\Sigma^{\dot a}$, show that repeated multiplication by $\Lambda^a$ generates the full spin-field basis, and derive the final continuum identity $v^{ij}(\Lambda)\leftrightarrow 16\,\Sigma^j\tilde\Sigma^i$. The numerical factor $16$ here is the Dijkgraaf--Motl normalization convention; when comparing with other continuum sources one should allow for the corresponding overall conversion factor before matching component formulas. So the continuum GS prefactor $p^i_{\mathrm{reg}}\tilde p^j_{\mathrm{reg}}v_{ij}(\Lambda)$ is precisely the lightcone Green--Schwarz representative of the same local supercurrent insertion at the join. This is the conceptual bridge from the NSR/matrix-string $G^\perp\widetilde G^\perp$ language to the compact GS formula $K^I\widetilde K^Jv_{IJ}(\Lambda)$ used in this note. What it does \emph{not} yet determine is the preferred finite-$a$ lattice quantization of the corresponding local operator.
There is also a concrete continuum convention bridge that is worth making explicit. Dijkgraaf--Motl define the local interaction-point fermion by the regulated branch-point field
\[
\Lambda^a_{\mathrm{DM}}
=
\sqrt{\frac z2}\,\theta^a(z)
\ii\sqrt{\frac{\bar z}2}\,\tilde\theta^a(\bar z),
\]
and state that it is related to the Brink--Green--Schwarz variable used in the older lightcone prefactor formulas by
\begin{equation}
\label{eq:s14-021a}
\Lambda^a_{\mathrm{DM}}
=
\sqrt{\frac{2}{\alpha}}\,
\Lambda^a_{\mathrm{GSB}}.
\end{equation}
Therefore a degree-$d$ monomial in the Pankiewicz--Stefanski / Brink--Green--Schwarz convention differs from the Dijkgraaf--Motl convention by the universal rescaling factor $(\alpha/2)^{d/2}$. The new helper \texttt{lambda\_convention\_bridge.py} verifies this directly on the imported coefficient tensors: after multiplying the degree-$2,4,6,8$ coefficient blocks by $(\alpha/2)^{1,2,3,4}$ respectively, the explicit continuum tensor set becomes $\alpha$-independent to machine precision and reproduces the Dijkgraaf--Motl normalized coefficients. So the present continuum implementation no longer has an unresolved Dijkgraaf--Motl versus Pankiewicz--Stefanski normalization ambiguity. The still-open issue is instead the genuinely local \emph{lattice} branch-point normalization.
For an actual implementation these coefficients must therefore be imported from a fixed continuum convention; the present note identifies the required tensor structures but does not itself rederive them from first principles. In the local diagnostics accompanying this note, the files \texttt{so8\_gamma.py} and \texttt{gs\_zero\_mode\_prefactor.py} now fix one concrete SO$(8)$ convention and assemble the imported continuum coefficients $v_{IJ}(\Lambda)$ explicitly in that basis, while \texttt{gs\_zero\_mode\_module.py} makes the corresponding $8_v\oplus 8_c$ ground-state Clifford module explicit. What is still not supplied by those helpers is the separate dictionary between the resulting Grassmann-polynomial basis and the external lightcone graviton states.
Throughout this discussion $\gamma^I_{a\dot a}$ denotes an SO$(8)$ Clebsch--Gordan matrix coupling $\mathbf 8_s\otimes \mathbf 8_c\to \mathbf 8_v$, and $\gamma^{IJ}_{ab}$ denotes the induced antisymmetrized two-index matrix acting on the chosen chiral spinor representation. The note itself still keeps these symbols abstract, but whenever a concrete component calculation is needed one must choose one fixed convention and stick to it throughout.

After imposing the kinematic overlap, the local fermionic data in the unfolded strip consist of the pair of strip representatives $\theta_{I_+}^a$, $\theta_{I_-}^a$ together with the surviving independent Grassmann zero-mode combination $\Lambda_{\mathrm{lat}}^a$ (or the canonically equivalent conjugate variable, depending on conventions). The lattice prefactor is therefore local to the interaction region, but not a polynomial in three independent endpoint spinors:
\begin{equation}
\label{eq:s14-022}
\begin{aligned}
v_{IJ}^{\mathrm{lat}}(\Lambda_{\mathrm{join}})
&= 
A^{(0)}_{IJ}
+A^{(2)}_{IJ,ab}\Lambda_{\mathrm{join}}^a\Lambda_{\mathrm{join}}^b\\
&\quad
+A^{(4)}_{IJ,abcd}\Lambda_{\mathrm{join}}^a\Lambda_{\mathrm{join}}^b
                        \Lambda_{\mathrm{join}}^c\Lambda_{\mathrm{join}}^d\\
&\quad
+A^{(6)}_{IJ,a_1\cdots a_6}\Lambda_{\mathrm{join}}^{a_1}\cdots\Lambda_{\mathrm{join}}^{a_6}\\
&\quad
+A^{(8)}_{IJ}\epsilon_{a_1\cdots a_8}\Lambda_{\mathrm{join}}^{a_1}\cdots\Lambda_{\mathrm{join}}^{a_8}.
\end{aligned}
\end{equation}
Equation~\eqref{eq:s14-022} is the local definition. The reduced coordinate $\Lambda_{\mathrm{lat}}$ introduced next is not a replacement definition of the vertex; it is only the overlap-constrained zero-mode variable that appears after setting aside the explicit local correction $\Xi_{\mathrm{loc}}$ in the present three-point ansatz.
Equivalently, $(\theta_{I_+},\theta_{I_-})$ are the local strip data at the join, while the averaged leg modes obey weighted overlap relations exactly as in the bosonic sector. A convenient explicit finite-$N$ coordinate on the surviving overlap-constrained fermionic zero-mode sector is
\begin{equation}
\label{eq:s14-023}
\Theta_{\mathrm{cm}}^a\equiv \theta_{\mathrm{av}}^{(3)a}
=
\frac{N_1\theta_{\mathrm{av}}^{(1)a}+N_2\theta_{\mathrm{av}}^{(2)a}}{N_3},
\qquad
\Lambda_{\mathrm{lat}}^a
\equiv
\sqrt{\frac{N_1N_2}{N_3}}\,
\bigl(\theta_{\mathrm{av}}^{(1)a}-\theta_{\mathrm{av}}^{(2)a}\bigr)
=
\sqrt{\frac{N_1N_2}{N_3}}\,\upsilon^a.
\end{equation}
However, the local endpoint fermions are \emph{not} equal to those averages. In the same real zero-sum basis $S_r$ used for the bosonic nonzero modes, one has the exact finite-$N$ decomposition
\begin{equation}
\label{eq:s14-023a}
\theta_n^{(r)a}
\;=\;
\theta_{\mathrm{av}}^{(r)a}
\;+\;
\sum_{m=1}^{N_r-1}(S_r)_{nm}\,\vartheta_m^{(r)a},
\end{equation}
so in particular
\begin{equation}
\label{eq:s14-023b}
\theta_{I_+}^a
=
\theta_{\mathrm{av}}^{(1)a}
\;+\;
\sum_{m=1}^{N_1-1}(S_1)_{0m}\,\vartheta_m^{(1)a},
\qquad
\theta_{I_-}^a
=
\theta_{\mathrm{av}}^{(2)a}
\;+\;
\sum_{m=1}^{N_2-1}(S_2)_{0m}\,\vartheta_m^{(2)a}.
\end{equation}
The accompanying helper \texttt{local\_interaction\_point\_fermion.py} records these exact site-level decompositions and the corresponding one-sided local arc differences explicitly.
It is also useful to rewrite the leg averages in the mixed zero-mode basis $(\Theta_{\mathrm{cm}},\Lambda_{\mathrm{lat}})$. Solving \eqref{eq:s14-023} gives
\begin{equation}
\label{eq:s14-023c}
\theta_{\mathrm{av}}^{(1)a}
=
\Theta_{\mathrm{cm}}^a
\;+\;
\sqrt{\frac{N_2}{N_1N_3}}\,\Lambda_{\mathrm{lat}}^a,
\qquad
\theta_{\mathrm{av}}^{(2)a}
=
\Theta_{\mathrm{cm}}^a
\;-\;
\sqrt{\frac{N_1}{N_2N_3}}\,\Lambda_{\mathrm{lat}}^a.
\end{equation}
It is then straightforward to characterize the most general endpoint-linear local
candidate. For
\begin{equation}
\label{eq:s14-023c1}
\Lambda_{\mathrm{trial}}^a
\equiv
c_+\,\theta_{I_+}^a+c_-\,\theta_{I_-}^a,
\end{equation}
the exact mixed zero-mode part is
\begin{equation}
\label{eq:s14-023c2}
\Lambda_{\mathrm{trial}}^a
=
(c_+ + c_-)\,\Theta_{\mathrm{cm}}^a
\;+\;
\left(
c_+\sqrt{\frac{N_2}{N_1N_3}}
-c_-\sqrt{\frac{N_1}{N_2N_3}}
\right)\Lambda_{\mathrm{lat}}^a
\;+\;(\text{nonzero modes}).
\end{equation}
Demanding zero center-of-mass contamination and unit reduced coefficient gives
\begin{equation}
\label{eq:s14-023c3}
c_+ + c_- = 0,
\qquad
c_+\sqrt{\frac{N_2}{N_1N_3}}
-c_-\sqrt{\frac{N_1}{N_2N_3}}
=1,
\end{equation}
whose unique solution is
\begin{equation}
\label{eq:s14-023c4}
c_+=\sqrt{\frac{N_1N_2}{N_3}},
\qquad
c_-=-\sqrt{\frac{N_1N_2}{N_3}}.
\end{equation}
So among linear combinations of the two endpoint site fermions, the scaled
local difference is the unique endpoint-linear choice with no
$\Theta_{\mathrm{cm}}$ contamination and unit $\Lambda_{\mathrm{lat}}$
coefficient. The helper \texttt{local\_interaction\_point\_fermion.py} now
exposes this inversion explicitly and verifies the closed-form coefficients at
finite~$N$.
One can sharpen this endpoint-linear statement by scanning the equal-magnitude
phase family
\begin{equation}
\label{eq:s14-023c5}
\widehat\Lambda_{\mathrm{phase}}^a(\phi)
\equiv
\mathcal{N}(\phi)\,
\bigl(\theta_{I_+}^a+e^{\ii\phi}\theta_{I_-}^a\bigr),
\qquad
\text{with $\mathcal{N}(\phi)$ chosen so that the $\Lambda_{\mathrm{lat}}$
coefficient is $1$.}
\end{equation}
The new helper \texttt{local\_endpoint\_phase\_scan.py} shows that, within this
equal-magnitude endpoint family, the canonical anti-phase point
$\phi=\pi$ is not only the unique CM-free choice but also the one that
minimizes the nonzero-mode two-point scalar after unit-$\Lambda_{\mathrm{lat}}$
normalization. On the sample point $(N_1,N_2)=(128,192)$ one finds
\begin{equation}
\label{eq:s14-023c6}
\bigl|\Theta_{\mathrm{cm}}\bigr|_{\phi=\pi}=0,
\qquad
\bigl|\Theta_{\mathrm{cm}}\bigr|_{\phi=\pm \pi/2}\approx 1.72\times 10^1,
\qquad
C_\Xi(\phi=\pi)\approx 7.63\times 10^1,
\qquad
C_\Xi(\phi=\pm\pi/2)\approx 1.47\times 10^2.
\end{equation}
So a literal finite-$N$ endpoint sum with relative phase $\pm\ii$ is not just
a harmless rephasing of the canonical difference. It carries large
center-of-mass contamination and a substantially larger local nonzero-mode
weight, so using it as the lattice interaction-point fermion would require an
additional local completion beyond the bare endpoint-linear ansatz.
Substituting this into \eqref{eq:s14-023b} yields one exact finite-$N$ local-to-reduced bridge:
\begin{equation}
\label{eq:s14-023d}
\sqrt{\frac{N_1N_2}{N_3}}\,
\bigl(\theta_{I_+}^a-\theta_{I_-}^a\bigr)
=
\Lambda_{\mathrm{lat}}^a
\;+\;
\sqrt{\frac{N_1N_2}{N_3}}
\left[
\sum_{m=1}^{N_1-1}(S_1)_{0m}\,\vartheta_m^{(1)a}
\;-\;
\sum_{m=1}^{N_2-1}(S_2)_{0m}\,\vartheta_m^{(2)a}
\right].
\end{equation}
So the scaled local endpoint difference is the reduced zero-mode coordinate plus an explicit nonzero-mode correction, and it has \emph{no} center-of-mass contamination. Writing
\begin{equation}
\label{eq:s14-023e}
\Xi_{\mathrm{loc}}^a
\equiv
\sqrt{\frac{N_1N_2}{N_3}}
\left[
\sum_{m=1}^{N_1-1}(S_1)_{0m}\,\vartheta_m^{(1)a}
\;-\;
\sum_{m=1}^{N_2-1}(S_2)_{0m}\,\vartheta_m^{(2)a}
\right],
\qquad
\Lambda_{\mathrm{join}}^a
\equiv
\sqrt{\frac{N_1N_2}{N_3}}\,
\bigl(\theta_{I_+}^a-\theta_{I_-}^a\bigr),
\end{equation}
one has the exact mixed decomposition
\begin{equation}
\label{eq:s14-023f}
\Lambda_{\mathrm{join}}^a
=
\Lambda_{\mathrm{lat}}^a+\Xi_{\mathrm{loc}}^a.
\end{equation}
Therefore the genuinely local prefactor symbol is
\begin{equation}
\label{eq:s14-023g}
v_{IJ}\!\bigl(\Lambda_{\mathrm{join}}\bigr)
=
\sum_{p=0}^{8}
\frac{1}{p!}\,
\Xi_{\mathrm{loc}}^{a_1}\cdots\Xi_{\mathrm{loc}}^{a_p}\,
\partial_{a_1}\cdots\partial_{a_p}\,
v_{IJ}\!\bigl(\Lambda_{\mathrm{lat}}\bigr),
\end{equation}
with all Grassmann derivatives acting on the continuum SO$(8)$ polynomial. The new helper \texttt{local\_prefactor\_expansion.py} verifies this mixed-variable decomposition exactly in sparse polynomial form: the $\Xi_{\mathrm{loc}}$-degree-$0$ component reproduces the current reduced ansatz, while the higher $\Xi_{\mathrm{loc}}$ sectors are nonzero and therefore carry genuine local information that still has to be integrated out.
One can already push this one step further before performing any fermionic nonzero-mode average. Define the \emph{local channel polynomial} by integrating over the reduced zero modes $\lambda_1,\lambda_2$ exactly, while keeping $\Xi_{\mathrm{loc}}$ symbolic. The new helper \texttt{local\_channel\_response.py} performs this exact Berezin reduction. For the trace-dropped $q_{\mathrm{rel}}^Iq_{\mathrm{rel}}^J$ benchmark graviton channels, the resulting local polynomials collapse on the sampled ratio grid $\lambda=\frac14,\frac25,\frac12$ to pure $\Xi_{\mathrm{loc}}$-degree-$0$ constants:
\begin{equation}
\label{eq:s14-023h}
\mathcal{R}^{(23,23,\parallel)}_{qq,\mathrm{loc}}(\Xi_{\mathrm{loc}};\lambda)
=
\mathcal{R}^{(23,23,\parallel)}_{qq}(\lambda),
\qquad
\mathcal{R}^{(23,24,\parallel)}_{qq,\mathrm{loc}}(\Xi_{\mathrm{loc}};\lambda)
=
\mathcal{R}^{(23,24,\parallel)}_{qq}(\lambda),
\qquad
\mathcal{R}^{(\parallel,23,23)}_{qq,\mathrm{loc}}(\Xi_{\mathrm{loc}};\lambda)
=
\mathcal{R}^{(\parallel,23,23)}_{qq}(\lambda),
\end{equation}
with no residual $\Xi_{\mathrm{loc}}$ dependence at all. By contrast, the benchmark dilaton response has no reduced piece but does carry a purely quartic local correction sector,
\begin{equation}
\label{eq:s14-023i}
\mathcal{R}^{(23,23,\mathrm{dil})}_{qq,\mathrm{loc}}(\Xi_{\mathrm{loc}};\lambda)
\in \bigwedge\nolimits^4\!\mathrm{Span}\{\Xi_{\mathrm{loc}}^a\},
\qquad
\bigl[\mathcal{R}^{(23,23,\mathrm{dil})}_{qq,\mathrm{loc}}(\Xi_{\mathrm{loc}};\lambda)\bigr]_{\Xi_{\mathrm{loc}}^0}=0,
\end{equation}
and the corresponding trace-dropped $\delta^{IJ}$ benchmark channel vanishes identically on the same sampled grid. So, for this specific canonical endpoint-difference local candidate, the benchmark graviton $qq$ channels already reduce exactly to the old reduced ansatz before any further nonzero-mode averaging, whereas the genuinely local correction sectors first appear in channels that are absent in the reduced benchmark. The new helper \texttt{local\_channel\_catalog.py} extends this from those benchmark channels to the full $5^3$ polarization catalog built from the small basis $\{\epsilon_\parallel,\epsilon_{23},\epsilon_{24},\epsilon_{\mathrm{dil}},B_{23}\}$. On the same sampled ratio grid and in the trace-dropped $qq$ response, the 125 channels split into only five exact classes: 47 vanish identically, 37 are purely quadratic in $\Xi_{\mathrm{loc}}$, 16 are pure reduced degree-$0$ responses, 16 are purely quartic in $\Xi_{\mathrm{loc}}$, and 9 contain both the reduced and quartic pieces. For the trace-dropped $\delta^{IJ}$ response, all 125 sampled channels vanish identically. So the local rebuild is now more organized than before: the benchmark graviton collapse is part of a small exact finite-$N$ classification rather than an isolated special case.
For the same canonical endpoint-difference candidate one can now also perform the first explicit \emph{nonzero-mode vacuum reduction}. Let $r_1$ and $r_2$ denote the real mode-space rows appearing in the exact decomposition of $\Xi_{\mathrm{loc}}$ on legs~1 and~2. In the product external oscillator vacuum, the nonzero-mode part is spinor-diagonal:
\begin{equation}
\label{eq:s14-023j}
\bigl\langle \Xi_{\mathrm{loc}}^a \Xi_{\mathrm{loc}}^b \bigr\rangle_{\mathrm{vac}}
=
C_\Xi(N_1,N_2)\,\delta^{ab},
\qquad
C_\Xi(N_1,N_2)
=
\frac12\!\left(\|r_1\|^2+\|r_2\|^2\right)
=
\frac{2N_1N_2-N_1-N_2}{2N_3}.
\end{equation}
Because every nonzero $\Xi_{\mathrm{loc}}$ monomial in the exact local channel polynomials carries distinct SO$(8)$ spinor labels, all positive-degree $\Xi_{\mathrm{loc}}$ sectors vanish under this contraction. The new helper \texttt{local\_vacuum\_reduction.py} therefore collapses the sampled trace-dropped local catalog to
\begin{equation}
\label{eq:s14-023k}
\#\bigl(\text{vanishing}\bigr)=100,
\qquad
\#\bigl(\text{reduced only}\bigr)=25,
\qquad
\mathcal{R}^{(23,23,\mathrm{dil})}_{qq,\mathrm{loc,vac}}(\lambda)=0
\end{equation}
on the sampled ratio grid. So, for the present canonical local candidate and for three-point vacuum external states, the explicit nonzero-mode reduction produces no correction beyond the $\Xi_{\mathrm{loc}}$-degree-$0$ reduced ansatz.
One can then assemble the actual trace-dropped benchmark amplitudes from these vacuum-contracted local responses and the bosonic coefficients $(A_\delta,B_{qq})$. The new helper \texttt{local\_superstring\_tree\_benchmark.py} carries out this end-to-end local construction and compares it both to the reduced assembly and to the known benchmark closed forms. For the present canonical endpoint-difference candidate one finds
\begin{equation}
\label{eq:s14-023l}
\max_{\mathrm{bench}}
\bigl|
\mathcal{A}^{\mathrm{loc,vac}}_F-\mathcal{A}^{\mathrm{red}}_F
\bigr|
 = 0,
\qquad
\max_{\mathrm{bench}}
\bigl|
\mathcal{A}^{\mathrm{loc,vac}}_F-\mathcal{A}^{\mathrm{bench}}_{\mathrm{GS}}
\bigr|
 < 10^{-14},
\end{equation}
where the scan runs over the sampled family set
$1{:}3,1{:}2,3{:}5,2{:}3,1{:}1$ with scales
$N_1=aL$, $N_2=bL$, $L=16,32,64,128$. So the current three-point local candidate now reproduces the same benchmark graviton, dilaton, and antisymmetric-channel answers as the reduced calculation, but by an explicit local-vacuum reduction rather than by direct insertion of the reduced ansatz.
The new helper \texttt{local\_arc\_candidate\_scan.py} sharpens what this does
and does not fix. If one extends the canonical endpoint difference by the simple
one-sided local arc family
\begin{equation}
\label{eq:s14-023m}
\Lambda_{\mathrm{trial}}^a
=
\Lambda_{\mathrm{join}}^a
+c_{\nabla,+}\,\nabla_+\theta^a
+c_{\nabla,-}\,\nabla_-\theta^a,
\end{equation}
then the mixed zero-mode coefficients remain unchanged because the one-sided arc
differences are pure nonzero-mode data. On the sampled candidate set
\[
(c_{\nabla,+},c_{\nabla,-})
\in
\left\{
(0,0),\left(\frac12,0\right),\left(0,\frac12\right),
\left(\frac12,-\frac12\right),\left(\frac12,\frac12\right),(1,-1)
\right\},
\]
the same three-point vacuum benchmark remains completely unchanged:
\begin{equation}
\label{eq:s14-023n}
\max_{\mathrm{arc},\,\mathrm{bench}}
\bigl|
\mathcal{A}^{\mathrm{trial,vac}}_F-\mathcal{A}^{\mathrm{red}}_F
\bigr|
=0,
\qquad
\max_{\mathrm{arc},\,\mathrm{bench}}
\bigl|
\mathcal{A}^{\mathrm{trial,vac}}_F-\mathcal{A}^{\mathrm{bench}}_{\mathrm{GS}}
\bigr|
<10^{-14}.
\end{equation}
So the present three-point vacuum benchmark fixes the endpoint-linear part of
the local candidate but does \emph{not} yet fix these simple pure-local arc
admixtures. The remaining ambiguity is therefore more specific than before:
it lives in the genuinely local nonzero-mode completion, not in the reduced
zero-mode coordinate itself.
One can sharpen this statement by returning to the full sampled
vacuum-contracted local catalog rather than only the benchmark channels. The
new helper \texttt{local\_arc\_catalog\_scan.py} evaluates the trace-dropped
vacuum-reduced catalog for the same arc family and finds no change at all on
the sampled grid $\lambda=\frac14,\frac25,\frac12$:
\begin{equation}
\label{eq:s14-023o}
\max_{\mathrm{arc},\,\mathrm{catalog}}
\bigl|
\mathcal{R}^{\mathrm{trial,vac}}_{\mathrm{loc}}
\;-\;
\mathcal{R}^{\mathrm{red}}_{\mathrm{loc}}
\bigr|
=0,
\qquad
\#_{qq}^{\mathrm{trial,vac}}
=
100\ \text{vanishing}
\;+\;
25\ \text{reduced only},
\qquad
\#_{\delta}^{\mathrm{trial,vac}}
=
125\ \text{vanishing}.
\end{equation}
So for three-point vacuum external states the present local rebuild is even
more rigid than the benchmark equations alone suggest: the entire sampled
vacuum-contracted catalog is blind to these simple arc admixtures. The
remaining structural uncertainty is therefore pushed one level deeper, to the
true branch-point normalization and to more general local completions involving
data beyond this simple endpoint-plus-one-sided-arc family.
This is the precise finite-$N$ statement that the later local rebuild should start from.
Because $v_{IJ}(\Lambda)$ is an octic Grassmann polynomial, this kind of conclusion cannot be obtained merely by observing that the nonzero-mode one-point functions vanish. One must integrate out the fermionic nonzero modes against the relevant three-point vacuum state. For the present endpoint-difference candidate and vacuum external states that reduction is now explicit and kills the positive-degree sectors, but a more general Grassmann-moment extraction is still needed once one changes the local candidate, inserts excited states, or sews multiple vertices.
This is the canonically normalized relative averaged zero-mode coordinate that survives the kinematic overlap. It should not be identified, without further derivation, with the genuinely local interaction-point fermion that appears in the continuum GS prefactor. The local strip data $(\theta_{I_+},\theta_{I_-})$ enter the prefactor through the short-distance completion of the interaction-point operator and through possible finite-$a$ counterterms, but at present the note does not derive the exact finite-$N$ local fermionic insertion from those data. What it does have is the reduced overlap variable $\Lambda_{\mathrm{lat}}$, which is later used as an explicit benchmark ansatz for the fermionic zero-mode sector. For the closed string there is, of course, an analogous right-moving relative averaged coordinate $\widetilde\Lambda_{\mathrm{lat}}^{\dot a}$ built from the tilded worldsheet fermions. In the standard lightcone GS convention used here, the continuum polynomial $v_{IJ}$ is written only in terms of the chiral variable $\Lambda^a$. The antichiral zero modes enter through the right-moving dynamical supercharge sector, through the tilded external-state Clifford module, and ultimately through the right-moving part of the three-string matrix element, rather than as separate arguments of $v_{IJ}$ itself. Accordingly, one may therefore regard
\begin{equation}
\label{eq:s14-024}
\Lambda_{\mathrm{lat}}^a = \sqrt{\frac{N_1N_2}{N_3}}\,\upsilon^a
+\,
O(a^{1/2})
\quad
\text{with optional local completion by }
(\theta_{I_+},\theta_{I_-},\pi_{\theta,I_+},\pi_{\theta,I_-}),
\end{equation}
where $\pi_{\theta,I_\pm}$ denotes the local site-space Grassmann momentum canonically conjugate to $\theta_{I_\pm}$, if one chooses to keep those endpoint canonical variables explicitly in a first-order lattice formalism. The note does not otherwise construct those endpoint momenta in detail, so at present this is only a description of the possible local data entering a finite-$a$ completion, not a completed formula. No unique explicit finite-$a$ completion is chosen here. Different local completions differ by terms that are irrelevant in the continuum limit, and a preferred lattice definition emerges only after one imposes an additional renormalization condition, for example matching the discrete dynamical supercharge algebra. Thus $\Lambda_{\mathrm{lat}}$ should be read only as a reduced coordinate on the overlap-constrained fermionic zero-mode sector. Whenever the later numerics use $v_{IJ}(\Lambda_{\mathrm{lat}})$ directly, they are using a reduced $\Lambda$ ansatz motivated by the continuum local operator, not a derivation of that local operator itself. The prefactor is therefore a local polynomial of total degree $0,2,4,6,8$ at the join:
\begin{equation}
\label{eq:s14-025}
v_{IJ}^{\mathrm{lat}} = v_{IJ}^{\mathrm{lat}}(\Lambda_{\mathrm{lat}};\theta_{I_+},\theta_{I_-},\pi_{\theta,I_+},\pi_{\theta,I_-}).
\end{equation}
The first few SO$(8)$ tensor structures may be represented as
\begin{equation}
\label{eq:s14-026}
A^{(0)}_{IJ}\sim \delta_{IJ},
\qquad
A^{(2)}_{IJ,ab}\sim (\gamma^{IJ})_{ab},
\qquad
A^{(4)}_{IJ,abcd}\sim (\gamma^{IK})_{[ab}(\gamma^{JK})_{cd]},
\end{equation}
while the top component is proportional to $\delta_{IJ}\epsilon_{a_1\cdots a_8}$. So the full discrete interaction-point operator is
\begin{equation}
\label{eq:s14-027}
{\cal P}_{I,\mathrm{lat}}
=
K^I_{\mathrm{lat}}\,\widetilde K^J_{\mathrm{lat}}\,
v_{IJ}^{\mathrm{lat}}(\Lambda_{\mathrm{lat}};\theta_{I_+},\theta_{I_-},\pi_{\theta,I_+},\pi_{\theta,I_-}),
\end{equation}
where the subscript on ${\cal P}_{I,\mathrm{lat}}$ labels the cubic vertex, while the superscripts on $K^I_{\mathrm{lat}}$, $\widetilde K^J_{\mathrm{lat}}$, and $v^{\mathrm{lat}}_{IJ}$ are transverse SO$(8)$ vector indices.
Thus ${\cal P}_{I,\mathrm{lat}}$ is a local bosonic derivative factor multiplied by an explicitly finite polynomial in the interaction-point fermions.

The lattice problem is therefore not to guess a random fermionic polynomial, but to discretize the known continuum building blocks. After the fermionic overlap is imposed, the interaction-point data are the pair $(\theta_{I_+},\theta_{I_-})$ together with the independent conjugate Grassmann zero-mode combination $\Lambda_{\mathrm{lat}}$. One must combine these with lattice approximations to the interaction-point derivatives,
\begin{equation}
\label{eq:s14-028}
\begin{aligned}
K^I_{\mathrm{lat}}
&=
a^{-1/2}c_K\,\bigl(\nabla_+ X_{I_+}^{(1)}\bigr)^I
=
a^{-1/2}c_K\,\bigl(\nabla_+ X_{I_+}^{(3)}\bigr)^I,\\
\widetilde K^I_{\mathrm{lat}}
&=
a^{-1/2}\widetilde c_K\,\bigl(\nabla_- X_{I_-}^{(2)}\bigr)^I
=
a^{-1/2}\widetilde c_K\,\bigl(\nabla_- X_{I_-}^{(3)}\bigr)^I,\\
\Lambda_{\mathrm{lat}}^a
&=
\sqrt{\frac{N_1N_2}{N_3}}\,\upsilon^a + O(a^{1/2}).
\end{aligned}
\end{equation}
with the understanding that one may replace this by an improved linear combination of legs without changing the continuum limit. The coefficients entering $K^I_{\mathrm{lat}}$ and $\widetilde K^I_{\mathrm{lat}}$ are fixed by the local Mandelstam geometry and the requirement that
\begin{equation}
\label{eq:s14-029}
K^I_{\mathrm{lat}}\to K^I,
\qquad
\widetilde K^I_{\mathrm{lat}}\to \widetilde K^I,
\qquad
\Lambda^a_{\mathrm{lat}}\to \Lambda^a
\end{equation}
in the continuum limit. Again, this identifies the matching conditions but does not yet solve them: the present note gives the finite-$N$ structures to be matched, not the final closed-form values of the matching coefficients.
The factored lattice ansatz used below,
\(
Q^-_{3,\mathrm{lat}}\sim K_{\mathrm{lat}}\,s_{\mathrm{lat}}|V_{\mathrm{kin}}\rangle
\)
and
\(
H_{3,\mathrm{lat}}\sim K_{\mathrm{lat}}\widetilde K_{\mathrm{lat}}\,v_{\mathrm{lat}}|V_{\mathrm{kin}}\rangle,
\)
should therefore be read as continuum-motivated rather than as a lattice theorem. At finite $a$ there could in principle be additional join-local operators with the same SO$(8)$ quantum numbers and the same leading scaling, for example alternative bosonic stencils or extra endpoint-fermion structures. The working hypothesis is that, after using locality and the exact overlap constraints, such effects can be absorbed into an enlarged local coefficient set inside $K_{\mathrm{lat}},\widetilde K_{\mathrm{lat}},s_{\mathrm{lat}},\widetilde s_{\mathrm{lat}},v_{\mathrm{lat}}$. The closure equations are then the real test of sufficiency: if the projected system is inconsistent, the ansatz was too small; if it is underdetermined, additional physical input or a larger local basis is required; and if it is solvable with smooth large-$N$ behavior, that solution selects the correct finite-$a$ completion. Correspondingly, the coefficients $c_K,\widetilde c_K,b_1,b_3,\dots,a_0,a_2,\dots$ should be expected to have finite-$N$ dependence before approaching their continuum limits.

\section{Superstring Lorentz and SUSY check}
For the superstring, the cleanest cubic-order check is through the dynamical supercharges,
\begin{equation}
\label{eq:s15-001}
Q^- = Q^-_2 + g Q^-_3 + O(g^2),
\qquad
\widetilde Q^- = \widetilde Q^-_2 + g \widetilde Q^-_3 + O(g^2),
\end{equation}
and the Hamiltonian
\begin{equation}
\label{eq:s15-002}
H = H_2 + g H_3 + O(g^2).
\end{equation}
Here $Q^-_2$, $\widetilde Q^-_2$, and $H_2$ are the free lightcone generators, while $Q^-_3$, $\widetilde Q^-_3$, and $H_3$ are their cubic interaction corrections. This section is a continuum target check: the generators are the standard lightcone GS ones whose lattice counterparts must approach the same algebra in the continuum limit.
At order $g$, the superalgebra requires
\begin{equation}
\label{eq:s15-003}
\{Q^-_{2\dot a},Q^-_{3\dot b}\}
+\{Q^-_{3\dot a},Q^-_{2\dot b}\}
=
2\delta_{\dot a\dot b} H_3,
\end{equation}
Here the subscripts $2$ and $3$ denote the free and cubic pieces of the dynamical supercharge, and $\dot a,\dot b=1,\dots,8$ are SO$(8)$ conjugate-spinor ($\mathbf{8}_c$) indices. The same statement holds in the right-moving sector. These equations uniquely determine the cubic prefactor $K^I \widetilde K^J v_{IJ}(\Lambda)$ up to overall normalization. Once the dynamical supercharges close, the cubic Lorentz generators follow from the super-Poincare algebra, so the order-$g$ Lorentz check is inherited from SUSY closure.

In the discrete formulation, the test should therefore be organized in the same order:
\begin{enumerate}
\item impose the exact $\sigma$-space kinematic overlap for both bosons and fermions,
\item construct the lattice analogues $K^I_{\mathrm{lat}}$, $\widetilde K^I_{\mathrm{lat}}$, and $\Lambda^a_{\mathrm{lat}}$,
\item solve the lattice version of the cubic dynamical supercharge equations,
\item verify that the resulting vertex tends to the continuum $K^I\widetilde K^J v_{IJ}(\Lambda)$ form.
\end{enumerate}
To make step 3 concrete, one should parameterize the cubic lattice generators themselves as
\begin{equation}
\label{eq:s15-004}
Q^-_{3\dot a,\mathrm{lat}}
=
{\cal C}_3^{(S)}\,
K^I_{\mathrm{lat}}\,
s^{\mathrm{lat}}_{I\dot a}(\Lambda_{\mathrm{lat}};\theta_{I_\pm},\pi_{\theta,I_\pm})\,
|V_{\mathrm{kin}}\rangle,
\end{equation}
\begin{equation}
\label{eq:s15-005}
\widetilde Q^-_{3\widetilde a,\mathrm{lat}}
=
{\cal C}_3^{(S)}\,
\widetilde K^I_{\mathrm{lat}}\,
\widetilde s^{\mathrm{lat}}_{I\widetilde a}(\Lambda_{\mathrm{lat}};\theta_{I_\pm},\pi_{\theta,I_\pm})\,
|V_{\mathrm{kin}}\rangle,
\end{equation}
and
\begin{equation}
\label{eq:s15-006}
H_{3,\mathrm{lat}}
=
{\cal C}_3^{(S)}\,
K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}\,
v^{\mathrm{lat}}_{IJ}(\Lambda_{\mathrm{lat}};\theta_{I_\pm},\pi_{\theta,I_\pm})\,
|V_{\mathrm{kin}}\rangle.
\end{equation}
Here $s^{\mathrm{lat}}_{I\dot a}$ and $\widetilde s^{\mathrm{lat}}_{I\widetilde a}$ are the left- and right-moving local fermionic polynomials that appear in the cubic dynamical supercharges, while $v^{\mathrm{lat}}_{IJ}$ is the local Hamiltonian polynomial introduced above. I write the right-moving spinor index as $\widetilde a$ rather than reusing $\dot a$ because the precise chirality bookkeeping depends on whether one ultimately specializes to IIA or IIB conventions; the present note has not fixed those component conventions completely. The lattice closure problem is then
\begin{equation}
\label{eq:s15-007}
\{Q^-_{2\dot a},Q^-_{3\dot b,\mathrm{lat}}\}
+\{Q^-_{3\dot a,\mathrm{lat}},Q^-_{2\dot b}\}
=
2\delta_{\dot a\dot b}H_{3,\mathrm{lat}},
\end{equation}
\begin{equation}
\label{eq:s15-008}
\{\widetilde Q^-_{2\widetilde a},\widetilde Q^-_{3\widetilde b,\mathrm{lat}}\}
+\{\widetilde Q^-_{3\widetilde a,\mathrm{lat}},\widetilde Q^-_{2\widetilde b}\}
=
2\delta_{\widetilde a\widetilde b}H_{3,\mathrm{lat}},
\end{equation}
together with the vanishing of the mixed left/right anticommutator at order $g$. Once one chooses a finite local basis for the bosonic stencils and for the SO$(8)$-covariant Grassmann polynomials $s^{\mathrm{lat}},\widetilde s^{\mathrm{lat}},v^{\mathrm{lat}}$, these relations reduce to a finite system of algebraic equations for the coefficient functions and the overall normalization ${\cal C}_3^{(S)}$. That is the precise sense in which the discrete supercharge-closure problem fixes the cubic superstring vertex.
The odd Grassmann degree of the dynamical supercharges means that one may parameterize the left-moving local polynomial as
\begin{equation}
\label{eq:s15-009}
\begin{aligned}
s^{\mathrm{lat}}_{I\dot a}
&=
B^{(1)}_{I\dot a,a}\,\Lambda_{\mathrm{lat}}^a
+B^{(3)}_{I\dot a,abc}\,\Lambda_{\mathrm{lat}}^a\Lambda_{\mathrm{lat}}^b\Lambda_{\mathrm{lat}}^c\\
&\quad
+B^{(5)}_{I\dot a,a_1\cdots a_5}\,
\Lambda_{\mathrm{lat}}^{a_1}\cdots\Lambda_{\mathrm{lat}}^{a_5}
+B^{(7)}_{I\dot a,a_1\cdots a_7}\,
\Lambda_{\mathrm{lat}}^{a_1}\cdots\Lambda_{\mathrm{lat}}^{a_7},
\end{aligned}
\end{equation}
and similarly for $\widetilde s^{\mathrm{lat}}_{I\widetilde a}$. Here each $B^{(2p+1)}$ is itself allowed to depend on the local finite-$a$ completion data $(\theta_{I_+},\theta_{I_-},\pi_{\theta,I_+},\pi_{\theta,I_-})$. After choosing a definite SO$(8)$ gamma-matrix convention, each $B^{(2p+1)}$ can be expanded on a finite basis of invariant tensors built from $\delta_{IJ}$, $\epsilon_{a_1\cdots a_8}$, and the gamma matrices. For instance, the leading continuum-motivated representatives are of the form
\begin{equation}
\label{eq:s15-010}
B^{(1)}_{I\dot a,a}\propto \gamma^I_{a\dot a},
\qquad
B^{(3)}_{I\dot a,abc}\propto (\gamma^{IJ})_{[ab}\gamma^J_{c]\dot a},
\end{equation}
while the degree-$5$ and degree-$7$ sectors are their SO$(8)$ Hodge duals in spinor-index space. I am being explicit here about the level of generality: the note does \emph{not} yet prove that only one coefficient survives at each odd degree, nor does it fix the detailed finite-$a$ endpoint completion. What it does establish is that, once a local support and a gamma-matrix convention are chosen, the cubic supercharge problem becomes a finite-dimensional algebraic system rather than an open-ended functional ansatz.
In particular, after fixing a concrete invariant basis
\begin{equation}
\label{eq:s15-011}
S^{(1)}_{I\dot a},\ S^{(3)}_{I\dot a},\ S^{(5)}_{I\dot a},\ S^{(7)}_{I\dot a},
\qquad
\widetilde S^{(1)}_{I\widetilde a},\ \widetilde S^{(3)}_{I\widetilde a},\ \widetilde S^{(5)}_{I\widetilde a},\ \widetilde S^{(7)}_{I\widetilde a},
\end{equation}
for the odd fermionic tensors and
\begin{equation}
\label{eq:s15-012}
V^{(0)}_{IJ},\ V^{(2)}_{IJ},\ V^{(4)}_{IJ},\ V^{(6)}_{IJ},\ V^{(8)}_{IJ},
\end{equation}
for the even Hamiltonian tensors, the minimal closure truncation takes the explicit coefficient form
\begin{equation}
\label{eq:s15-013}
s^{\mathrm{lat}}_{I\dot a}
=
b_1 S^{(1)}_{I\dot a}
+b_3 S^{(3)}_{I\dot a}
+b_5 S^{(5)}_{I\dot a}
+b_7 S^{(7)}_{I\dot a},
\end{equation}
\begin{equation}
\label{eq:s15-014}
\widetilde s^{\mathrm{lat}}_{I\widetilde a}
=
\widetilde b_1 \widetilde S^{(1)}_{I\widetilde a}
+\widetilde b_3 \widetilde S^{(3)}_{I\widetilde a}
+\widetilde b_5 \widetilde S^{(5)}_{I\widetilde a}
+\widetilde b_7 \widetilde S^{(7)}_{I\widetilde a},
\end{equation}
\begin{equation}
\label{eq:s15-015}
v^{\mathrm{lat}}_{IJ}
=
a_0 V^{(0)}_{IJ}
+a_2 V^{(2)}_{IJ}
+a_4 V^{(4)}_{IJ}
+a_6 V^{(6)}_{IJ}
+a_8 V^{(8)}_{IJ}.
\end{equation}
Combined with the bosonic support-three stencil parameters $(t_+,t_-)$ and the overall normalization ${\cal C}_3^{(S)}$, this turns the lattice cubic supercharge problem into a finite set of unknown coefficients
\begin{equation}
\label{eq:s15-016}
(t_+,t_-,b_1,b_3,b_5,b_7,\widetilde b_1,\widetilde b_3,\widetilde b_5,\widetilde b_7,a_0,a_2,a_4,a_6,a_8,{\cal C}_3^{(S)}),
\end{equation}
to be constrained by the discrete superalgebra. The point of writing the problem this way is not to pretend that the coefficients are already known, but to make clear that the remaining task is finite and algebraic once the local support and convention basis are fixed.
There is also a useful structural simplification before any component calculation is done. On the fermionic zero-mode Clifford module, the \emph{free} dynamical supercharge acts by the sum of one piece that raises the $\Lambda$-degree by one and one piece that lowers it by one. Abstractly one may therefore write
\begin{equation}
\label{eq:s15-017}
Q^-_{2\dot a}
=
q^{(+)}_{2\dot a}+q^{(-)}_{2\dot a}+Q^-_{2\dot a,\mathrm{osc}},
\qquad
\widetilde Q^-_{2\widetilde a}
=
\widetilde q^{(+)}_{2\widetilde a}+\widetilde q^{(-)}_{2\widetilde a}+\widetilde Q^-_{2\widetilde a,\mathrm{osc}},
\end{equation}
where $q^{(+)}$ denotes the part that wedges one more fermionic zero mode, $q^{(-)}$ denotes the part that contracts one zero mode, and $Q_{2,\mathrm{osc}}$ denotes the nonzero-mode contribution. This decomposition is an imported continuum structural fact about the lightcone GS Clifford module; the note is not claiming to have rederived the full finite-$N$ component formulas here.

Once one factors out the common bosonic operator $K_{\mathrm{lat}}$ or $\widetilde K_{\mathrm{lat}}$ and suppresses the nonzero-mode bookkeeping, the cubic closure equations split by even $\Lambda$-degree. Schematically, the left-moving sector takes the block-triangular form
\begin{equation}
\label{eq:s15-018}
\begin{aligned}
\deg 0: &\qquad q^{(-)}\cdot S^{(1)} \sim a_0 V^{(0)},\\
\deg 2: &\qquad q^{(+)}\cdot S^{(1)} + q^{(-)}\cdot S^{(3)} \sim a_2 V^{(2)},\\
\deg 4: &\qquad q^{(+)}\cdot S^{(3)} + q^{(-)}\cdot S^{(5)} \sim a_4 V^{(4)},\\
\deg 6: &\qquad q^{(+)}\cdot S^{(5)} + q^{(-)}\cdot S^{(7)} \sim a_6 V^{(6)},\\
\deg 8: &\qquad q^{(+)}\cdot S^{(7)} \sim a_8 V^{(8)},
\end{aligned}
\end{equation}
and similarly in the right-moving sector with tilded quantities. Here ``$\sim$'' means equality after the common local bosonic factor and the relevant gamma-matrix basis have been projected onto the chosen invariant tensors. The nonzero-mode part of the free supercharge modifies the coefficients in these relations but does not change their degree pattern.

This degree decomposition already gives several exact selection rules. For example, the scalar Hamiltonian coefficient $a_0$ can only be generated from the degree-1 supercharge sector, while the top component $a_8$ can only be generated from the degree-7 sector. Likewise, the degree-2, 4, and 6 Hamiltonian blocks couple only neighboring odd sectors. So once a concrete gamma-matrix basis is fixed, the closure equations are not an arbitrary dense system: they are organized into a short nearest-neighbor chain in Grassmann degree. This does not solve the coefficient values, but it sharply constrains how the solution can look.
One can make this sparsity slightly more explicit without pretending to have solved the component algebra. If the chosen invariant basis is such that each projected block is one-dimensional, then the left-moving free supercharge acts by numerical coefficients
\begin{equation}
\label{eq:s15-019}
\begin{aligned}
q^{(-)}\cdot S^{(1)}&=\lambda_0\,V^{(0)},\\
q^{(+)}\cdot S^{(1)}&=\lambda_{21}\,V^{(2)},
\qquad
q^{(-)}\cdot S^{(3)}=\lambda_{23}\,V^{(2)},\\
q^{(+)}\cdot S^{(3)}&=\lambda_{43}\,V^{(4)},
\qquad
q^{(-)}\cdot S^{(5)}=\lambda_{45}\,V^{(4)},\\
q^{(+)}\cdot S^{(5)}&=\lambda_{65}\,V^{(6)},
\qquad
q^{(-)}\cdot S^{(7)}=\lambda_{67}\,V^{(6)},\\
q^{(+)}\cdot S^{(7)}&=\lambda_8\,V^{(8)},
\end{aligned}
\end{equation}
and similarly in the right-moving sector with tilded coefficients. Then the projected left-moving closure chain takes the concrete sparse matrix form
\begin{equation}
\label{eq:s15-020}
2
\begin{pmatrix}
a_0\\ a_2\\ a_4\\ a_6\\ a_8
\end{pmatrix}
=
\begin{pmatrix}
\lambda_0 & 0 & 0 & 0\\
\lambda_{21} & \lambda_{23} & 0 & 0\\
0 & \lambda_{43} & \lambda_{45} & 0\\
0 & 0 & \lambda_{65} & \lambda_{67}\\
0 & 0 & 0 & \lambda_8
\end{pmatrix}
\begin{pmatrix}
b_1\\ b_3\\ b_5\\ b_7
\end{pmatrix},
\end{equation}
with an analogous tilded equation on the right-moving side. In this reduced setting the endpoint equations fix the degree-1 and degree-7 sectors first, and the middle three equations only propagate information one step at a time through the chain. I emphasize again that the numbers $\lambda_\bullet$ are not being guessed here: they are precisely the projected matrix elements of the finite-$N$ free dynamical supercharge in the chosen SO$(8)$ basis, and computing them is one of the concrete tasks still left open.
At present the note identifies this calculation but does not perform it explicitly: neither the discrete supercharge-closure equations nor the resulting on-shell superstring three-point amplitudes have yet been worked out in detail. As in the bosonic case, the on-shell three-point comparison is logically secondary to the operator statement. One should first solve the cubic supercharge constraints at the level of operators and only then use conventional oscillator-basis on-shell amplitudes as a comparison test. At this order the cubic vertex can be made super-Poincare invariant. However, as emphasized already in \cite{GreenSeiberg1988} and revisited recently in \cite{Ando2025}, the cubic vertex alone is not the full interacting theory: quartic contact terms are required at order $g^2$.

\subsection{On-shell three-graviton check}
The minimal massless external check in the superstring is the three-graviton amplitude. In lightcone GS gauge the massless states live in the fermionic zero-mode Clifford module, not at the first bosonic oscillator level. After choosing the standard SO$(8)$ vector basis $|I\rangle_r$ and $|\widetilde J\rangle_r$ for the left- and right-moving ground-state multiplets on leg $r$, with all nonzero bosonic and fermionic oscillators in their vacuum, a graviton state may be written as
\begin{equation}
\label{eq:s15-1-001}
|h_r\rangle
=
\epsilon_{IJ}^{(r)}\,
|I\rangle_r\otimes |\widetilde J\rangle_r\otimes |0_{\mathrm{osc}};p_r\rangle,
\end{equation}
with $\epsilon_{IJ}^{(r)}$ symmetric and traceless in the transverse SO$(8)$ space. A description based on the first bosonic oscillator level would refer to a higher GS excitation, not to the graviton itself, so it should not be used here. This vector/spinor basis is also the one that appears in the lightcone Ramond-ground-state description familiar from matrix string theory: the left-moving Ramond ground fields are a vector $\psi^I$ and an anti-chiral spinor $S^{\dot a}$, with operator products
\begin{equation}
\label{eq:s15-1-002}
\theta^a(z)\psi^I(0)\sim \frac{1}{\sqrt{2z}}\,\gamma^{I}_{a\dot a}\,S^{\dot a}(0),
\qquad
\theta^a(z)S^{\dot a}(0)\sim \frac{1}{\sqrt{2z}}\,\gamma^{I}_{a\dot a}\,\psi^I(0).
\end{equation}
Keeping only the zero-mode part gives
\begin{equation}
\label{eq:s15-1-003}
\sqrt2\,S_0^a|I\rangle = \gamma^I_{a\dot a}|\dot a\rangle,
\qquad
\sqrt2\,S_0^a|\dot a\rangle = \gamma^I_{a\dot a}|I\rangle,
\end{equation}
which is exactly the explicit $8_v\oplus 8_c$ module implemented in the local helper \texttt{gs\_zero\_mode\_module.py}. So the external graviton basis itself is no longer ambiguous; the remaining ambiguity lies in how the even Grassmann symbol $v_{IJ}(\Lambda)$ is quantized as an operator on that module. For strictly real Minkowski momenta, massless three-point kinematics is degenerate, so the standard nontrivial comparison is understood after analytic continuation to complexified momenta (or an equivalent split-signature kinematics). After rewriting the lightcone $1+2\to 3$ process in the usual all-outgoing convention, the required covariant target structure is
\begin{equation}
\label{eq:s15-1-004}
{\cal A}_{hhh}^{\mathrm{cov}}
=
\kappa\,
\delta^{(10)}\!\left(p_1+p_2+p_3\right)\,
\epsilon_{II'}^{(1)}\epsilon_{JJ'}^{(2)}\epsilon_{KK'}^{(3)}
V^{IJK}(p_1,p_2,p_3)\,
V^{I'J'K'}(p_1,p_2,p_3),
\end{equation}
where
\begin{equation}
\label{eq:s15-1-005}
V^{IJK}(p_1,p_2,p_3)
\equiv
\delta^{IJ}(p_1-p_2)^K
+\delta^{JK}(p_2-p_3)^I
+\delta^{KI}(p_3-p_1)^J.
\end{equation}
This is the familiar Einstein-Hilbert three-graviton tensor written as the product of left- and right-moving Yang-Mills-like factors. Up to field-redefinition-equivalent terms that vanish on shell, there is no other Lorentz-invariant cubic graviton structure.

It is also useful to recall how the corresponding local interaction-point operator appears in the standard continuum three-point derivation. In the NSR presentation one may place three massless $(-1,-1)$-picture vertices at $t=0,1,\infty$ and insert the PCOs at the interaction point
\begin{equation}
\label{eq:s15-1-006}
t_1=\frac{k_1^+}{k_1^++k_2^+}=\frac{\alpha_1}{\alpha_3}.
\end{equation}
For lightcone-adapted polarizations with $\zeta_i^+=0$ and $\zeta_i^-=(k_i^\perp\!\cdot\zeta_i^\perp)/k_i^+$, the pure-ghost pieces and the $\psi^+\partial X^-$ term in the PCO do not contribute to the three-point correlator, while the $\psi^-\partial X^+$ term is proportional to
\begin{equation}
\label{eq:s15-1-007}
\frac{k_1^+}{t_1}+\frac{k_2^+}{t_1-1}=0.
\end{equation}
So the full local matter insertion reduces to the transverse supercurrents $G^\perp(t_1)\widetilde G^\perp(\bar t_1)$ at the join, and the continuum amplitude takes the lightcone form
\begin{equation}
\label{eq:s15-1-008}
{\cal A}_{hhh}^{\mathrm{cov}}
\propto
g_s\,
\frac{(k_1^+)^2(k_2^+)^2}{(k_3^+)^4}\,
\Big\langle
\zeta_3^\perp\!\cdot\psi^\perp\,
\widetilde\zeta_3^\perp\!\cdot\widetilde\psi^\perp\,
e^{ik_3^\perp\cdot X^\perp}(\infty)\,
G^\perp\widetilde G^\perp(t_1)\,
\prod_{r=1}^2
\zeta_r^\perp\!\cdot\psi^\perp\,
\widetilde\zeta_r^\perp\!\cdot\widetilde\psi^\perp\,
e^{ik_r^\perp\cdot X^\perp}(t_r)
\Big\rangle .
\end{equation}
This does \emph{not} determine a unique finite-$a$ lattice stencil, but it gives a concrete continuum target: the discrete prefactor must approach a local transverse interaction-point insertion with a smooth dependence on the lightcone momentum ratio $\lambda=\alpha_1/\alpha_3$, rather than an arbitrary nonlocal momentum polynomial.
This NSR comparison is only a consistency check on the continuum target. It is not a direct operator dictionary for the lattice GS prefactor, since the GS and NSR interaction-point operators are related only after the standard continuum field-redefinition and ghost-dressing machinery.

From the cubic lightcone vertex written earlier, the actual matrix element to be evaluated is
\begin{equation}
\label{eq:s15-1-009}
\begin{aligned}
{\cal A}_{hhh}^{\mathrm{lc}}(N)
&\equiv
\langle h_1,h_2,h_3|H_3\rangle \\
&=
{\cal C}_3^{(S)}\,
\epsilon_{I_1J_1}^{(1)*}\epsilon_{I_2J_2}^{(2)*}\epsilon_{I_3J_3}^{(3)*}
\langle I_1,\widetilde J_1;I_2,\widetilde J_2;I_3,\widetilde J_3;
0_{\mathrm{osc}};p_1,p_2,p_3| \\
&\qquad\times
K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}
v^{\mathrm{lat}}_{IJ}(\Lambda_{\mathrm{lat}})
|V_{\mathrm{kin}}\rangle .
\end{aligned}
\end{equation}
For real polarization tensors the complex conjugation on the bra may be dropped, but the starred form is the correct one for the complexified kinematics used in analytic continuation arguments.
For the tree-level graviton check this zero-mode contraction can now be written explicitly in one reduced $\Lambda$ ansatz suggested by the Dijkgraaf--Motl dictionary
\(
v^{ij}(\Lambda)\leftrightarrow 16\,\Sigma^j\widetilde\Sigma^i
\).
In that convention a vector-vector ground state with transverse polarization $\epsilon_{IJ}$ is represented by the local fermionic wavefunction
\begin{equation}
\label{eq:s15-1-009a}
\Psi_\epsilon(\lambda)
\equiv
\frac1{16}\,\epsilon_{IJ}\,v^{JI}(\lambda).
\end{equation}
The kinematical part of the cubic measure contains
\(
\Delta^8(\lambda_1+\lambda_2+\lambda_3)
\),
and the elementary Grassmann identity
\(
\int d\eta\,(\xi+\eta)f(\eta)=f(\xi)
\)
reduces the three-string zero-mode integral to a 16-Grassmann integral:
\begin{equation}
\label{eq:s15-1-009b}
\begin{aligned}
{\cal A}^{(F)}_{hhh}(N)
&=
T_{\rm bos}^{IJ}(N)
\int d^8\lambda_1\,d^8\lambda_2\,
\Psi_{\epsilon^{(1)}}(\lambda_1)\,
\Psi_{\epsilon^{(2)}}(\lambda_2)\,
\Psi_{\epsilon^{(3)}}(\lambda_1+\lambda_2)
\\
&\qquad\times
v_{IJ}\!\left(\lambda\,\lambda_2-(1-\lambda)\lambda_1\right),
\qquad
\lambda\equiv \frac{\alpha_1}{\alpha_3},
\end{aligned}
\end{equation}
with
\begin{equation}
\label{eq:s15-1-009c}
T_{\rm bos}^{IJ}(N)=A_\delta(N)\,\delta^{IJ}+B_{qq}(N)\,\hat q^I\hat q^J.
\end{equation}
This is implemented directly in the new helper \texttt{fermionic\_graviton\_contraction.py}. Numerically, the key point is that after the $\Delta^8$ reduction the entire problem becomes a sparse polynomial computation in the 16 Grassmann variables
\(
\lambda_1^1,\dots,\lambda_1^8,\lambda_2^1,\dots,\lambda_2^8
\).
The Berezin integral is then nothing but extraction of the top-form coefficient:
\begin{equation}
\label{eq:s15-1-009d}
\int d^8\lambda_1\,d^8\lambda_2\,
P(\lambda_1,\lambda_2)
=
\bigl[\lambda_1^1\cdots\lambda_1^8\lambda_2^1\cdots\lambda_2^8\bigr]\,
P(\lambda_1,\lambda_2).
\end{equation}
In practice the code expands the three external wavefunctions and the local prefactor as sparse dictionaries of monomials, multiplies them with explicit Grassmann signs, and then reads off the coefficient of the unique degree-16 monomial above. A dedicated regression compares this reduced 16-variable evaluation against the brute-force 24-variable integral with the explicit $\Delta^8(\lambda_1+\lambda_2+\lambda_3)$ insertion and finds agreement at the level
\begin{equation}
\label{eq:s15-1-009e}
\bigl|{\cal A}^{(F)}_{\rm brute}-{\cal A}^{(F)}_{\rm reduced}\bigr|
=1.7\times 10^{-13}
\end{equation}
in the benchmark reduction test. So the missing tree-level fermionic zero-mode contraction is no longer merely schematic: in a fixed reduced $\Lambda$ ansatz it is now an explicit finite-dimensional Grassmann calculation. This statement needs a clear caveat. The calculation below does not derive the exact local finite-$N$ interaction-point fermion from the strip endpoint data. Instead it assumes that the overlap-constrained averaged coordinate $\Lambda_{\mathrm{lat}}$ is an adequate reduced variable on which to evaluate the continuum polynomial $v_{IJ}$. The resulting numerics are therefore tests of that reduced ansatz, not yet of the full local lattice superstring vertex. A further diagnostic in \texttt{gs\_weyl\_symbol\_diagnostic.py} still provides an independent structural check by asking how the same Grassmann symbol acts under the candidate Weyl map on the $8_v\oplus 8_c$ module. Under that auxiliary map the $8_v\to 8_v$ block remains entirely in the minimal SO$(8)$-covariant tensor span
\begin{equation}
\label{eq:s15-1-010}
A(\alpha)\,\delta_{IJ}\delta_{KL}
{}+B(\alpha)\,\delta_{IK}\delta_{JL}
{}+C(\alpha)\,\delta_{IL}\delta_{JK},
\end{equation}
with numerical residual at the $10^{-13}$--$10^{-14}$ level in the sample checks $\alpha=\frac12,1,2,3$. Here $K,L$ label the external vector basis states. So the candidate Weyl map introduces no exotic tensor structures on the graviton sector. What remains unresolved is not only the overall normalization, but also the precise relation between this reduced $\Lambda$ ansatz, the genuinely local interaction-point operator, the Weyl-ordered Clifford realization, and the lattice supercharge-closure derivation.

The nonzero-mode bosonic part of this matrix element can, however, already be reduced explicitly. Let $S_r$ be an $N_r\times (N_r-1)$ matrix whose columns form an orthonormal real basis of the zero-sum subspace
\begin{equation}
\label{eq:s15-1-011}
\left\{v\in\RR^{N_r}~\big|~{\bf 1}_{N_r}^Tv=0\right\},
\end{equation}
so that
\begin{equation}
\label{eq:s15-1-012}
S_r^TS_r=\mathbb I_{N_r-1},
\qquad
S_rS_r^T=\mathbb I_{N_r}-\frac{1}{N_r}{\bf 1}_{N_r}{\bf 1}_{N_r}^T.
\end{equation}
A concrete choice is the real cosine/sine basis used in the diagnostic scripts, but the formulas below depend only on these abstract projection properties. Also note that the site-space rows $d_+$ and $d_-$ introduced here act on the individual leg variables before the embedding into the global boundary vector ${\bf X}$ discussed in Section~8. With this understood, let
\begin{equation}
\label{eq:s15-1-013}
d_+ = (-1,1,0,\dots,0),
\qquad
d_- = (1,0,\dots,0,-1)
\end{equation}
be the site-space rows implementing the present nearest-neighbor choices
\(
\nabla_+X_{I_+}^{(1)}=X_1^{(1)}-X_{I_+}
\)
and
\(
\nabla_-X_{I_-}^{(2)}=X_{I_-}-X_{N_2-1}^{(2)}.
\)
In the stacked incoming real nonzero-mode variable
\begin{equation}
\label{eq:s15-1-014}
Q \equiv \begin{pmatrix} q^{(1)}_{\mathrm{phys}} \\ q^{(2)}_{\mathrm{phys}} \end{pmatrix},
\end{equation}
define the corresponding linear functionals
\begin{equation}
\label{eq:s15-1-015}
D_+ \equiv \bigl(d_+S_1,\,0\bigr),
\qquad
D_- \equiv \bigl(0,\,d_-S_2\bigr).
\end{equation}
With the same Gaussian data $G_T$, $B_T$, $C_T$, and $\gamma_T=C_T-B_T^TG_T^{-1}B_T$ introduced in the bosonic three-tachyon section, the fixed-$y$ bosonic integral satisfies
\begin{equation}
\label{eq:s15-1-016}
\bigl\langle (D_+Q)(D_-Q)\bigr\rangle_y
=
\Sigma_{+-}+\eta_+\eta_-\,y^2,
\end{equation}
where
\begin{equation}
\label{eq:s15-1-017}
\Sigma_{+-}\equiv D_+G_T^{-1}D_-^T,
\qquad
\eta_\pm \equiv -D_\pm G_T^{-1}B_T.
\end{equation}
After Fourier transforming the relative center-of-mass displacement $y$ to the relative transverse momentum $q_{\mathrm{rel}}$, one finds the exact finite-$N$ bosonic prefactor tensor
\begin{equation}
\label{eq:s15-1-018}
\begin{aligned}
\langle 0_{\mathrm{osc}};p_1,p_2,p_3|
K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}
|V_3^{(B)}\rangle
&=
a^{-1}c_K\widetilde c_K\,
{\cal A}^{(B)}_{\mathrm{vac}}(N;q_{\mathrm{rel}})
\\
&\quad\times
\left[
\left(\Sigma_{+-}+\frac{\eta_+\eta_-}{\gamma_T}\right)\delta^{IJ}
-
\frac{\eta_+\eta_-}{\gamma_T^2}\,
q_{\mathrm{rel}}^I q_{\mathrm{rel}}^J
\right],
\end{aligned}
\end{equation}
with ${\cal A}^{(B)}_{\mathrm{vac}}(N;q_{\mathrm{rel}})$ the bosonic vacuum matrix element without local prefactor insertions. So the bosonic piece of the three-graviton calculation is already an explicit discrete Gaussian computation; the unresolved part is the matching of the local operator basis and the fermionic zero-mode tensor carried by $v^{\mathrm{lat}}_{IJ}(\Lambda_{\mathrm{lat}})$.

This explicit reduction also exposes a real finite-$a$ issue. For the present minimal right-arc stencil $d_-=(1,0,\dots,0,-1)$, a direct scan of the exact discrete formulas over
\begin{equation}
\label{eq:s15-1-019}
4\le N_1,N_2\le 40
\end{equation}
gives
\begin{equation}
\label{eq:s15-1-020}
\max |\eta_-| \approx 5.4\times 10^{-15},
\end{equation}
while $\Sigma_{+-}$ and $\eta_+$ remain of order $10^{-1}$ on the same grid. So the current nearest-neighbor ansatz produces, to numerical precision, only the $\delta^{IJ}$ term and no $q_{\mathrm{rel}}^Iq_{\mathrm{rel}}^J$ term at all. By contrast, nearby local one-site differences on the same leg do \emph{not} show this vanishing. Thus the cancellation is specific to the present right-arc choice, not a generic consequence of locality. This is exactly the kind of issue that the discrete supercharge-closure calculation has to settle: either the correct lattice $\widetilde K_{\mathrm{lat}}$ differs from the minimal nearest-neighbor representative, or a finite-$a$ local counterterm/improvement must be included before the three-graviton tensor can match its continuum target.

There is also a simple exact explanation for this vanishing. Let $J_r$ be the site-reversal matrix on incoming leg $r$, $(J_r)_{mn}=\delta_{m,N_r-1-n}$, and let
\begin{equation}
\label{eq:s15-1-021}
\Pi_r \equiv S_r^T J_r S_r,
\qquad
\Pi\equiv \mathrm{diag}(\Pi_1,\Pi_2),
\end{equation}
be the induced parity operator in the stacked real nonzero-mode basis. The exact discrete Gaussian data satisfy
\begin{equation}
\label{eq:s15-1-022}
\Pi G_T=G_T\Pi,
\qquad
\Pi B_T=B_T,
\end{equation}
so the source response $G_T^{-1}B_T$ is parity-even. Concretely, the mode metrics commute with $\Pi_r$ because $\omega_{N_r-m}=\omega_m$, and the overlap blocks are compatible with simultaneous site reversal on the incoming and outgoing legs, which together imply the stated symmetry of $G_T$ and $B_T$. By contrast, the minimal right-arc difference
\begin{equation}
\label{eq:s15-1-023}
d_-=(1,0,\dots,0,-1)
\end{equation}
is parity-odd under $J_2$, hence $D_-$ is odd under $\Pi$ and therefore
\begin{equation}
\label{eq:s15-1-024}
\eta_-=-D_-G_T^{-1}B_T=0
\end{equation}
exactly. So the missing $q_{\mathrm{rel}}^Iq_{\mathrm{rel}}^J$ term is not an accidental floating-point cancellation; it is enforced by a discrete symmetry of the present first-order ansatz.
Indeed, writing $X\equiv G_T^{-1}B_T$, the parity relations above imply $\Pi X=X$ and $D_-\Pi=-D_-$. Therefore
\begin{equation}
\label{eq:s15-1-024a}
\eta_-
=
-D_-X
=
-D_-\Pi X
=
-(-D_-)X
=
D_-X
=
-\eta_-,
\end{equation}
which forces $\eta_-=0$ exactly.

This also shows how the obstruction can be removed without abandoning locality. The one-sided second-order right-arc stencil already written earlier,
\begin{equation}
\label{eq:s15-1-025}
\widetilde D^{(2)}_{I_-}X^{(2)}
\equiv
\frac{3X_{I_-}-4X_{N_2-1}^{(2)}+X_{N_2-2}^{(2)}}{2},
\end{equation}
is not parity-odd, so it need not annihilate the even source response. Numerically it indeed restores a nonzero momentum-bilinear coefficient. For example, at
\begin{equation}
\label{eq:s15-1-026}
(N_1,N_2)=(16,24)
\end{equation}
one finds
\begin{equation}
\label{eq:s15-1-027}
\eta_-^{(2)}\approx -5.57\times 10^{-2},
\qquad
B_{qq}^{(2)}\approx 5.38\times 10^{-2},
\end{equation}
whereas the first-order stencil gives $\eta_-\approx 0$ and $B_{qq}\approx 0$. So locality by itself is not the problem; the issue is that the raw first-order representative is too constrained by parity to reproduce the expected graviton tensor structure.

The left/right ordering comparison makes the same point more sharply. At $(N_1,N_2)=(16,24)$ one finds
\begin{equation}
\label{eq:s15-1-028}
\begin{aligned}
(\text{minimal},\text{minimal})&:
&&\eta_+\approx 1.10\times 10^{-1},\qquad
\eta_-\approx 0,\qquad
B_{qq}\approx 0,\\
(\text{minimal},\text{second})&:
&&\eta_+\approx 1.10\times 10^{-1},\qquad
\eta_-\approx -5.57\times 10^{-2},\qquad
B_{qq}\approx 5.38\times 10^{-2},\\
(\text{second},\text{second})&:
&&\eta_+\approx 1.28\times 10^{-1},\qquad
\eta_-\approx -5.57\times 10^{-2},\qquad
B_{qq}\approx 6.28\times 10^{-2}.
\end{aligned}
\end{equation}
So the essential obstruction is on the right arc, but a symmetric second-order choice on both arcs is the cleanest local finite-$a$ ansatz if one wants the two chiral prefactors to be treated on the same footing before imposing supercharge closure.

In fact, on the fixed-ratio family $N_1:N_2=2:3$, the symmetric second-order choice has a stable large-$N$ limit:
\begin{equation}
\label{eq:s15-1-029}
N_1 B_{qq}\to 1.156\ldots,
\qquad
\sqrt{N_1}\,\eta_+\to 0.575\ldots,
\qquad
\sqrt{N_1}\,\eta_-\to -0.255\ldots,
\qquad
A_\delta\to 0.305\ldots.
\end{equation}
Thus the explicit prefactor coefficient $a^{-1}B_{qq}$ and the one-point responses $a^{-1/2}\eta_\pm$ approach finite nonzero limits on this family. This does not yet prove that the symmetric second-order stencil is the \emph{correct} GS discretization, but it makes it the most plausible local starting point for the forthcoming discrete supercharge-closure analysis.

The same behavior is not confined to that single ratio. If one samples the large-$N$ family
\begin{equation}
\label{eq:s15-1-030}
N_1=128\,a,
\qquad
N_2=128\,b,
\qquad
\lambda\equiv \frac{\alpha_1}{\alpha_3}\approx \frac{a}{a+b},
\end{equation}
with $(a,b)=(1,3),(1,2),(3,5),(2,3),(1,1)$, one finds
\begin{equation}
\label{eq:s15-1-031}
\begin{array}{c|cccc}
\lambda & N_1B_{qq} & \sqrt{N_1}\,\eta_+ & \sqrt{N_1}\,\eta_- & A_\delta\\
\hline
\frac14 & 0.912 & 0.476 & -0.211 & 0.311\\
\frac13 & 1.025 & 0.527 & -0.234 & 0.311\\
\frac38 & 1.104 & 0.557 & -0.247 & 0.308\\
\frac25 & 1.147 & 0.571 & -0.253 & 0.309\\
\frac12 & 1.360 & 0.627 & -0.277 & 0.312
\end{array}
\end{equation}
and the coefficients vary smoothly with $\lambda$. So the improved bosonic prefactor does not merely work on one special fixed-ratio family; it appears to define a genuine ratio-dependent continuum profile. What remains open is to derive, from supercharge closure rather than numerical fitting, which local lattice representative within that smooth family is the physically correct one.

It is useful to make this finite local freedom explicit. If one restricts to support on the first three sites of each incoming arc and requires that the site-space rows annihilate constants exactly and differentiate linear profiles exactly, then the most general one-sided local family is
\begin{equation}
\label{eq:s15-1-032}
D^{(t_+)}_{I_+}X^{(1)}
\equiv
(-1+t_+)X_{I_+}
+(1-2t_+)X_1^{(1)}
+t_+X_2^{(1)},
\end{equation}
\begin{equation}
\label{eq:s15-1-033}
\widetilde D^{(t_-)}_{I_-}X^{(2)}
\equiv
(1+t_-)X_{I_-}
-(1+2t_-)X_{N_2-1}^{(2)}
+t_-X_{N_2-2}^{(2)}.
\end{equation}
The minimal first-order choice corresponds to $(t_+,t_-)=(0,0)$, whereas the standard one-sided second-order choice corresponds to $(t_+,t_-)=(-\frac12,+\frac12)$. The explicit bosonic three-graviton data show that the amplitude-level test already constrains this family, but does not yet fix it uniquely. Within this support-three family, the right-arc stencil is parity-odd only at $t_-=0$. Thus the raw first-order choice carries an accidental discrete symmetry that suppresses the physical momentum-bilinear tensor, whereas the second-order choice already breaks that accidental parity obstruction. For example, at $(N_1,N_2)=(16,24)$ one finds
\begin{equation}
\label{eq:s15-1-034}
\begin{aligned}
(t_+,t_-)=(0,0)&:
&&N_1B_{qq}\approx 0,\\
(t_+,t_-)=(0,\tfrac12)&:
&&N_1B_{qq}\approx 0.861,\\
(t_+,t_-)=(-\tfrac12,\tfrac12)&:
&&N_1B_{qq}\approx 1.005.
\end{aligned}
\end{equation}
So the bosonic test rules out the parity-odd right-endpoint $t_-=0$, but it does \emph{not} by itself single out a unique remaining local admixture. What makes $(t_+,t_-)=(-\frac12,+\frac12)$ special is not that the bosonic amplitude forces it, but that it is the unique member of this support-three family that is second-order accurate as a one-sided derivative. This is exactly the sort of local freedom that the discrete supercharge algebra must remove.

Accordingly, the concrete bosonic ansatz I would now take into the discrete supercharge-closure problem is the symmetric one-sided second-order pair
\begin{equation}
\label{eq:s15-1-035}
D^{(2)}_{I_+}X^{(1)}
\equiv
\frac{-3X_{I_+}+4X_1^{(1)}-X_2^{(1)}}{2},
\qquad
\widetilde D^{(2)}_{I_-}X^{(2)}
\equiv
\frac{3X_{I_-}-4X_{N_2-1}^{(2)}+X_{N_2-2}^{(2)}}{2},
\end{equation}
namely
\begin{equation}
\label{eq:s15-1-036}
K_{\mathrm{lat}}^I
\stackrel{\rm provisional}{=}
a^{-1/2}c_K\,D^{(2)}_{I_+}X^I,
\qquad
\widetilde K_{\mathrm{lat}}^J
\stackrel{\rm provisional}{=}
a^{-1/2}\widetilde c_K\,\widetilde D^{(2)}_{I_-}X^J.
\end{equation}
The word ``provisional'' matters here: this is not yet derived from the discrete superalgebra. It is simply the minimal local choice currently known to survive the bosonic part of the three-graviton test with a smooth ratio-dependent continuum profile. The actual supercharge-closure calculation must still determine whether these stencils are exact, whether additional local admixtures are required, and how the constants $c_K,\widetilde c_K$ are fixed.

It is therefore useful to separate the \emph{current numerical status} of this stencil family from the still-open structural questions. The local regression driver \texttt{numerical\_suite.py} now bundles the bosonic three-tachyon, bosonic $2T+1M$, bosonic normalization-structure fits, the continuum three-tachyon Schur benchmark, the explicit continuum $\mu(\alpha)^2$ factor split, the continuum DM/PS $\Lambda$-convention bridge, bosonic prefactor, Weyl-block, projected-channel, explicit fermionic tree-level contraction in the reduced $\Lambda$ ansatz, pure fermionic response-basis checks, finite-$N$ local interaction-point fermion decomposition checks, the exact mixed-variable local prefactor expansion checks, the exact local channel-polynomial checks, the full local channel catalog, the explicit local nonzero-mode vacuum reduction for the canonical endpoint-difference candidate, the new local three-point tree benchmark assembled from those vacuum-contracted local responses, the dedicated $\lambda$-profile scan of those reduced responses, trace-dropped superstring ansatz checks, a structural comparison to the known flat-space GS lightcone benchmark within the same reduced ansatz, normalization-factorization scripts, the twisted-cylinder loop-building-block diagnostics, the first single-cylinder oscillator-trace prototype, and the stable pre-GSO Bose--Fermi ratio scan into one reproducible checkpoint. In its present form the suite reports $87/87$ passing tests. Within the endpoint-linear family, the scaled local difference
\[
\Lambda_{\mathrm{join}}
=
\sqrt{\frac{N_1N_2}{N_3}}\,(\theta_{I_+}-\theta_{I_-})
\]
is now also fixed uniquely by the finite-$N$ requirements of zero
$\Theta_{\mathrm{cm}}$ contamination and unit $\Lambda_{\mathrm{lat}}$
coefficient. Moreover, the new endpoint-phase scan shows that after
unit-$\Lambda_{\mathrm{lat}}$ normalization the canonical anti-phase endpoint
difference is the unique CM-free equal-magnitude endpoint choice, while the
naive $\theta_{I_+}\pm\ii\theta_{I_-}$ sums carry large
$\Theta_{\mathrm{cm}}$ contamination and a substantially larger local
two-point scalar. The bosonic checks remain sharp: the three-tachyon
factorization residual is at the $10^{-9}$ level and its critical-dimension
scan still singles out $D_\perp=24$, the fixed-ratio Schur benchmark matches
the analytic continuum target with maximum absolute error $1.94\times 10^{-5}$
and maximum relative error $5.37\times 10^{-5}$, while the on-shell factor
split also verifies $\log\mu(\alpha)^2=q_{\mathrm{rel}}^2/(2\gamma_T^{\mathrm{cont}})$ exactly and matches the discrete Richardson limit with maximum absolute error $1.01\times 10^{-6}$ and maximum relative error $2.42\times 10^{-7}$, while the $2T+1M$ continuum fits give
\begin{equation}
\label{eq:s15-1-037}
A_{\rm tr}=-3.68\times 10^{-6}\pm 3.55\times 10^{-6},
\qquad
B_{\rm rel}=1.92026\pm 7.03\times 10^{-4},
\end{equation}
so the trace term is numerically consistent with zero and the physical momentum-bilinear coefficient extrapolates smoothly to a nonzero limit. On the superstring side, for the provisional second-order choice one finds
\begin{equation}
\label{eq:s15-1-038}
N_1 B_{qq}=1.15653\pm 6.86\times 10^{-4},
\qquad
A_\delta=0.305495\pm 5.15\times 10^{-5},
\end{equation}
in the fixed-ratio continuum fit used by the suite.
The new fermionic-contraction helper then evaluates the reduced Grassmann integral \eqref{eq:s15-1-009b} directly. At the benchmark point
\begin{equation}
\label{eq:s15-1-038a}
(N_1,N_2)=(128,192),
\qquad
\lambda=\frac25,
\end{equation}
with the provisional second-order stencil and the on-shell trace drop, define
\begin{equation}
\label{eq:s15-1-038b}
\epsilon_\parallel
\equiv
\sqrt{\frac87}\left(\hat q\hat q-\frac18\delta\right),
\qquad
\epsilon_{23}
\equiv
\frac{e_2e_2-e_3e_3}{\sqrt2},
\qquad
\epsilon_{24}
\equiv
\frac{e_2e_2-e_4e_4}{\sqrt2}.
\end{equation}
Then the explicit fermionic contraction gives
\begin{equation}
\label{eq:s15-1-038c}
\begin{aligned}
{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)
&=4.78557\times 10^{-2},\\
{\cal A}_F(\epsilon_{23},\epsilon_{24},\epsilon_\parallel)
&=2.39279\times 10^{-2},\\
{\cal A}_F(\epsilon_\parallel,\epsilon_\parallel,\epsilon_\parallel)
&=4.79887\times 10^{-1},\\
{\cal A}_F(\epsilon_\parallel,\epsilon_{23},\epsilon_{23})
&=2.99098\times 10^{-1},
\end{aligned}
\end{equation}
while the same calculation gives the exact zeros
\begin{equation}
\label{eq:s15-1-038d}
{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_{\rm dil})
=
{\cal A}_F(\epsilon_\parallel,\epsilon_\parallel,\epsilon_{\rm dil})
=
{\cal A}_F(\epsilon_{23},\epsilon_{23},B_{23})
=
{\cal A}_F(\epsilon_\parallel,\epsilon_\parallel,B_{23})
=0
\end{equation}
to machine precision in the present regression test. So the tree-level fermionic piece now really has been assembled in explicit polarization channels, not only in the auxiliary Weyl-block proxy.

For the later scans it is useful to separate the bosonic prefactor data from the purely fermionic channel responses. For any fixed polarization channel ${\cal C}$ one may write
\begin{equation}
\label{eq:s15-1-038d1}
{\cal A}_F^{\cal C}(N;\lambda,t)
=
A_\delta(N;\lambda,t)\,{\cal R}^{\cal C}_\delta(\lambda)
+
B_{qq}(N;\lambda,t)\,{\cal R}^{\cal C}_{qq}(\lambda),
\end{equation}
where ${\cal R}^{\cal C}_\delta$ and ${\cal R}^{\cal C}_{qq}$ are obtained by evaluating the same Grassmann integral with $T_{\rm bos}^{IJ}=\delta^{IJ}$ and $T_{\rm bos}^{IJ}=\hat q^I\hat q^J$ separately. This decomposition is implemented explicitly in the helper and cached, so once a given $\lambda$ has been fixed, scanning the stencil family only changes the bosonic coefficients $A_\delta$ and $B_{qq}$.
For the benchmark graviton channels used below, the trace-dropped contraction shows a further simplification on the sampled $\lambda$ grid:
\begin{equation}
\label{eq:s15-1-038d2}
{\cal R}^{(23,23,\parallel)}_\delta(\lambda)
=
{\cal R}^{(23,24,\parallel)}_\delta(\lambda)
=
{\cal R}^{(\parallel,23,23)}_\delta(\lambda)
=0,
\end{equation}
while ${\cal R}^{\cal C}_{qq}(\lambda)$ is nonzero. Numerically one then finds
\begin{equation}
\label{eq:s15-1-038d3}
\frac{{\cal R}^{(23,24,\parallel)}_{qq}(\lambda)}
{{\cal R}^{(23,23,\parallel)}_{qq}(\lambda)}
=
\frac12,
\qquad
\lambda^2
\frac{{\cal R}^{(\parallel,23,23)}_{qq}(\lambda)}
{{\cal R}^{(23,23,\parallel)}_{qq}(\lambda)}
=
1.
\end{equation}
Even more sharply, the dedicated response-grid scan on
\(
\lambda\in\{\frac14,\frac13,\frac38,\frac25,\frac12\}
\)
shows that the diagonal benchmark response itself fits the simple profile
\begin{equation}
\label{eq:s15-1-038d3a}
{\cal R}^{(23,23,\parallel)}_{qq}(\lambda)
=
4\sqrt{14}\,(1-\lambda)^2
\end{equation}
with maximum absolute deviation
\begin{equation}
\label{eq:s15-1-038d3b}
\max_{\rm grid}
\left|
{\cal R}^{(23,23,\parallel)}_{qq}(\lambda)
-4\sqrt{14}\,(1-\lambda)^2
\right|
=2.13\times 10^{-14}.
\end{equation}
This is not confined to the default scan points: the current off-grid
regression check at $\lambda=\frac15$ and $\lambda=\frac35$ also matches the
same closed form, with maximum absolute deviation
\begin{equation}
\label{eq:s15-1-038d3b2}
\max_{\lambda\in\{\frac15,\frac35\}}
\left|
{\cal R}^{(23,23,\parallel)}_{qq}(\lambda)
-4\sqrt{14}\,(1-\lambda)^2
\right|
=1.99\times 10^{-13}.
\end{equation}
So on the sampled grid the other two benchmark graviton responses are already
fixed by \eqref{eq:s15-1-038d3} to
\begin{equation}
\label{eq:s15-1-038d3c}
{\cal R}^{(23,24,\parallel)}_{qq}(\lambda)
=
2\sqrt{14}\,(1-\lambda)^2,
\qquad
{\cal R}^{(\parallel,23,23)}_{qq}(\lambda)
=
4\sqrt{14}\,\frac{(1-\lambda)^2}{\lambda^2}.
\end{equation}
Since the benchmark trace-dropped channels also satisfy
\(
{\cal R}_\delta=0
\),
the assembled amplitudes themselves collapse to
\begin{equation}
\label{eq:s15-1-038d3d}
\begin{aligned}
{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel;N,\lambda,t)
&=
4\sqrt{14}\,(1-\lambda)^2\,B_{qq}(N;\lambda,t),\\
{\cal A}_F(\epsilon_{23},\epsilon_{24},\epsilon_\parallel;N,\lambda,t)
&=
2\sqrt{14}\,(1-\lambda)^2\,B_{qq}(N;\lambda,t),\\
{\cal A}_F(\epsilon_\parallel,\epsilon_{23},\epsilon_{23};N,\lambda,t)
&=
4\sqrt{14}\,\frac{(1-\lambda)^2}{\lambda^2}\,B_{qq}(N;\lambda,t),
\end{aligned}
\end{equation}
with the benchmark dilaton and antisymmetric channels still vanishing. This is
now checked directly in the finite-$N$ family scan: across
\(
t\in\{0,\frac18,\frac14,\frac38,\frac12,\frac58,\frac34\}
\),
\(
\lambda\in\{\frac14,\frac13,\frac38,\frac25,\frac12\}
\),
and
\(
s\in\{16,32,64,128\}
\),
the maximum absolute deviation between the explicit contraction and
\eqref{eq:s15-1-038d3d} is
\begin{equation}
\label{eq:s15-1-038d3e}
\max_{\rm scan}
\bigl|
{\cal A}_F^{\rm explicit}
-{\cal A}_F^{\rm closed\ form}
\bigr|
=1.60\times 10^{-14}.
\end{equation}
\paragraph{Discrete-vs-continuum comparison.}
It is worth spelling out exactly what is being compared here. On the discrete
side,
\(
{\cal A}_F^{\rm explicit}
\)
means the finite-$N$ lightcone-lattice amplitude obtained by combining:
\begin{enumerate}
\item the discretized bosonic nonzero-mode coefficient
\(
B_{qq}(N;\lambda,t)
\)
extracted from the Gaussian sewing problem, and
\item the explicit $16$-Grassmann fermionic contraction in the local
\(
\Lambda
\)
-superfield convention.
\end{enumerate}
On the analytic side, the benchmark target is the flat-space GS lightcone cubic
prefactor projected onto the same polarization channels. In the continuum one has
\(
H_3\propto \mathbb{P}^I\mathbb{P}^J v_{IJ}(\Lambda)
\)
with
\(
\mathbb{P}^I=\alpha_1 p_{(2)}^I-\alpha_2 p_{(1)}^I=-\alpha_3 q_{\mathrm{rel}}^I
\),
so after packaging the still-unresolved overall
$q_{\mathrm{rel}}^Iq_{\mathrm{rel}}^J$ coefficient into
$B_{qq}$ the benchmark targets are exactly the channel formulas in
\eqref{eq:s15-1-038d3d}. Equivalently, the comparison is performed channel by
channel as
\begin{equation}
\label{eq:s15-1-038d3f}
{\cal A}_F^{\rm explicit}(N,\lambda,t)
\quad\text{vs.}\quad
{\cal A}_F^{\rm analytic\ target}(N,\lambda,t)
:=
B_{qq}(N;\lambda,t)\,{\cal R}^{\rm cont}_{qq}(\lambda),
\end{equation}
where
\(
{\cal R}^{\rm cont}_{qq}(\lambda)
\)
is the known continuum response for the chosen benchmark channel. The new helper
\texttt{superstring\_continuum\_benchmark.py} checks this explicit
continuum-lightcone target directly within the same reduced $\Lambda$ ansatz, and the same family scan gives the same
maximum deviation~\eqref{eq:s15-1-038d3e}. So for these benchmark channels the
reduced discrete superstring ansatz is now being compared directly to the known continuum GS cubic
tensor structure in the same reduced convention, but not yet with an
independently fixed overall normalization. In particular, the present benchmark
does \emph{not} yet compare the discrete
\(
B_{qq}(N;\lambda,t)
\)
itself to an independently known continuum normalization coefficient; it tests
that once the unresolved overall coefficient is packaged into
\(
B_{qq}
\),
the polarization selection rules, channel ratios, and
\(
\lambda
\)
-dependence agree with the analytic GS target. Because the locality of the finite-$N$ fermionic insertion has not yet been derived, this should be read as a structural check of the reduced ansatz rather than as a complete validation of the local lattice superstring vertex.
\paragraph{Benchmark response values.}
At the benchmark ratio $\lambda=\frac25$, the new response-level helper in
\texttt{fermionic\_graviton\_contraction.py} gives
\begin{equation}
\label{eq:s15-1-038d4}
{\cal R}^{(23,23,\parallel)}_\delta=0,
\qquad
{\cal R}^{(23,23,\parallel)}_{qq}=5.387986636954\ldots,
\end{equation}
\begin{equation}
\label{eq:s15-1-038d5}
{\cal R}^{(23,24,\parallel)}_\delta=0,
\qquad
{\cal R}^{(23,24,\parallel)}_{qq}=2.693993318477\ldots,
\end{equation}
\begin{equation}
\label{eq:s15-1-038d6}
{\cal R}^{(\parallel,23,23)}_\delta=0,
\qquad
{\cal R}^{(\parallel,23,23)}_{qq}=33.674916480965\ldots,
\end{equation}
while the dilaton and antisymmetric benchmark channels have both
\(
{\cal R}_\delta
\)
and
\(
{\cal R}_{qq}
\)
equal to zero to machine precision in the same check.
So the later universal channel relations are not mysterious fit accidents: for these benchmark channels the trace-dropped fermionic contraction eliminates the $A_\delta$ contribution entirely, and the only surviving stencil dependence comes from the overall bosonic coefficient $B_{qq}$.

The next question is whether these benchmark channels are isolated accidents or
whether they persist in the actual continuum scans. The updated
\texttt{superstring\_decisive\_test.py} now uses the explicit fermionic
contraction itself, not the Weyl-block proxy, over the symmetric family
\begin{equation}
\label{eq:s15-1-038e}
t\in\left\{0,\frac18,\frac14,\frac38,\frac12,\frac58,\frac34\right\},
\qquad
\lambda\in\left\{\frac14,\frac13,\frac38,\frac25,\frac12\right\},
\end{equation}
with fixed-ratio continuum extrapolation on the scale set
\(
N_1=a\,s,\ N_2=b\,s,\ s\in\{16,32,64,128\}
\)
for each ratio family $(a,b)$. The scan tracks one nonzero diagonal graviton channel, one mixed-transverse graviton channel, one channel with the parallel polarization on leg 1, and the dilaton / antisymmetric leakage channels. In that direct scan the
minimal stencil $t=0$ is again the only blocked candidate, while every
unblocked point on the positive branch satisfies
\begin{equation}
\label{eq:s15-1-038f}
\frac{{\cal A}_F(\epsilon_{23},\epsilon_{24},\epsilon_\parallel)}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}
=
\frac12,
\qquad
\lambda^2
\frac{{\cal A}_F(\epsilon_\parallel,\epsilon_{23},\epsilon_{23})}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}
=
1,
\end{equation}
and the dilaton / antisymmetric benchmark channels continue to vanish. The
current regression bounds are
\begin{equation}
\label{eq:s15-1-038g}
\max_{\rm unblocked}
\left|
\frac{{\cal A}_F(\epsilon_{23},\epsilon_{24},\epsilon_\parallel)}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}
-\frac12
\right|
=7.88\times 10^{-15},
\qquad
\max_{\rm unblocked}
\left|
\lambda^2
\frac{{\cal A}_F(\epsilon_\parallel,\epsilon_{23},\epsilon_{23})}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}
-1
\right|
=2.58\times 10^{-14},
\end{equation}
with the corresponding zero channels remaining exactly zero to machine
precision. So at the level of the actual tree-level fermionic contraction, not
merely the auxiliary proxy, the minimal stencil fails and the unblocked branch
already obeys a rigid normalized channel structure.

There is one further scaling point that matters for interpreting these data.
Because the bosonic coefficient satisfies $B_{qq}\sim N_1^{-1}$ on fixed-ratio
families, the raw fermionic channel amplitudes scale the same way. The finite
continuum quantity is therefore
\begin{equation}
\label{eq:s15-1-038h}
\widetilde{\cal A}_{\rm diag}(\lambda,t)
\equiv
\lim_{N_1\to\infty}
N_1\,{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel;\lambda,t).
\end{equation}
The companion script
\texttt{superstring\_normalization\_factorization.py} assembles this quantity
into the positive-branch matrix $\widetilde{\cal A}_{\rm diag}(\lambda,t)$ and
finds that it is again very nearly rank one:
\begin{equation}
\label{eq:s15-1-038i}
\widetilde{\cal A}_{\rm diag}(\lambda,t)\approx {\cal N}(t)\,{\cal F}(\lambda),
\end{equation}
with numerical diagnostics
\begin{equation}
\label{eq:s15-1-038j}
\frac{\sigma_2}{\sigma_1}=1.11\times 10^{-4},
\qquad
\frac{\|\widetilde{\cal A}_{\rm diag}-\widetilde{\cal A}_{\rm rank\;1}\|_F}
{\|\widetilde{\cal A}_{\rm diag}\|_F}
=1.11\times 10^{-4},
\qquad
\max_{t>0,\lambda}
\left|
\frac{\widetilde{\cal A}_{\rm diag}(\lambda,t)}
{\widetilde{\cal A}_{\rm diag}(\frac25,t)}
-
\frac{\widetilde{\cal A}_{\rm diag}(\lambda,\frac12)}
{\widetilde{\cal A}_{\rm diag}(\frac25,\frac12)}
\right|
=6.97\times 10^{-4}.
\end{equation}
So the explicit fermionic contraction does not merely produce isolated
benchmark numbers: once the trivial $1/N_1$ scaling is removed, the surviving
positive branch is numerically very close to one common $\lambda$-profile times
one overall normalization.

The older Weyl-block diagnostics are still useful, but they should now be read
as an auxiliary structural cross-check rather than as the primary decisive
superstring test. The script \texttt{projected\_graviton\_channels.py} combines
the extrapolated bosonic data with the explicit Weyl-quantized $8_v\to 8_v$
block of $v_{IJ}(\Lambda)$. Under the current candidate map this block is
\begin{equation}
\label{eq:s15-1-039}
A=25,
\qquad
B=-32+12\,\ii,
\qquad
C=-32-12\,\ii,
\end{equation}
with numerical residual at the $10^{-14}$ level. Contracting this vector block with the rank-two bosonic tensor
\(
M_{KL}=M_\delta \delta_{KL}+M_{qq}\hat q_K\hat q_L
\)
produces explicit vector and symmetric-traceless polarization channels. Two useful facts come out immediately. First, the parity-blocked minimal stencil $(t_+,t_-)=(0,0)$ remains genuinely blocked in the projected graviton channel, not merely in the raw $B_{qq}$ scan. Second, among the positive symmetric branch $t=t_-=-t_+$ the current projected-channel ranking is
\begin{equation}
\label{eq:s15-1-040}
t=0.75 \ \text{(rank 1)},\qquad
t=0.625 \ \text{(rank 2)},\qquad
t=0.5 \ \text{(rank 3)},
\end{equation}
while $t=0$ is pushed to the bottom once blocked channels are penalized. For the second-order point $t=\frac12$ itself, the projected-channel smoothness diagnostics are
\begin{equation}
\label{eq:s15-1-041}
\begin{aligned}
\text{vector-ratio smoothness} &= 4.43\times 10^{-4},\\
\text{graviton-channel smoothness} &= 4.33\times 10^{-2},\\
\text{graviton-channel relative uncertainty} &= 1.50\times 10^{-3}.
\end{aligned}
\end{equation}
So the numerics now say something more precise than before at the level of the \emph{full} candidate vector block: the minimal stencil is ruled out robustly, the positive-$t$ branch is coherent, and the standard second-order choice remains a strong representative, but those raw projected observables still do not isolate it uniquely from nearby stronger one-sided stencils.

Within that auxiliary proxy, one may also study a trace-dropped on-shell
simplification. In the flat-space three-particle matrix element the terms in
$v_{IJ}$ proportional to $\delta_{IJ}$ do not contribute, so following that
continuum simplification one may drop the corresponding trace pieces in the
present Weyl block. In the current candidate map this leaves
\begin{equation}
\label{eq:s15-1-042}
A_{\rm on}(\lambda)=\frac{8}{\lambda^2},
\qquad
B_{\rm on}(\lambda)= -\frac{32}{\lambda^2}
\;+\;\ii\!\left(\frac{16}{\lambda^3}-\frac{4}{\lambda}\right),
\qquad
C_{\rm on}(\lambda)=\overline{B_{\rm on}(\lambda)},
\end{equation}
with $\lambda=\alpha_1/\alpha_3$, and these coefficients satisfy the exact identity
\begin{equation}
\label{eq:s15-1-043}
8A_{\rm on}+B_{\rm on}+C_{\rm on}=0.
\end{equation}
Therefore the trace-dropped contraction with
\(
T^{IJ}_{\rm bos}=A_\delta \delta^{IJ}+B_{\rm phys}\hat q^I\hat q^J
\)
collapses to
\begin{equation}
\label{eq:s15-1-044}
M_\delta=\frac{8B_{\rm phys}}{\lambda^2},
\qquad
M_{qq}=-\frac{64B_{\rm phys}}{\lambda^2},
\end{equation}
so the normalized projected channels obey the universal relations
\begin{equation}
\label{eq:s15-1-045}
\frac{M_{qq}}{M_\delta}=-8,
\qquad
\frac{{\cal A}_{\rm vec,\parallel}}{{\cal A}_{\rm vec,\perp}}=-7,
\qquad
{\cal A}_{\rm dilaton}=0.
\end{equation}
The new regression script \texttt{superstring\_decisive\_test.py} checks these identities directly over the symmetric family $t\in\{0,\frac18,\frac14,\frac38,\frac12,\frac58,\frac34\}$. Numerically, the minimal stencil $t=0$ is the \emph{only} blocked candidate, while every unblocked candidate obeys the universal relations above to machine precision:
\begin{equation}
\label{eq:s15-1-046}
\max_{\rm unblocked}\left|\frac{{\cal A}_{\rm vec,\parallel}}{{\cal A}_{\rm vec,\perp}}+7\right|
=8.88\times 10^{-16},
\qquad
\max_{\rm unblocked}|{\cal A}_{\rm dilaton}|
=2.27\times 10^{-13}.
\end{equation}
One can go a step further and test whether even that residual normalization dependence factorizes. The companion script \texttt{superstring\_normalization\_factorization.py} assembles the positive symmetric branch $t\in\{\frac18,\frac14,\frac38,\frac12,\frac58,\frac34\}$ into the matrix
\begin{equation}
\label{eq:s15-1-047}
B_{\rm phys}(\lambda,t)
\equiv
\frac{N_1 B_{qq}(\lambda,t)}{\lambda},
\end{equation}
and checks whether it is approximately rank one, i.e.\ whether
\begin{equation}
\label{eq:s15-1-048}
B_{\rm phys}(\lambda,t)\approx {\cal N}(t)\,{\cal F}(\lambda).
\end{equation}
Numerically this factorization is extremely accurate on the unblocked branch:
\begin{equation}
\label{eq:s15-1-049}
\frac{\sigma_2}{\sigma_1}=1.15\times 10^{-4},
\qquad
\frac{\|B_{\rm phys}-B_{\rm rank\;1}\|_F}{\|B_{\rm phys}\|_F}
=1.15\times 10^{-4},
\end{equation}
and after calibrating each candidate at $\lambda=\frac25$ against the second-order point $t=\frac12$, the normalized profile differs from the reference profile by at most
\begin{equation}
\label{eq:s15-1-050}
\max_{t>0,\lambda}
\left|
\frac{B_{\rm phys}(\lambda,t)}{B_{\rm phys}(\frac25,t)}
-
\frac{B_{\rm phys}(\lambda,\frac12)}{B_{\rm phys}(\frac25,\frac12)}
\right|
=7.14\times 10^{-4}.
\end{equation}
This sharpens the superstring story substantially, but only at the level of a reduced fermionic ansatz. First, the tree-level
fermionic zero-mode contraction has been carried out explicitly in that reduced
$\Lambda$ convention, and its benchmark polarization channels already
show the expected graviton / dilaton / $B$-field separation in
\eqref{eq:s15-1-038c}--\eqref{eq:s15-1-038d}. Second, the full
continuum-extrapolated fermionic scan itself now shows that the parity-blocked
minimal stencil is the only blocked candidate, that the unblocked branch
obeys the rigid channel relations \eqref{eq:s15-1-038f} with the bounds in
\eqref{eq:s15-1-038g}, and that the scaled amplitude
$\widetilde{\cal A}_{\rm diag}$ is very close to a rank-one
normalization-times-profile form as in \eqref{eq:s15-1-038j}. Third, the older
Weyl-block proxy remains consistent with that picture as an auxiliary
structural diagnostic. In that sense the superstring test is now genuinely
binary at the level of normalized observables: the parity-blocked minimal
stencil fails, and the unblocked local branch passes the explicit tree-level
fermionic channel relations while differing almost entirely by one
normalization factor. What these statements do not show is that the underlying local finite-$N$ interaction-point fermion has been derived correctly; they show only that once one uses the present reduced $\Lambda$ ansatz, the resulting benchmark channels behave coherently.

So in the superstring case there is no analogue of the bosonic tachyon simplification to a single scalar vacuum amplitude. The bosonic derivative part and the tree-level fermionic zero-mode contraction are now both explicit, but the correct local prefactor basis and the overall normalization are still not fixed uniquely from first principles. This is precisely why the supercharge-closure problem cannot be skipped. Until the lattice coefficients in $K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}v^{\mathrm{lat}}_{IJ}$ are fixed, the three-graviton amplitude cannot yet be claimed as a derived prediction of the cubic vertex rather than a highly constrained numerical candidate.

Therefore the superstring amplitude check is also sharp: once the lattice prefactor $K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}v_{IJ}^{\mathrm{lat}}$ and the overall normalization ${\cal C}_3^{(S)}$ have been fixed by the discrete dynamical supercharge algebra, the matrix element $\langle h_1,h_2,h_3|H_3\rangle$ must reduce in the continuum limit to the tensor above, again up to the conventional external-state normalization. The present note has now completed the explicit tree-level fermionic contraction only in the reduced $\Lambda$ ansatz, and the remaining uncertainty is therefore not just the choice and normalization of the local lattice prefactor, but also the derivation of the correct local finite-$N$ fermionic interaction-point variable itself.

\section{Continuum limit and Neumann structure}
The discrete framework must recover the usual continuum three-string squeeze data in the limit $N_r\to\infty$ at fixed $\alpha_r=aN_r$, but there are actually \emph{two} different finite-$N$ oscillator objects in play and they should not be conflated:
\begin{enumerate}
\item impose the exact overlap in $\sigma$ position space,
\item either keep all three legs and extract the full Neumann data from Gaussian moments of the uneliminated vertex, or eliminate one leg and form the reduced sewn Gaussian used in the explicit vacuum-amplitude calculations,
\item only then transform the chosen object to Fourier modes on each leg.
\end{enumerate}
If one follows the second route and eliminates leg $3$ after solving the position-space overlap, one may transform each leg to discrete Fourier modes,
\begin{equation}
\label{eq:s16-001}
q_m^{(r)}=\frac{1}{\sqrt{N_r}}\sum_{n=0}^{N_r-1} X_n^{(r)} e^{-2\pi \ii mn/N_r},
\qquad
m=1,\dots,N_r-1,
\end{equation}
and the reduced constrained quadratic form at a cubic vertex takes the form
\begin{equation}
\label{eq:s16-002}
Q^{(I)}_{\mathrm{osc}}
=
\frac12
\sum_{r,s=1}^3
\sum_{m,n\geq 1}
q_m^{(r)}\,\bar{\mathcal G}^{rs}_{mn}(N)\,q_n^{(s)}.
\end{equation}
The coefficients $\bar{\mathcal G}^{rs}_{mn}(N)$ are \emph{not} the standard continuum Neumann coefficients $\bar N^{rs}_{mn}$. They belong to the reduced sewn Gaussian obtained after one leg has been substituted out. By contrast, the standard continuum Neumann data should be extracted from the full three-leg overlap vertex through Gaussian moments such as
\begin{equation}
\label{eq:s16-003}
\bar N^{rs}_{mn}(N)
=
-\frac{\langle 0|a_m^{(r)}a_n^{(s)}|V_3^{(B)}\rangle}
{\langle 0|V_3^{(B)}\rangle},
\end{equation}
not by naively inverting the formal boundary-state matrix of Section~11. The reduced form $\bar{\mathcal G}$ and the full Gaussian-moment Neumann data encode related but genuinely different information, and only the latter should be compared entry-by-entry with continuum lightcone Neumann coefficients.

The reason the continuum limit is still plausible is structural: the DFT basis converges to the Fourier basis on the lightcone cylinders, while the embedding maps $P_1,P_2$ converge to inclusion of the two arcs of lengths $\alpha_1,\alpha_2$ into the outgoing cylinder of length $\alpha_3=\alpha_1+\alpha_2$ in the positive-circumference notation. But for the reduced form one must be more careful about what is expected to converge. In a DFT basis with mode metric $M_r$, define the oscillator-normalized reduced coefficients
\begin{equation}
\label{eq:s16-004}
\widehat{\mathcal G}^{rs}_{mn}(N)
\equiv
\frac{\bar{\mathcal G}^{rs}_{mn}(N)}{\sqrt{(M_r)_{mm}(M_s)_{nn}}}.
\end{equation}
Numerically these \emph{normalized reduced} coefficients do not approach finite entrywise limits. Along the fixed-ratio refinement family $\alpha_1:\alpha_2=2:3$, one finds for example
\begin{equation}
\label{eq:s16-005}
\widehat{\mathcal G}^{11}_{11}
=
2.05,\ 2.13,\ 2.21,\ 2.28,\ 2.35,
\qquad
\widehat{\mathcal G}^{12}_{11}
=
-0.076,\ -0.153,\ -0.225,\ -0.296,\ -0.367
\end{equation}
at $N_1=8,16,32,64,128$. The growth is logarithmic in $N$, not convergent. This is not a bug: it is the lattice-regulated branch-point normal-ordering divergence caused by eliminating the outgoing leg in the presence of the discontinuous concatenation map. It is precisely this reduced-form ultraviolet divergence that feeds the determinant/vacuum-normalization sector of the three-tachyon amplitude and produces the observed finite-$N$ signal of the critical bosonic dimension.

Consequently the honest continuum comparison splits in two parts. First, the reduced Gaussian should be tested through its \emph{physical scalar outputs}, such as the Schur complement $\gamma_T=C_T-B_T^TG_T^{-1}B_T$ and the determinant factor $\kappa_{1\mathrm d}\propto (\det G_T)^{-1/2}$, because those are the quantities that actually enter the sewn amplitudes. Second, if one wants the standard continuum Neumann coefficients $\bar N^{rs}_{mn}$ themselves, one must extract them from the full uneliminated three-leg vertex by Gaussian moments in a fixed DFT/Fourier convention with the appropriate mode rescalings removed. In an arbitrary real zero-sum basis the raw coefficients can carry trivial $a$-scaling from the mode metric, and basis vectors need not approach fixed Fourier harmonics, so the clean comparison basis remains the DFT basis or an explicitly equivalent fixed-harmonic basis.

\section{Zero modes, loop momenta, and determinant primes}
The prime on bosonic determinants should not be left implicit. The clean implementation is to separate the center-of-mass mode on every cylinder from the start:
\begin{equation}
\label{eq:s17-001}
X_n^{(r)}(\tau)=x_{\mathrm{cm}}^{(r)}(\tau)+X_n^{\prime(r)}(\tau),
\qquad
\sum_{n=0}^{N_r-1} X_n^{\prime(r)}(\tau)=0.
\end{equation}
Only the oscillator variables $X^{\prime(r)}$ enter the determinant factor. The zero modes are handled separately in momentum space.

At a cubic vertex, the full-boundary overlap implies the weighted center-of-mass relation, and after Fourier transform this produces the usual transverse momentum conservation
\begin{equation}
\label{eq:s17-002}
\delta^{(\perpD)}(p^{(1)}_\perp+p^{(2)}_\perp-p^{(3)}_\perp).
\end{equation}
For a connected genus-$h$ diagram, after imposing momentum conservation at all vertices, there remain $h$ independent loop momenta $\ell_A$, $A=1,\dots,h$. These are not part of the determinant prime and must be integrated explicitly.
More precisely, after choosing a cycle basis for the graph, $\ell_A$ may be taken to be the transverse center-of-mass momentum flowing around cycle $A$. Every internal zero-mode momentum is then an affine linear combination of the external transverse momenta and these $\ell_A$.
Figure~\ref{fig:loop-zero-mode-separation} summarizes the bookkeeping: the determinant prime acts only on oscillator fluctuations, while the center-of-mass sector produces explicit loop-momentum and twist integrations on a cycle basis.

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.95, every node/.style={font=\small}]
\node[font=\bfseries] at (-3.2,3.0) {Mode split on one cylinder};
\draw[thick] (-5.2,1.8) -- (-1.2,1.8);
\foreach \x/\h in {-4.8/0.18,-4.2/-0.10,-3.6/0.24,-3.0/-0.16,-2.4/0.13,-1.8/-0.18} {
  \fill ({\x},{1.8+\h}) circle (1.2pt);
\draw[thin,gray] (\x,1.8) -- (\x,{1.8+\h});
}
\fill (-3.2,1.8) circle (1.4pt);
\node[above] at (-3.2,2.28) {mode split $x_{\mathrm{cm}}(\tau)+X_n'(\tau)$};
\node[right] at (-3.1,1.95) {$x_{\mathrm{cm}}(\tau)$};
\draw[decorate,decoration={brace,mirror,amplitude=5pt}] (-5.2,1.15) -- (-1.2,1.15);
\node[below] at (-3.2,0.95) {oscillator sector $X_n'$};

\draw[densely dashed] (0,0.3) -- (0,3.4);

\node[font=\bfseries] at (3.15,3.0) {Independent cycle data};
\draw[thick] (3.1,1.8) circle (1.15);
\fill (3.1,2.95) circle (1.3pt);
\fill (3.1,0.65) circle (1.3pt);
\draw[->,thick] (2.25,2.55) arc[start angle=135,end angle=35,radius=1.0];
\node at (3.05,2.7) {$\ell_A$};
\draw[->,thick,green!50!black] (4.1,1.8) arc[start angle=0,end angle=75,radius=0.75];
\node[green!50!black] at (5.0,2.35) {$\varphi_A$};
\node[left,blue] at (1.95,1.8) {$T_e$};
\draw[->,thick,blue] (2.0,1.8) -- (2.25,1.8);

\node[draw,rounded corners,align=left,text width=5.2cm,inner sep=5pt] at (3.15,-0.1)
{oscillator block:\\
$\det{}' {\cal M}_{B,\mathrm{osc}}$, $\mathrm{Pf}(\mathbb A_{F,\mathrm{osc}})$\\
zero-mode block:\\
$\int \dd^{\perpD}\ell_A$ on the chosen cycle basis};
\end{tikzpicture}
\caption{Separation of oscillator and zero-mode data. On each cylinder one first splits off the center-of-mass mode $x_{\mathrm{cm}}(\tau)$ from the oscillator fluctuations $X_n'(\tau)$. After sewing the diagram, the prime determinant acts only on the constrained oscillator block, while the remaining center-of-mass sector produces explicit loop-momentum integrals $\ell_A$ and twist moduli $\varphi_A$ associated with a basis of graph cycles.}
\label{fig:loop-zero-mode-separation}
\end{figure}

Accordingly, $\det{}'$ means the determinant of the constrained oscillator block only. For tree amplitudes there is no loop-momentum integral, while for loops one gets
\begin{equation}
\label{eq:s17-003}
\begin{aligned}
{\cal A}_{\cal D}
&=(2\pi)^{\perpD}\delta^{(\perpD)}\!\left(\sum p_{\perp}^{\mathrm{ext}}\right)
\int \prod_e \dd T_e
\int \prod_{A=1}^{h}\dd\varphi_A\;
J_{\mathrm{M}}(T,\varphi;\alpha_{\mathrm{ext}})\\
&\quad\times
\int \prod_{A=1}^{h}\dd^{\perpD}\ell_A\;
\Big[\det {\cal M}_{B,\mathrm{osc}}(T,\varphi)\Big]^{-\perpD/2}
\mathrm{Pf}\!\left(\mathbb A_{F,\mathrm{osc}}(T,\varphi)\right)\,
W_{\mathrm{int}}(T,\varphi,\ell).
\end{aligned}
\end{equation}
The explicit prefactor $(2\pi)^{\perpD}\delta^{(\perpD)}(\sum p_\perp^{\mathrm{ext}})$ comes from the Fourier-transform convention used to separate the global transverse zero mode. In the earlier compact sewing formulas that same momentum-conservation factor was left implicit inside the vertex and external-state insertions rather than being displayed up front.
Here $\mathbb A_{F,\mathrm{osc}}$ denotes the antisymmetric Majorana matrix associated with the fermionic oscillator kernel. For a closed string this means the combined left-moving plus right-moving oscillator sector; equivalently one may think of the same factor as the product of the two chiral Pfaffians after a choice of IIA/IIB convention and, at higher genus, a spin-structure sector. If one instead keeps coherent-state variables throughout, the same factor is written as $\det {\cal M}_{F,\mathrm{osc}}(T,\varphi)$. The remaining factor $W_{\mathrm{int}}(T,\varphi,\ell)$ is \emph{not} a new unknown functional inserted by hand. It is simply the explicit output of the local cubic prefactors after they act on the global Gaussian sewing formula. Concretely, the bosonic interaction-point operators $K_{\mathrm{lat}}$, $\widetilde K_{\mathrm{lat}}$ act as derivatives on the bosonic source terms introduced earlier, and after those derivatives have been taken one sets the sources to zero. At tree level the completed sources reduce to the external momenta, while at loop level the zero-mode completion introduces the independent loop momenta $\ell_A$. Since each cubic prefactor contributes one factor of $K\widetilde K$, the resulting $W_{\mathrm{int}}$ is polynomial in loop and external momenta of degree at most $2V$, where $V$ is the number of cubic vertices in the diagram. The purely fermionic polynomial $v_{IJ}^{\mathrm{lat}}$ then multiplies this bosonic derivative output.
No additional transverse-space power multiplies the fermionic Pfaffian: unlike the bosonic determinant, whose exponent reflects the number of transverse coordinates, $\mathbb A_{F,\mathrm{osc}}$ already acts on the full GS fermionic oscillator space, including all SO$(8)$ components and both chiral sectors when the closed-string theory is assembled.

More explicitly, after separating the oscillator sector the loop-momentum dependence always takes the form
\begin{equation}
\label{eq:s17-004}
\exp\!\left[
-\frac12 \ell^T Q(T,\varphi)\,\ell
+L(T,\varphi;p_{\mathrm{ext}})^T\ell
+c_0(T,\varphi;p_{\mathrm{ext}})
\right]
\times
P_{2V}(\ell;p_{\mathrm{ext}}),
\end{equation}
where $Q(T,\varphi)$ is the $h\times h$ positive-definite quadratic form obtained from the zero-mode Gaussian after choosing the cycle basis, $L(T,\varphi;p_{\mathrm{ext}})$ is the corresponding linear coupling of the loop momenta to the external transverse momenta, $c_0(T,\varphi;p_{\mathrm{ext}})$ is the remaining scalar term, and $P_{2V}(\ell;p_{\mathrm{ext}})$ is the degree-at-most-$2V$ polynomial produced by the interaction-point derivatives described in the previous paragraph. Therefore the loop-momentum integrals are themselves finite-dimensional Gaussian moments and can be done analytically. The genuinely numerical part of the higher-loop problem is then the remaining moduli integral over $(T,\varphi)$, unless one chooses to retain the $\ell_A$ variables temporarily for diagnostics or cross-checks.

\section{Short-edge limit and regularization}
One practical advantage of the discrete-$\sigma$ scheme is that the worldsheet spectrum is bounded:
\begin{equation}
\label{eq:s18-001}
\omega_k\leq \omega_{\max}(N)\leq \frac{2}{a},
\end{equation}
where $\omega_{\max}(N)=\max_k \omega_k$ reaches exactly $2/a$ only when $N$ is even and otherwise approaches $2/a$ from below as $N$ increases.
Hence the $T\to 0$ limit of the cylinder kernel is controlled at fixed lattice spacing. For small $T$,
\begin{align}
\omega_k\coth(\omega_k T)&=\frac{1}{T}+\frac{\omega_k^2 T}{3}+O(T^3),
\label{eq:s15-smallT-coth}\\
\omega_k\mathrm{csch}(\omega_k T)&=\frac{1}{T}-\frac{\omega_k^2 T}{6}+O(T^3),
\label{eq:s15-smallT-csch}
\end{align}
so the short cylinder approaches the identity overlap plus local contact corrections. This is precisely where UV/contact divergences of lightcone string field theory should appear in the discrete formalism.

Conversely, the long-cylinder limit $T\to\infty$ projects onto low modes and gives the expected factorization channels. Thus both UV and IR boundaries of moduli space are visible directly in the discrete Gaussian data.

\section{Operational roadmap}
\begin{enumerate}
\item Choose a refinement sequence $a_\nu\to 0$ with $\alpha_r^{(\nu)}=a_\nu N_r^{(\nu)}\to \alpha_r$ and exact full-boundary concatenation $N_3^{(\nu)}=N_1^{(\nu)}+N_2^{(\nu)}$ at every cubic join, imposed directly in $\sigma$ position space at each finite $\nu$.
\item Separate zero modes from oscillators on every propagator cylinder.
\item For each internal edge, build $A_e(T_e)$, $B_e(T_e,\varphi_e)$, and $U_e(T_e,\varphi_e)$ from the FFT-diagonal formulas on the oscillator sector, using exact lattice shifts when $N_e\varphi_e\in\ZZ$ and the stated spectral interpolation prescription otherwise.
\item At each cubic vertex, impose the full-boundary overlap matrix $C_I=(P_1\ P_2\ -\mathbb I_{N_3})$ and construct the kinematic overlap state.
\item In the bosonic theory, evaluate the explicit low-point amplitudes already accessible from the finite-$N$ Gaussian vertex, beginning with the three-tachyon and $2T+1M$ channels, and determine the one-string normalization factors needed to match the standard lightcone targets.
\item Use the join-local analysis only as guidance for which local finite-$a$ structures matter, while keeping the main validation criterion amplitude-level agreement and smooth continuum extrapolation.
\item On the superstring side, restrict to a small local family of interaction-point stencils, but treat the present reduced $\Lambda$ computations only as provisional diagnostics until the local finite-$N$ fermionic insertion has been derived.
\item Use the known continuum GS prefactor first as target data for testing reduced ans\"atze, and then return to the derivation of a genuinely local lattice representative of $K^I_{\mathrm{lat}}\widetilde K^J_{\mathrm{lat}}v^{\mathrm{lat}}_{IJ}$.
\item Assemble the global oscillator matrices ${\cal M}_{B,\mathrm{osc}}(T,\varphi)$, $\mathbb A_{F,\mathrm{osc}}(T,\varphi)$, and the explicit loop-momentum dependence.
\item Integrate all internal boundary fields analytically to get diagram integrand
\[
I_{\cal D}(T,\varphi)=
\;J_{\mathrm{M}}(T,\varphi;\alpha_{\mathrm{ext}})
\big[\det {\cal M}_{B,\mathrm{osc}}(T,\varphi)\big]^{-\perpD/2}\,
\mathrm{Pf}\!\big(\mathbb A_{F,\mathrm{osc}}(T,\varphi)\big)\,
\widetilde W_{\text{int}}(T,\varphi),
\]
\quad where $J_{\mathrm{M}}$ may be omitted if it has already been absorbed into the chosen definition of the lightcone cell measure $\dd\mu_{\mathrm{lc}}=\prod_e\dd T_e\prod_A\dd\varphi_A$.
\item Integrate the loop momenta analytically as Gaussian moments, and perform only the remaining moduli $(T,\varphi)$ integration numerically with Monte Carlo / quasi-Monte Carlo.
\item Use the three-tachyon and three-graviton amplitudes as the first mandatory on-shell validations, then extend the same oscillator-basis comparison to higher external states.
\item Repeat at increasing lattice resolution and compare the reduced-Gaussian scalars $(\gamma_T,\kappa_{1\mathrm d})$ together with the separately extracted full three-leg Gaussian-moment Neumann data against their continuum lightcone counterparts.
\item Treat operator-level bosonic commutators and discrete supercharge closure as secondary structural checks to revisit after the numerical amplitude method is working cleanly.
\end{enumerate}

\section{Minimal first deliverables}
\begin{enumerate}
\item Reproduce exact free-cylinder normalization and two-point propagation at finite $N$.
\item Add the discrete $\sigma$-twist operator $R_N(\varphi)$ and verify the twisted propagator against the centered-frequency Fourier/interpolation formula, distinguishing exact lattice shifts from generic spectral interpolation.
\item Implement one cubic join with the full overlap matrix $C_I=(P_1\ P_2\ -\mathbb I_{N_3})$ and verify the bosonic sewing formula.
\item Evaluate the on-shell bosonic three-tachyon amplitude over several $(N_1,N_2)$ families and extract the one-string normalization factors that turn the explicit bare diagnostic into the standard constant target, up to the conventional external-state normalization.
\item Evaluate the bosonic $2T+1M$ amplitude with the exact finite-$N$ first-harmonic normalization and verify the expected tensor decomposition numerically.
\item Extract the reduced sewn quadratic-form diagnostics $(\gamma_T,\kappa_{1\mathrm d})$ and the separate full three-leg Gaussian-moment Neumann data, and compare the latter with the continuum Neumann coefficients in a fixed Fourier convention.
\item On the superstring side, scan a small local family of lattice prefactors only as provisional ans\"atze, and identify which reduced computations have a smooth ratio-dependent continuum profile.
\item Derive the local finite-$N$ fermionic interaction-point variable and then reevaluate the on-shell superstring three-graviton amplitude numerically against the standard Einstein-Hilbert/Yang-Mills-squared cubic tensor.
\item Compute the first nontrivial loop integrand numerically with explicit twist and analytic loop-momentum elimination.
\item Add continuum extrapolation and uncertainty estimates.
\item Return to operator-level commutators and supercharge closure only after the low-point amplitude numerics are working reliably.
\end{enumerate}

\section{Higher-loop numerical form}
After Gaussian integration over all internal oscillator data and over the finite-dimensional loop-momentum Gaussian moments, each diagram reduces to the explicit finite-dimensional form
\begin{equation}
\label{eq:s21-001}
\begin{aligned}
{\cal A}_{\cal D}
&=
\delta^{(\perpD)}\!\left(\sum p_\perp^{\mathrm{ext}}\right)
\int\prod_{e=1}^{E}\dd T_e
\int\prod_{A=1}^{h}\dd\varphi_A\;
J_{\mathrm{M}}(T,\varphi;\alpha_{\mathrm{ext}})\\
&\quad\times
\Big[\det {\cal M}_{B,\mathrm{osc}}(T,\varphi;N)\Big]^{-\perpD/2}\;
\mathrm{Pf}\!\left(\mathbb A_{F,\mathrm{osc}}(T,\varphi;N)\right)\;
\widetilde W_{\text{int}}(T,\varphi;N),
\end{aligned}
\end{equation}
where:
\begin{itemize}
\item $J_{\mathrm{M}}$ is an optional residual lightcone-measure density on the Schwinger-twist chart $(T,\varphi)$; in conventions where the lightcone Feynman rules are written directly in these variables, it is absorbed into $\dd\mu_{\mathrm{lc}}$ and one sets $J_{\mathrm{M}}=1$,
\item ${\cal M}_{B,\mathrm{osc}}$ and $\mathbb A_{F,\mathrm{osc}}$ are the explicit constrained oscillator matrices assembled from cylinder kernels and full-boundary overlap conditions,
\item the twist moduli $\varphi_A$ enter through the $\sigma$-shift operators in the propagators,
\item the loop momenta $\ell_A$ enter only through the separated zero-mode sector and have already been integrated out analytically,
\item $\widetilde W_{\text{int}}$ is obtained from $W_{\mathrm{int}}(T,\varphi,\ell)$ by carrying out the $\ell_A$ Gaussian moments analytically, so it is the residual polynomial-in-moduli interaction factor after zero-mode integration.
\end{itemize}
This is the practical sense in which discretized $\sigma$ makes higher-loop superstring amplitudes numerically tractable.

\section{Summary}
With discrete $\sigma$, the free lightcone worldsheet path integral becomes an exactly computable finite-dimensional Gaussian on each propagator cylinder. The interacting problem is then cleanly separated into three parts: exact free propagation on the cylinders, exact site-space sewing of the boundaries at each cubic join, and a Green--Schwarz interaction-point prefactor whose bosonic derivative part is explicit while the fermionic interaction-point variable still needs a genuinely local finite-$N$ derivation. The loop-side free building block is now also explicit numerically: the centered-frequency twist operator has been checked against exact lattice shifts, and the corresponding oscillator-sector twisted trace quadratic form has been verified to have strictly positive real part with log-determinant matching its closed Fourier-mode formula on the sampled grid.

This also determines the natural division of labor between bases. The $\sigma$-position basis is the primary computational basis for higher-loop sewing, because the propagators are exact Gaussians there and the boundary concatenation is local there. The Fourier/oscillator basis is the primary comparison basis, because conventional lightcone Neumann coefficients and low-point lightcone amplitudes are written most naturally in that language, with Lorentz/SUSY generators available as optional structural checks when needed.

What the note makes explicit is the first two pieces together with the resulting finite-dimensional Gaussian assembly problem. In the bosonic sector, the explicit discrete cubic vertex now goes further in three complementary ways. First, the three-tachyon amplitude has been reduced to an exact Gaussian formula and the remaining bare normalization factor has been checked numerically to factorize into incoming/outgoing one-string pieces with no irreducible three-body dependence; in the current automated suite this factorization still holds with residual at the $10^{-9}$ level and the critical-dimension scan still singles out $D_\perp=24$. Second, the Schur complement $\gamma_T$ itself now has a direct analytic continuum comparison: the fixed-ratio Richardson extrapolations agree with the standard continuum lightcone target with maximum absolute error $1.94\times10^{-5}$ and maximum relative error $5.37\times10^{-5}$ on the sampled family set. Third, the bosonic two-tachyon/one-massless diagnostic can now be written with an exact finite-$N$ external-state normalization, $C_{1,N}=\pi\alpha'/(2N\sin(\pi/N))$, and the resulting tensor decomposition already shows that the trace term is $O(a)$ while the physical $q_{\mathrm{rel}}^I q_{\mathrm{rel}}^J$ coefficient approaches a smooth nonzero continuum profile, numerically $A_{\rm tr}\approx 0$ and $B_{\rm rel}\to 1.9203$ in the present continuum fit. These are exactly the kinds of amplitude-level checks that matter for the present project: the standard continuum lightcone construction is taken as known, and the question is whether the discrete-$\sigma$ method reproduces it numerically. What remains open on the bosonic side is therefore no longer the reduced Gaussian kinematics, but the overall cubic normalization and its principled continuum/operator derivation. On the superstring side, the nonzero-mode bosonic part of the three-graviton prefactor has also now been reduced explicitly, and that calculation already shows that the current minimal nearest-neighbor right-arc stencil is too naive: its one-point coefficient vanishes to numerical precision, so the expected momentum-bilinear piece of the graviton tensor cannot yet emerge from that raw choice. Beyond that, the present fermionic numerics must now be read more carefully than before. The explicit tree-level Grassmann contraction is explicit only in the reduced $\Lambda$ ansatz built from the overlap-constrained averaged zero mode, not from a derived local finite-$N$ interaction-point fermion. Within that reduced ansatz the direct continuum scan of the fermionic amplitudes shows that the minimal stencil is the only blocked candidate while every unblocked positive-$t$ candidate satisfies
\[
\frac{{\cal A}_F(\epsilon_{23},\epsilon_{24},\epsilon_\parallel)}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}=\frac12,
\qquad
\lambda^2
\frac{{\cal A}_F(\epsilon_\parallel,\epsilon_{23},\epsilon_{23})}
{{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)}=1,
\]
with the dilaton and antisymmetric benchmark channels still vanishing to machine precision in the current regression suite. More strongly, these benchmark channels are now compared directly to the known flat-space GS lightcone cubic target at the level of tensor structure,
\(
\mathbb{P}^I\mathbb{P}^J v_{IJ}(\Lambda)
\)
in the same reduced convention, with maximum finite-$N$ scan error $1.60\times10^{-14}$, but still without an independently fixed overall normalization and still without an independent derivation of the local fermionic insertion. The new local-vacuum reduction step sharpens the three-point statement for the present canonical endpoint-difference candidate: across the sampled $5^3$ local channel catalog, every positive-degree $\Xi_{\mathrm{loc}}$ sector now vanishes after the explicit nonzero-mode vacuum contraction, so the catalog collapses to 100 vanishing channels and 25 pure reduced channels. In particular, the benchmark dilaton quartic sector gives zero after contraction. The new helper \texttt{local\_superstring\_tree\_benchmark.py} then assembles the actual trace-dropped benchmark amplitudes from these vacuum-contracted local responses and the bosonic coefficients $(A_\delta,B_{qq})$. On the sampled family set it agrees exactly with the reduced assembly and matches the benchmark closed forms with maximum error below $10^{-14}$. So, for the present canonical endpoint-difference candidate and three-point vacuum external states, the explicit local construction already reproduces the same benchmark graviton, dilaton, and antisymmetric-channel answers as the reduced pipeline, but now by an actual local-vacuum reduction rather than by direct reduced insertion. After removing the trivial $1/N_1$ scaling, the surviving positive branch is also again very close to one common $\lambda$-profile times one overall normalization, now for the actual scaled channel amplitude $N_1{\cal A}_F(\epsilon_{23},\epsilon_{23},\epsilon_\parallel)$ itself, with relative rank-one error and singular-value ratio both at $1.11\times 10^{-4}$. The bosonic normalization side has also become more explicit: the helper \texttt{bosonic\_normalization\_structure.py} now packages the gauge-invariant three-leg tail and the gauge-fixed incoming/outgoing one-string tails into machine-readable fits. On the $4\le N_1,N_2\le 60$, $N_3\le 120$ grid it gives ${\cal C}_{\mathrm{tail}}=-22.496054835$ with invariant-tail RMS residual $2.48\times 10^{-7}$, while the fixed incoming/outgoing nonlinear tails $(7,\pi,\pi^2/72)$ and $(-5,-\pi,\pi^2/72)$ leave only linear-plus-constant remainders with RMS residuals $1.61\times 10^{-12}$ and $2.91\times 10^{-11}$. On the loop side, the free-cylinder checks now go one step further than the twisted trace diagnostic alone: the first explicit single-cylinder oscillator trace prototype, built from the same twisted bosonic and fermionic kernels, matches the closed mode-product formulas on the sampled grid with maximum relative errors $2.40\times10^{-13}$ in the bosonic one-coordinate factor and $1.22\times10^{-15}$ in the fermionic coherent-state factor. A new stable log-polar scan of the unsummed sector ratio shows that no pre-GSO sector is yet close to Bose--Fermi cancellation on the sampled grid: the closest sampled sector has distance $0.34085$ from the target ratio $1$, while the worst sampled log-magnitude is already of order $5.0\times 10^3$. So the next loop-side target is no longer another free-kernel identity, but the explicit spin-structure/GSO and zero-mode assembly needed for a physical cancellation test. The older Weyl-block and projected-channel calculations remain useful as auxiliary structure checks, but they are no longer the strongest statement we have. What this still does \emph{not} determine is the exact physical normalization and operator interpretation of the surviving branch, nor does it remove the need to fix the actual lattice prefactor by the discrete supercharge algebra or to derive the correct branch-point-normalized finite-$N$ fermionic interaction-point variable. The fermionic squeezed-state notation is likewise still only partially explicit: the exact overlap constraints are known, the first local vacuum reduction for the canonical endpoint-difference candidate is now in hand, but a more general Grassmann-moment extraction of finite-$N$ fermionic cubic data is still deferred. So the immediate task is not to reprove standard lightcone-gauge consistency, but to demonstrate that the discrete-$\sigma$ machinery produces the correct bosonic amplitudes, to finish the bosonic normalization match, and to rebuild the superstring calculation on a genuinely local fermionic definition. Operator-level bosonic commutators and discrete supercharge closure remain worthwhile structural follow-ups, but for the superstring they are also part of fixing the vertex itself rather than optional afterthoughts.

\begin{thebibliography}{99}

\bibitem{GreenSchwarz1982Vertices}
M.~B.~Green and J.~H.~Schwarz,
``Supersymmetric dual string theory: (II). Vertices and trees,''
\emph{Nucl.\ Phys.\ B} \textbf{198} (1982) 252--268,
\doi{10.1016/0550-3213(82)90556-9}.

\bibitem{GreenSchwarz1983Interactions}
M.~B.~Green and J.~H.~Schwarz,
``Superstring interactions,''
\emph{Nucl.\ Phys.\ B} \textbf{218} (1983) 43--88,
\doi{10.1016/0550-3213(83)90475-3}.

\bibitem{GreenSeiberg1988}
M.~B.~Green and N.~Seiberg,
``Contact interactions in superstring theory,''
\emph{Nucl.\ Phys.\ B} \textbf{299} (1988) 559--586,
\doi{10.1016/0550-3213(88)90549-4}.

\bibitem{GreensiteKlinkhamer1988}
J.~Greensite and F.~R.~Klinkhamer,
``Superstring amplitudes and contact interactions,''
\emph{Nucl.\ Phys.\ B} \textbf{304} (1988) 108--128,
\doi{10.1016/0550-3213(88)90622-0}.

\bibitem{Berkovits1992N20}
N.~Berkovits,
``The heterotic Green--Schwarz superstring on an $N=(2,0)$ super world-sheet,''
\emph{Nucl.\ Phys.\ B} \textbf{379} (1992) 96--120,
\doi{10.1016/0550-3213(92)90591-X}.

\bibitem{Berkovits1993Twistor}
N.~Berkovits,
``Calculation of Green--Schwarz superstring amplitudes using the $N=2$ twistor-string formalism,''
\emph{Nucl.\ Phys.\ B} \textbf{395} (1993) 77--118,
\doi{10.1016/0550-3213(93)90209-8}.

\bibitem{SpradlinVolovich2002}
M.~Spradlin and A.~Volovich,
``Superstring interactions in a pp-wave background,''
\arxiv{hep-th/0204146}.

\bibitem{PankiewiczStefanski2002}
A.~Pankiewicz and B.~Stefanski,
``pp-wave light-cone superstring field theory,''
\arxiv{hep-th/0210246}.

\bibitem{DVV1997Matrix}
R.~Dijkgraaf, E.~Verlinde and H.~Verlinde,
``Matrix String Theory,''
\emph{Nucl.\ Phys.\ B} \textbf{500} (1997) 43--61,
\doi{10.1016/S0550-3213(97)00326-X},
\arxiv{hep-th/9703030}.

\bibitem{DijkgraafMotl2003}
R.~Dijkgraaf and L.~Motl,
``Matrix string theory, contact terms, and superstring field theory,''
\arxiv{hep-th/0309238},
\doi{10.48550/arXiv.hep-th/0309238}.

\bibitem{Kishimoto2006}
I.~Kishimoto, S.~Moriyama and S.~Teraguchi,
``Twist field as three string interaction vertex in light-cone string field theory,''
\emph{Nucl.\ Phys.\ B} \textbf{744} (2006) 221--237,
\doi{10.1016/j.nuclphysb.2006.03.035}.

\bibitem{Ando2025}
Y.~Ando, R.~Fujii, H.~Kunitomo and J.~Totsuka-Yoshinaka,
``A Consistent Light-Cone-Gauge Superstring Field Theory,''
\emph{Prog.\ Theor.\ Exp.\ Phys.} \textbf{2025} (2025) 033B02,
\doi{10.1093/ptep/ptaf021},
\arxiv{2411.19570}.

\end{thebibliography}

\end{document}
