\documentclass[12pt]{article}
\pdfoutput=1

\usepackage{draft}
\usepackage[hidelinks]{hyperref}

\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\begin{document}

\begin{center}
\LARGE Bosonized Interpretation of the Genus-One $bc$ Sewing Defect
\end{center}

\section{Goal}

This note records a working picture of how the discretized $bc$ path integral of
\[
\Psi_c[c] \propto \prod_{n=1}^\infty c_n
\]
should be reproduced from a bosonized scalar with background charge on the \emph{sewn disk}. The main points are:
\begin{enumerate}
\item the \emph{global} zero-mode constraint coming from the singular sewn-disk metric,
\item the identification of where the arc-dependent sewing data that selects concrete $b$-ghost functionals actually resides.
\end{enumerate}

A key finding is that the shifted field $\hat\phi(z) \equiv \phi(z) - \log z$ has a \emph{universal}, arc-independent jump $i\pi$ across every seam. Therefore:
\begin{itemize}
\item the $\hat\phi$ variable encodes only the sign flip $c(z')/z' = -c(z)/z$ and carries no arc-specific information;
\item the arc-dependent data that determines the $b$-ghost insertions resides in the \emph{original} sewing rule for $\phi$, specifically in the interplay between the Jacobian piece $-2\log z$ and the identification geometry (which boundary points are paired);
\item in the discretized path integral, this data manifests as a linear term in the Gaussian for $\phi$, whose singular behavior at the arc junctions (Strebel vertex positions) localizes the $b$ insertions.
\end{itemize}

\section{Bosonized Variables}

For charge bookkeeping we use a chiral scalar $\phi$ such that
\be
j(z) = - \pa \phi(z), \qquad c(z) \sim e^{\phi(z)}, \qquad b(z) \sim e^{-\phi(z)}.
\ee
Thus a factor $e^{q\phi}$ carries ghost number $q$. We only need these relations and do not rely on a detailed oscillator construction in this note.

The genus-one disk sewing rule for the $c$ ghost is
\be
\frac{c(z')}{z'} = - \frac{c(z)}{z},
\qquad
z'=\frac{q_i}{z},
\qquad
|q_i|=1,
\label{eq:czglue}
\ee
on the $i$-th identified arc pair. Equivalently,
\be
c(z') = - \frac{z'}{z} c(z)
= - \frac{q_i}{z^2} c(z).
\ee
Therefore the bosonized scalar obeys
\be
\phi(z') = \phi(z) + \Lambda_i(z),
\qquad
\Lambda_i(z) = i\pi + \log q_i - 2 \log z.
\label{eq:phijump}
\ee

\section{Split into Jacobian and Endpoint Pieces}

It is useful to separate
\be
\Lambda_i(z) = \Lambda_i^{\rm end} + \Lambda^{\rm jac}(z),
\qquad
\Lambda_i^{\rm end} = i\pi + \log q_i,
\qquad
\Lambda^{\rm jac}(z) = - 2 \log z.
\label{eq:lambdasplit}
\ee

The piece $\Lambda^{\rm jac}$ is universal: it is the same on every sewn arc and comes entirely from the tensorial transformation law of $c$. The piece $\Lambda_i^{\rm end}$ is constant on each arc and carries the residual phase information.

One might hope that introducing the shifted field
\be
\hat{\phi}(z) \equiv \phi(z) - \log z
\label{eq:phihatdef}
\ee
would isolate the arc-dependent information in a simple constant jump. However, a careful calculation shows that the jump of $\hat\phi$ is in fact \emph{universal}. Using $z' = q_i/z$, so that $\log z' = \log q_i - \log z$:
\ie
\hat{\phi}(z')
&= \phi(z') - \log z'
= \bigl[\phi(z) + i\pi + \log q_i - 2\log z\bigr] - \bigl[\log q_i - \log z\bigr]
\\
&= \phi(z) + i\pi - \log z
= \hat{\phi}(z) + i\pi.
\label{eq:phihatjump}
\fe
The $\log q_i$ terms cancel because the definition of $\hat\phi$ subtracts $\log z$ at both $z$ and $z'$, and the difference $\log z' - \log z = \log q_i - 2\log z$ absorbs both the endpoint piece $\log q_i$ and one power of the Jacobian piece $-2\log z$.

Physically, $e^{\hat\phi(z)} = c(z)/z$, and the universal jump $\hat\Lambda = i\pi$ simply states that $c(z')/z' = -c(z)/z$, which is the original sewing rule \eqref{eq:czglue}. The shifted field $\hat\phi$ therefore encodes no arc-dependent information; it merely restates the sign flip in logarithmic form.

\section{Global Zero-Mode Constraint on the Sewn Disk}

The robust statement is the zero-mode condition for the bosonized scalar on the \emph{singular sewn disk}. If operator insertions carry bosonized charges $q_a$, then integrating over the zero mode of $\phi$ imposes
\be
\sum_a q_a = Q(1-g)
\label{eq:globalneutrality}
\ee
per chiral sector, with $Q=3$ for the bosonized $bc$ system. Equivalently,
\be
\sum_a q_a =
\begin{cases}
0, & g=1,\\
-3, & g=2.
\end{cases}
\label{eq:g1g2neutrality}
\ee

This is the right way to phrase the genus dependence. The sewn disk knows the genus only through the singular Weyl factor produced by the sewing. Therefore the curvature concentrated at the puncture, the seam junctions, and any other singular loci created by the sewing must combine to reproduce \eqref{eq:globalneutrality}.

\section{Local Decomposition of the Background Charge}

The local distribution of the background charge on the sewn disk is a separate issue from the global condition \eqref{eq:globalneutrality}. It is natural to expect contributions from the singular points associated with the Strebel geometry.

For genus one, the familiar disk-frame singularities are:
\begin{enumerate}
\item the puncture at the disk origin,
\item the two triples of boundary points that sew to the two cubic Strebel vertices.
\end{enumerate}
In this case, a local split of the form
\be
-1 + \frac12 + \frac12 = 0
\label{eq:g1localsplit}
\ee
at the level of the singular Weyl factor is plausible and consistent with the resulting genus-one neutrality condition.

For genus two, however, a naive extrapolation using only one puncture and six cubic vertices is not sufficient. If one simply assigns $-1$ to the puncture and $+\frac12$ to each cubic vertex, one obtains
\be
-1 + 6\cdot \frac12 = 2,
\ee
which does \emph{not} reproduce the genus-two condition \eqref{eq:g1g2neutrality}. Therefore additional negative contributions must be present somewhere in the singular sewn-disk description.

So the right conclusion at present is:
\begin{itemize}
\item the Strebel vertices very likely \emph{do} contribute to the local background-charge balance;
\item but they cannot be the whole story in higher genus;
\item only the \emph{total} singular curvature is fixed unambiguously by \eqref{eq:globalneutrality}.
\end{itemize}

\section{Operator Charges}

The usual ghost insertions already match the global neutrality condition.

For genus one, the relevant chiral correlator is
\be
\la c(p)\,\cL[b]\ra_{\Sigma_{1,1}},
\ee
whose bosonized charge is
\be
(+1)+(-1)=0.
\label{eq:g1insertions}
\ee
Nonchirally this becomes
\be
c\wt c : +2,
\qquad
b\wt b : -2,
\qquad
\text{total }0.
\ee

For genus two, the relevant chiral correlator is
\be
\la c(p)\,\prod_{r=1}^4 \cL_r[b]\ra_{\Sigma_{2,1}},
\ee
whose bosonized charge is
\be
(+1)+4(-1)=-3,
\label{eq:g2insertions}
\ee
exactly as required by \eqref{eq:g1g2neutrality}. Nonchirally this is
\be
c\wt c : +2,
\qquad
4\times b\wt b : -8,
\qquad
\text{total }-6.
\ee

Thus the role of the singular sewn-disk geometry is to reproduce the genus-dependent right-hand side of \eqref{eq:globalneutrality}, while the usual $c$ and $b$ insertions saturate that charge in the expected way.

\section{Where the Arc-Dependent Data Lives}

Since the $\hat\phi$ variable has a universal jump (Section~3), the arc-dependent information that selects the $b$-ghost functionals must reside elsewhere. It is encoded in the \emph{original} sewing rule for $\phi$ itself:
\be
\phi(k') = \phi(k) + \Delta_i(k),
\qquad
\Delta_i(k) = i\pi + \log q_i - 2\log z_k,
\label{eq:phishift}
\ee
where $z_k = e^{2\pi i k/L}$ and the arc label $i$ depends on which segment $k$ belongs to.

\subsection{The sewing shift and its structure}

It is convenient to work with the spacelike bosonization $c = e^{i\varphi}$, where $\varphi$ is a real scalar with standard positive-definite kinetic term and $\phi = i\varphi$. The sewing rule $c(k') = -e^{2\pi i(k'-k)/L}c(k)$ then gives
\be
\varphi(k') = \varphi(k) + \delta_k,
\qquad
\delta_k = \pi + \frac{2\pi(k'-k)}{L},
\label{eq:varphishift}
\ee
where $\delta_k$ is \emph{real} and $k'=s(k)-k$ is the partner of site $k$ under the identification.

Within each of the three arcs, $k'-k$ decreases by 2 for each unit increase in $k$, so $\delta_k$ has a uniform slope:
\be
\delta_{k+1} - \delta_k = -\frac{4\pi}{L} \qquad\text{(within any arc)}.
\ee
At the three arc junctions ($k=\ell_1$, $k=\ell_1+\ell_2$, $k=L/2$), $\delta_k$ has \emph{discontinuous jumps}.

\subsection{Explicit identification of the $b$-ghost insertions}
\label{sec:explicitB}

Define the normalized edge lengths $t_i = 2\ell_i/L$ with $t_1+t_2+t_3=1$. The discrete derivative $\delta_{k+1}-\delta_k$ can be decomposed as
\be
\delta_{k+1}-\delta_k = -\frac{4\pi}{L}
+ \sum_{v=1}^{3} J_v\,\delta_{k,k_v},
\label{eq:jumpdecomp}
\ee
where $k_v$ are the three junction positions and $J_v$ are the jump magnitudes. The three junctions correspond to the boundary preimages of the two cubic Strebel vertices; at each junction, two of the three ribbon-graph edges meet.

The jump magnitudes are determined exactly by the edge lengths:
\be
\begin{array}{c|c|c|c}
\text{junction} & \text{position} & \text{edges meeting} & \text{jump magnitude} \\
\hline
v_1 & k=\ell_1 & \text{edges 1, 2} & J_1 = \pi(t_1+t_2) = \pi(1-t_3) \\
v_2 & k=\ell_1+\ell_2 & \text{edges 2, 3} & J_2 = \pi(t_2+t_3) = \pi(1-t_1) \\
v_3 & k=L/2 & \text{edges 3, 1} & J_3 = \pi(t_3+t_1) = \pi(1-t_2)
\end{array}
\label{eq:jumptable}
\ee
This has been verified numerically (see \texttt{bosonized\_ghost.py}) to machine precision ($\sim 10^{-16}$) for all $L$ tested. In addition, the jump signal is \emph{identically zero} away from the junctions: the discrete derivative $\delta_{k+1}-\delta_k + 4\pi/L$ vanishes to machine precision at every non-junction site.

Therefore $\delta_k$ decomposes cleanly into
\be
\delta_k = \delta_k^{\rm smooth} + \delta_k^{\rm sing},
\ee
where $\delta^{\rm smooth}$ is strictly linear (extrapolating the within-arc slope from the first arc) and $\delta^{\rm sing}$ is a \emph{staircase} supported only at the three junctions. In the continuum limit,
\be
\frac{d\delta^{\rm sing}}{d\sigma} = \sum_{v=1}^{3} J_v\,\delta(\sigma - \sigma_v),
\label{eq:deltasing}
\ee
which is a sum of delta functions localized at the Strebel vertex preimages, with magnitudes set by the edge lengths.

This is the explicit identification of the $b$-ghost insertions: each junction contributes a delta-function source whose strength $J_v = \pi(1-t_v)$ is the fraction of the boundary perimeter subtended by the two edges meeting at that vertex.

\subsection{Linear term in the Gaussian}

After imposing \eqref{eq:varphishift} for the dependent half of the variables, the bosonized wavefunctional for $\Psi_c$ takes the form (in the exponent)
\be
-\sum_{k,\ell=1}^{L/2} A_{k\ell}\,\varphi(k)\varphi(\ell)
\;+\; \sum_{k=1}^{L/2} v_k\,\varphi(k)
\;+\; \text{const},
\ee
where $A_{k\ell}$ is the \emph{same} matrix as in the free boson sewing (the quadratic form is insensitive to the real shift $\delta$), and
\be
v_k = -\omega_k + \frac{2i}{L},
\qquad
\omega_k = 2\sum_{s=1}^{L/2}\bigl(A^{(0)}_{k,p(s)} + A^{(0)}_{p(k),p(s)}\bigr)\delta_s,
\label{eq:linearterm}
\ee
with the $2i/L$ piece from the vertex operator $e^{i\varphi_0}$. Here $A^{(0)}$ is the unsewed circulant matrix, $p(s)$ denotes the partner of site $s$, and $\omega_k$ is the cross-term from the sewing shifts.

The vertex-operator piece $2i/L$ lies entirely in the zero-mode direction of $A$ (since $\sum_k (2i/L) = i$, while $\sum_k \omega_k = 0$). After projecting onto the subspace orthogonal to the zero mode, $v_k$ reduces to $-\omega_k$, which is real. The zero-mode piece enforces the global charge neutrality \eqref{eq:globalneutrality} (the $c$-ghost carrying charge $+1$).

Since $\omega_k$ inherits the decomposition of $\delta_k$, the linear coefficient also separates into smooth and singular parts:
\be
\omega = \omega^{\rm smooth} + \omega^{\rm sing},
\ee
where $\omega^{\rm sing}$ is the convolution of the Green's function kernel with the jump sources \eqref{eq:deltasing}. In the continuum limit,
\be
\omega^{\rm sing}(\sigma) \sim \sum_{v=1}^3 J_v\,G(\sigma, \sigma_v),
\ee
where $G$ is the scalar propagator on the sewn boundary. This is the profile of a bosonized scalar sourced by vertex operators $e^{-\varphi(\sigma_v)}$ at the Strebel vertices, confirming that the $b$-ghost insertions arise from the jump discontinuities.

\subsection{Relation to the combined matter+ghost amplitude}

The Gaussian integral in $\varphi$ gives
\be
(\det' \wt{A})^{-1/2}\,\exp\!\left(\tfrac14\,\omega^T \wt{A}^{-1} \omega\right)
\times (\text{zero-mode factor}),
\ee
where $\wt{A}$ is the reduced matrix with the zero mode removed. The bilinear form $\omega^T \wt{A}^{-1}\omega$ captures the vertex-operator contribution: it is the scalar two-point function evaluated at the Strebel vertex positions.

However, the full relationship
\be
|\det B| \stackrel{?}{\propto} (\det' A)^{1/2}\,\exp\!\left(\tfrac14\,\omega^T \wt{A}^{-1}\omega\right)
\ee
does \emph{not} hold as stated at finite $L$: the residual is moduli-dependent. The missing piece is the \emph{Weyl anomaly} factor. The free boson ($c=1$) and the bosonized ghost ($c=-26$) have different Weyl anomalies on the singular Strebel metric, contributing a moduli-dependent correction proportional to the Liouville action $S_L = \frac{1}{12\pi}\int\partial\omega\bar\partial\omega$. In the combined matter+ghost system (26 bosons $+$ ghost), the Weyl anomaly cancels, consistent with the known result
\be
|\det B|\,(\det' A)^{-13} \propto \tau_2^{-13}\,|\eta(\tau)|^{-48}\,|\widehat{f}(0)|^2\,|\nu|^4.
\ee
The structural identification of the $b$-ghost insertion \emph{locations} is exact at any $L$; only the overall \emph{magnitude} of $\det B$ relative to $\det A$ receives the Weyl anomaly correction.

\subsection{Localization at Strebel vertices}

Combining the results above: the $b$-ghost insertions in $\det B$ arise from the discontinuities of the sewing shift $\delta_k$ at the three arc junctions. Specifically:
\begin{enumerate}
\item the smooth part $\delta^{\rm smooth}$ (constant slope $-4\pi/L$) encodes the Weyl anomaly / background-charge contribution from the Jacobian between the disk metric and the Strebel metric;
\item the singular part $\delta^{\rm sing}$ (jumps at the junctions) sources the bosonized scalar at the Strebel vertex positions via the Green's function, generating the $b$-ghost vertex operators $b(z_v) \sim e^{-i\varphi(z_v)}$;
\item the jump magnitude $J_v = \pi(1-t_v) = \pi(t_{v_1}+t_{v_2})$ at each junction is the fraction of the boundary perimeter subtended by the two edges meeting at the corresponding Strebel vertex.
\end{enumerate}

The renormalization factor $(1-z/z_v)^{2/3}$ found numerically in the discretized $\det B$ should emerge from the regularization of $\wt{A}^{-1}$ at the singular points, matching the Jacobian $\gamma_v$ between disk and flat coordinates near the vertex.

\subsection{Vertex functionals}

The natural local functionals are the renormalized Strebel-vertex evaluations
\be
\beta_v[q]
\equiv
\lim_{z\to z_v}
\left(1-\frac{z}{z_v}\right)^{2/3}
q_{zz}(z),
\label{eq:betavdef}
\ee
because near a cubic Strebel vertex one has
\be
\frac{du}{dz} \sim (z-z_v)^{-1/3},
\qquad
q_{zz}(z)=q_{uu}(u)\left(\frac{du}{dz}\right)^2
\sim
(z-z_v)^{-2/3}.
\ee
Hence $\beta_v$ is the finite part of the $b$ field at the vertex in a regular local coordinate.

In punctured genus one the holomorphic zero-mode space is one-dimensional,
\be
H^0(\Sigma,K^2(p)) \cong \bC.
\ee
Therefore any nonzero linear functional is necessarily proportional to the Beltrami insertion:
\be
\beta_{v_+}[b]
\propto
\beta_{v_-}[b]
\propto
B[\mu][b].
\label{eq:seampropto}
\ee
This is the precise sense in which the bosonized sewing data, once processed through the Green's function, must produce an effective $b$-ghost insertion at the Strebel vertices.

In genus two, the six vertex functionals $\beta_v$ ($v=1,\dots,6$) live on a four-dimensional zero-mode space $H^0(\Sigma,K^2(p))$. Only four independent linear combinations survive:
\be
\cL_r = \sum_{v=1}^6 c_{rv}\,\beta_v,
\qquad
r=1,\dots,4.
\label{eq:g2linearcomb}
\ee
The conversion from the vertex-functional basis to the Beltrami-dual basis is encoded in a $4\times 4$ Jacobian $|\det M|^2$.

\section{Resulting Picture}

The bosonized version of the discretized path integral should be organized as follows:
\begin{enumerate}
\item Start from the bosonized wavefunctional corresponding to the chosen ghost state, e.g.\ $\Psi_c$.
\item Impose the $z$-dependent sewing rule \eqref{eq:phijump} for $\phi$ directly (not the shifted $\hat\phi$).
\item The sewing produces a Gaussian with a linear term $v_k$ on top of the same quadratic form $A$ as the free boson.
\item The linear term encodes the $b$-ghost insertions; its singularities at the arc junctions (Strebel vertices) localize the $b$ insertions there.
\item The zero-mode integral enforces the global charge neutrality \eqref{eq:globalneutrality}.
\item The resulting correlator is $\la c\wt c(p)\,\cL[b]\,\ol{\cL}[\wt b]\ra_\Sigma$ with vertex-supported $b$-ghost functionals such as \eqref{eq:seampropto} or, in higher genus, \eqref{eq:g2linearcomb}.
\end{enumerate}

Note that the shifted field $\hat\phi = \phi - \log z$ is \emph{not} the right variable for this analysis: it removes all arc-dependent information and reduces the sewing to a universal sign flip $e^{\hat\phi(z')} = -e^{\hat\phi(z)}$. The arc-dependent structure that determines the $b$ insertions lives in the interplay between the Jacobian factor $-2\log z$ and the identification geometry.

\section{Practical Continuum Translation}

In continuum notation, the discretized bosonized path integral is expected to have the schematic form
\be
\int [D\phi] \,
\Psi_c^{(\phi)}[\phi]\,
\delta_{\rm twisted\ sewing}
\leadsto
\left\langle
c\wt{c}(p)\,
\cL_{\rm vertex}[b]\,
\ol{\cL_{\rm vertex}}[\wt{b}]
\right\rangle_{\Sigma},
\ee
where $\Sigma$ is the punctured Riemann surface associated with the ribbon graph and $\cL_{\rm vertex}$ denotes the Strebel-vertex functional data selected by the sewing geometry. The global neutrality of this correlator is fixed by \eqref{eq:globalneutrality}, while the local form of $\cL_{\rm vertex}$ is controlled by the discontinuities of the sewing shift at the arc junctions, propagated through the bosonized Green's function.

\end{document}
